---
title: "Comparative effectiveness of 2 x BNT162b2 vs 2 x ChAdOx1-S in people with kidney disease"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
## Import libraries
library('here')
library('tidyverse')
library('readr')
library('tidyr')
library('lubridate')
library('glue')
library('gt')
library('gtsummary')
library('reshape2')
library('kableExtra')
library('cowplot')
library('fs')
library('survival')
library('survminer')
library('scales')

## Import custom user functions
source(here::here("analysis", "functions.R"))

## Set list of outcomes and date variable names
outcomes <- read_rds(
  here::here("output", "lib", "outcomes.rds")
)
outcome_list = outcomes$short_name
clean_list = outcomes$clean_name
date_list = outcomes$date_name

## Read in data for cumulative incidence curves
data_tte_unmatched <- read_rds(here::here("output", "data", "data_cohort_VE.rds")) %>%
  mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))

data_tte_matched <- read_rds(here::here("output", "data", "data_cohort_VE_matched.rds")) %>%
  mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))

## Import outcome time periods
postvax_list <- read_rds(
  here::here("output", "lib", "postvax_list.rds")
)
postvaxcuts = postvax_list$postvaxcuts
postvax_periods = postvax_list$postvax_periods
period_length = postvaxcuts[2]-postvaxcuts[1]
lastfupday = max(postvaxcuts)

## Set rounding threshold for calculation of KM steps
threshold = 5

## Calculated total cohort size rounded to nearest 5
rounded_n_unmatched = plyr::round_any(nrow(data_tte_unmatched), 5)
rounded_n_matched = plyr::round_any(nrow(data_tte_matched), 5)
```
<br/><br/>  

#### Background
Kidney disease is a significant risk factor for COVID-19-related mortality. Although vaccination has the potential to mitigate this risk, chronic kidney disease (CKD) and kidney failure requiring renal replacement therapy (RRT) have been linked with impaired COVID-19 vaccine immunogenicity and high rates of breakthrough infection among individuals who have received a 2-dose primary vaccine series.

Vaccine recommendations for people with kidney disease in the UK have evolved over time (see [protocol](https://docs.google.com/document/d/1w48W-bCMfn0RdkfxlU6fbRkPv3MnIYd3/edit#heading=h.1fob9te). Relative uptake of different vaccines in this population has been described in our recent [preprint](https://www.medrxiv.org/content/10.1101/2022.06.14.22276391v1). However, the relative vaccine effectiveness (VE) of different regimens remains uncertain. This project seeks to address this key evidence gap.

Most people with kidney disease received a 2-dose homologous primary series of either BNT162b2 or ChAdOx1-S between January and June 2021 (see Supplementary Table 1 of [coverage preprint](https://www.medrxiv.org/content/10.1101/2022.06.14.22276391v1)). Subsequently, individuals received a third primary or first booster dose of an RNA vaccine (either BNT162b2 or ChAdOx1-S). The primary comparison of interest in the present study was post-vaccination outcomes for BNT162b2 vs ChAdOx1-S. Outcomes after receipt of booster doses will be considered as a secondary analyses.
<br/><br/>

#### Inclusion criteria for primary cohort
* Registered for at least 3m before index date (01-Dec-2020)    
* Aged ≥16 on index date
* eGFR<60 in 2 years before index date OR present in UK Renal Registry (UKRR) on 31-Dec-2020 (the status update closest to the index date)  
* No RRT mismatch (primary care dialysis/Tx code but absent from UKRR 2020 population)
* No missing demographic data   
* Received 2 x ChAdOx1-S or 2 x BNT162b2 as first two vaccine doses
* Received first dose after 04 January 2021 (the period in which vaccines were in use)
* Dose interval was in the range of 8-14 weeks
* Events designated as postvaccination outcomes occurred after the date of the second dose
* Not a healthcare worker, care home resident, receiving end-of-life care, or housebound
* No SARS-CoV-2 infection in the 90 days preceding dose 1

### Matching criteria for matched cohort
* Region   
* Age (within 3y)      
* Dose 2 date (within 3d)         
* Dose 1 date (within 7d)         
* JCVI group    
* IMD    
* Ethnicity    
* Kidney disease category (CDK3, CKD4-5, RRT)    
* Clinically extremely vulnerable    
* Prior SARS-CoV-2 at index date    

#### Cohort selection - unmatched
```{r}
flowchart <- read.csv(here::here("output", "tables", "flowchart_VE.csv"))
names(flowchart)[1] = "Criteria"

# Correct wording relating to analysis cut-off
flowchart$Criteria = str_replace(flowchart$Criteria, "8-16 weeks", "8-14 weeks")

# Render flowchart
flowchart %>%
  mutate(`N (rounded)` = prettyNum(plyr::round_any(flowchart$n, 5), big.mark=",")) %>%
  select(Criteria, `N (rounded)`) %>%
  gt() %>%
  tab_options(table.font.size = pct(95), column_labels.font.weigh="bold")
```
<br/><br/>

#### Cohort selection - unmatched
Of the **`r prettyNum(rounded_n_unmatched)`** individuals in the unmatched cohort (see above), **`r prettyNum(rounded_n_matched)`** were selected for the matched cohort (see matching criteria above).
<br/><br/>

#### Table 1: Summary of primary outcome population
```{r}
table_1 <- rbind(
  read_rds(here::here("output", "tables", "table1_VE_primary_redacted_unmatched_all.rds")) %>% mutate(subgroup = "All", subgroup_id = 1),
  read_rds(here::here("output", "tables", "table1_VE_primary_redacted_matched_all.rds")) %>% mutate(subgroup = "Matched (all)", subgroup_id = 2),
  read_rds(here::here("output", "tables", "table1_VE_primary_redacted_unmatched_CKD3.rds")) %>% mutate(subgroup = "CKD3", subgroup_id = 3),
  read_rds(here::here("output", "tables", "table1_VE_primary_redacted_unmatched_CKD4-5.rds")) %>% mutate(subgroup = "CKD4-5", subgroup_id = 4),
  read_rds(here::here("output", "tables", "table1_VE_primary_redacted_unmatched_RRT.rds")) %>% mutate(subgroup = "RRT", subgroup_id = 5)
)

table_1_wide = table_1 %>% 
    pivot_wider(    
      names_from = c(subgroup, subgroup_id),
      values_from = c(`ChAdOx1-S`, `BNT162b2`),
      names_glue = "{.value} [{subgroup_id}]"
    ) 

## Generate table
table_1_wide %>%
    gt(rowname_col = "Variable", groupname_col = "Group") %>%
    tab_spanner(
      label = "Unmatched",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [1]")
    ) %>%
     tab_spanner(
      label = "Matched",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [2]")
    ) %>%
    tab_spanner(
      label = "CKD3 subgroup (unmatched)",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [3]")
    ) %>%
    tab_spanner(
      label = "CKD4-5 subgroup (unmatched)",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [4]")
    ) %>%
    tab_spanner(
      label = "RRT subgroup (unmatched)",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [5]")
    ) %>%

    tab_options(table.font.size = pct(70)) %>%
     tab_style(
        style = list(
          cell_borders(
            sides = c("right"), color = "#cccccc"
          )
          ),
        locations = list(
          cells_body(
            columns = starts_with("BNT")
          )
        )
     ) %>%
    tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
    tab_style(
       style = cell_text(indent = pct(5)),
       locations = cells_body(columns = "Variable")
     )
```
Data are n (%) after rounding to the nearest 5. Any cells with rounded counts or non-counts (relative to the denominator) of >0 and <=10 are redacted. Primary care codes and risk groups are coded by separate binary variables; percentages in these subheadings therefore do not sum to 100. **Prior SARS-CoV-2** was determined based on evidence of a positive SARS-CoV-2 test, COVID-19-related primary care code, or COVID-19-related hospitalisation as of 1st December 2020. **Any immunosuppression** included a history of transplant, immunosuppression, haematologic cancer, or asplenia at baseline. JCVI group was inferred based on age and shielding code lists (to define **Clinically extremely vulnerable** individuals). **Comorbidity count** includes severe obesity, chronic heart disease, diabetes, chronic liver disease, any respiratory disease (including asthma), and chronic neurological disease. CKD, chronic kidney disease; CND, chronic neurological disease; RRT, renal replacement therapy. 
<br/><br/>

#### Cumulative incidence plots and hazard ratios over time
```{r, fig.width=21, fig.height=15}
create_rounded_surv_table = function(outcome_number, input_data) {
  data_surv <-
    input_data %>%
    mutate(
      ind_outcome = get(paste0("ind_",outcome_list[outcome_number])),
      tte_outcome = get(paste0("tte_",outcome_list[outcome_number],"_or_censor"))
    ) %>%
    group_by(vax2_type_descr) %>%
    nest() %>%
    mutate(
      n_events = map_int(data, ~sum(.x$ind_outcome, na.rm=TRUE)),
      surv_obj = map(data, ~{
        survfit(Surv(tte_outcome, ind_outcome) ~ 1, data = .x, conf.type="log-log")
      }),
      surv_obj_tidy = map(surv_obj, ~tidy_surv(.x, times=seq_len(max(postvaxcuts)))), # return survival table for each day of follow up
    ) %>%
    select(vax2_type_descr, n_events, surv_obj_tidy) %>%
    unnest(surv_obj_tidy)

  data_surv_rounded <-
    data_surv %>%
    mutate(
      N = plyr::round_any(max(n.risk, na.rm=TRUE),threshold),
      cml.event = cumsum(replace_na(n.event, 0)),
      cml.censor = cumsum(replace_na(n.censor, 0)),
      cml.event = floor_any(cml.event, threshold),
      cml.censor = floor_any(cml.censor, threshold),
      n.event = diff(c(0,cml.event)),
      n.censor = diff(c(0,cml.censor)),
      n.risk = N - lag(cml.event + cml.censor,1,0),
      summand = n.event / ((n.risk - n.event) * n.risk),
      surv = cumprod(1 - n.event / n.risk),
      surv.se = surv * sqrt(cumsum(replace_na(summand, 0))),
      llsurv = log(-log(surv)),
      llsurv.se = sqrt((1 / log(surv)^2) * cumsum(summand)),
      surv.ll = exp(-exp(llsurv + qnorm(0.025)*llsurv.se)),
      surv.ul = exp(-exp(llsurv + qnorm(0.975)*llsurv.se)),
      cum.in = 1 - surv,
      haz = -(surv-lag(surv, 1, 1))/lag(surv, 1, 1), # n.event / (n.risk * interval),
      haz.se = haz * sqrt((n.risk - n.event) / (n.risk* n.event)),
      cml.haz = cumsum(haz),
      cml.haz.se = surv.se/surv,
    ) %>%
    select(
      vax2_type_descr, time, lagtime, leadtime, interval,
      n.risk, n.event, n.censor, summand,
      surv, surv.se, surv.ll, surv.ul,
      haz, haz.se,
      cml.haz, cml.haz.se
    )
  #write.csv(data_surv_rounded, "data_surv_rounded.csv")
  data_surv_rounded
}

## Collate unmatched survival data
surv_covid_postest = create_rounded_surv_table(1, data_tte_unmatched) %>% mutate(outcome_clean = clean_list[1])
surv_covid_hosp = create_rounded_surv_table(3, data_tte_unmatched) %>% mutate(outcome_clean = clean_list[3])
surv_covid_death = create_rounded_surv_table(4, data_tte_unmatched) %>% mutate(outcome_clean = clean_list[4])
surv_noncovid_death = create_rounded_surv_table(5, data_tte_unmatched) %>% mutate(outcome_clean = clean_list[5])

## Collate across outcomes
surv_collated = rbind(surv_covid_postest, surv_covid_hosp, surv_covid_death, surv_noncovid_death)
surv_collated$outcome_clean = factor(surv_collated$outcome_clean, levels = clean_list)

## Collate KM contrasts for unmatched survival data
surv_covid_postest_contrast = kmcontrast(surv_covid_postest) %>% mutate(outcome_clean = clean_list[1])
surv_covid_hosp_contrast = kmcontrast(surv_covid_hosp) %>% mutate(outcome_clean = clean_list[3])
surv_covid_death_contrast = kmcontrast(surv_covid_death) %>% mutate(outcome_clean = clean_list[4])
surv_noncovid_death_contrast = kmcontrast(surv_noncovid_death) %>% mutate(outcome_clean = clean_list[5])

## Collate across outcomes
surv_collated_contrast = rbind(surv_covid_postest_contrast, surv_covid_hosp_contrast, surv_covid_death_contrast, surv_noncovid_death_contrast)
surv_collated$outcome_clean = factor(surv_collated$outcome_clean, levels = clean_list)

## Collate matched survival data
surv_covid_postest_matched = create_rounded_surv_table(1, data_tte_matched) %>% mutate(outcome_clean = clean_list[1])
#surv_covid_emergency_matched = create_rounded_surv_table(2) %>% mutate(outcome_clean = clean_list[2])
surv_covid_hosp_matched = create_rounded_surv_table(3, data_tte_matched) %>% mutate(outcome_clean = clean_list[3])
surv_covid_death_matched = create_rounded_surv_table(4, data_tte_matched) %>% mutate(outcome_clean = clean_list[4])
surv_noncovid_death_matched = create_rounded_surv_table(5, data_tte_matched) %>% mutate(outcome_clean = clean_list[5])

## Collate across outcomes
surv_collated_matched = rbind(surv_covid_postest_matched, surv_covid_hosp_matched, surv_covid_death_matched, surv_noncovid_death_matched)
surv_collated_matched$outcome_clean = factor(surv_collated_matched$outcome_clean, levels = clean_list)

## Generate KM plot across 4 outcomes
generate_km_plot = function(surv_data) {
  surv_data %>%
  ggplot(aes(x = time, y = 1-surv, colour = vax2_type_descr, fill = vax2_type_descr)) + geom_step(size = 0.8) +
  facet_wrap(.~outcome_clean, nrow=1) +
  geom_rect(aes(xmin=lagtime, xmax=time, ymin=1-surv.ll, ymax=1-surv.ul), alpha=0.1, colour="transparent") +
  scale_x_continuous(breaks=postvaxcuts, limits=c(0, max(postvaxcuts)+period_length), expand = c(0, 0)) +
  scale_y_continuous(expand = expansion(mult=c(0,0.01))) +
  labs(
    x = "",
    y = "Cumulative incidence",
    colour = "",
    title = "") +
  theme_bw() +
  guides(fill="none") +
  scale_colour_manual(values = c("#CC79A7", "#0072B2")) +
  scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
  theme(
    strip.text = element_text(size=20),
    axis.text = element_text(size=20),
    axis.title = element_text(size=20),
    legend.text = element_text(size=20),
    panel.border = element_blank(),
    axis.line.y = element_line(colour = "black"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.spacing = unit(0.8, "lines"),
    plot.title = element_text(hjust = 0),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0, face= "italic"),
    legend.position = "right"  
    )
}
g1 = generate_km_plot(surv_collated) + ggtitle("Unmatched") + theme(title = element_text(size=20))
g1_matched = generate_km_plot(surv_collated_matched) + ggtitle("Matched") + theme(title = element_text(size=20))

### Generate plot of hazard ratios over time

## Read in persontime models
model_persontime = rbind(
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[1],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[1]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[3],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[3]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[4],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[4]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[5],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[5])
  ) %>% 
  mutate(model_group = paste0("Person-time"," (",model_name,")"))

## Read in calendartime models
model_calendartime = rbind(
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_calendartime_",outcome_list[1],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[1]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_calendartime_",outcome_list[3],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[3]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_calendartime_",outcome_list[4],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[4]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_calendartime_",outcome_list[5],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[5])
  ) %>% 
  mutate(model_group = paste0("Calendar-time"," (",model_name,")"))

## Read in matched models
model_matched = rbind(
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_matched_persontime_",outcome_list[1],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[1]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_matched_persontime_",outcome_list[3],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[3]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_matched_persontime_",outcome_list[4],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[4]),
  read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_matched_persontime_",outcome_list[5],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[5])
  ) %>% 
  mutate(model_group = "Matched")

## Collated models
model = rbind(model_persontime, model_calendartime, model_matched)

## Set factor levels
model$model_name = factor(model$model_name, levels = c("unadjusted", "region/date adjusted", "fully adjusted"))
model$outcome_clean = factor(model$outcome_clean, levels = clean_list)

## Remove redacted components from plot
model$estimate = as.numeric(model$estimate)
model$conf.low = as.numeric(model$conf.low)
model$conf.high = as.numeric(model$conf.high)

## Add left, right, and midpoint for full models
model$term_midpoint[model$term=="15-182"] = max(postvaxcuts)+period_length/2
model$term_left[model$term=="15-182"] = max(postvaxcuts)
model$term_right[model$term=="15-182"] = max(postvaxcuts)+period_length

## Add redaction text
model$redaction = NA
model$redaction[model$p.value=="[Redacted]" & model$model==0] = "[R]"
model$n_event = as.numeric(model$AZ_events) + as.numeric(model$BNT_events)
model$redaction[model$n_event==0 & model$model==0] = "[N]"
#write.csv(model, "model.csv")

## Selected fully adjusted models
model_subset = subset(model, model_group %in% c("Person-time (unadjusted)", "Person-time (fully adjusted)", "Calendar-time (fully adjusted)", "Matched"))
model_subset$model_group = factor(model_subset$model_group, levels = c("Person-time (unadjusted)","Person-time (fully adjusted)", "Calendar-time (fully adjusted)", "Matched"))

## Generate HR plot for 4 ouctomes
g2 = ggplot(data = model_subset) +
    geom_point(size = 2.5, aes(y=exp(estimate), x=term_midpoint, colour=model_group), position = position_dodge(width = 30)) +
    geom_linerange(aes(ymin=exp(conf.low), ymax=exp(conf.high), x=term_midpoint, colour=model_group), position = position_dodge(width = 30)) +
    geom_hline(aes(yintercept=1), colour='grey') +
    scale_y_log10(
      limits = c(0.25,4),
      breaks=c(0.25, 0.5, 0.67, 1, 1.5, 2, 4),
      sec.axis = dup_axis(name="<- Favours BNT / Favours AZ ->", breaks = NULL)
    ) +
  facet_wrap(.~outcome_clean, nrow=1) +
  scale_x_continuous(breaks=postvaxcuts, limits=c(0, max(postvaxcuts)+period_length), expand = c(0, 0)) +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#7570B3", "#B40F20")) +
  labs(
    y="Hazard ratio (95% CI)",
    x="Time since second dose (days)",
    colour=NULL,
    title=NULL
  ) +
  theme_bw()+
  annotate("rect", xmin = lastfupday, xmax =  lastfupday+period_length, ymin = 0.25, ymax = 4, alpha = .3, fill = "grey") +
  annotate("text", x =lastfupday+period_length/2, y = 3.3, label = "All", size=7) +
  #geom_text(aes(x = term_midpoint, y = 1, label = redaction), size=6) +
  theme(
    strip.text = element_text(size=20, colour="white"), # set as white to avoid repeating text in aligned plot
    axis.text = element_text(size=20),
    axis.title.y.right = element_text(size=18),
    axis.title = element_text(size=20),
    legend.text = element_text(size=20),
    panel.border = element_blank(),
    axis.line.y = element_line(colour = "black"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.spacing = unit(0.8, "lines"),
    plot.title = element_text(hjust = 0),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0, face= "italic"),
    legend.position = "right",
    axis.line.y.right = element_line(size=0)
  )

## Generate aligned plot
plot_grid(g1, g1_matched, g2, ncol=1,  align="v", axis = c("lr"))
```
Cumulative incidence = 1 - Kaplan-Meier estimate for probability of survival in unadjusted models. Steps occur every 5 events.
<br/><br/>

#### Crude incidence rate ratios and hazard ratios over time (table)
```{r}
## Read in table of IRRs
table_irr <- read_rds(here::here("output", "tables", "table_irr_primary_redacted_unmatched_all.rds"))

## Update column names
table_irr <- table_irr %>%
  filter(outcome_clean != "COVID-related A&E admission") %>%
  select(c(period, BNT_n, BNT_events, BNT_personyears, BNT_rate, AZ_n, AZ_events, AZ_personyears, AZ_rate, rr, outcome_clean))
names(table_irr) <- c("Period (days)", "n, BNT (total)", "n, BNT (events)", "person-years, BNT", "rate, BNT", 
                      "n, AZ (total)", "n, AZ (events)", "person-years, AZ", "rate, AZ", 
                      "IRR", "outcome_clean")

## Redact rates if number of events = 0
table_irr$`rate, BNT`[table_irr$`n, BNT (events)`==0] = "--"
table_irr$`rate, AZ`[table_irr$`n, AZ (events)`==0] = "--"

## Generate table of HRs
HR_summary <- model %>% select(model_group, term, estimate, conf.low, conf.high, outcome_clean) %>%
  mutate(
    `HR (95% CI)` = paste0(round(exp(estimate),2)," (",round(exp(conf.low),2),"-",round(exp(conf.high),2),")"),
    `HR (95% CI)` = if_else(`HR (95% CI)`=="NA (NA-NA)", "--", `HR (95% CI)`),
    ) %>%
  select(-c(estimate, conf.low, conf.high)) %>%
  pivot_wider(
    names_from = model_group,
    values_from = `HR (95% CI)` 
    ) %>%
  rename(`Period (days)` = term)

## Merge tables
left_join(table_irr, HR_summary, by = c("Period (days)", "outcome_clean")) %>%
  gt(groupname_col = "outcome_clean") %>%
  tab_spanner(
    label = "BNT162b2",
    columns = c("n, BNT (total)", "n, BNT (events)", "person-years, BNT", "rate, BNT")
  ) %>%
  tab_spanner(
    label = "ChAdOx1-S",
    columns = c("n, AZ (total)", "n, AZ (events)", "person-years, AZ", "rate, AZ")
  ) %>%
  tab_spanner(
    label = "Hazard ratios",
    columns = c("Person-time (unadjusted)", "Person-time (region/date adjusted)", "Person-time (fully adjusted)", "Calendar-time (unadjusted)", "Calendar-time (region/date adjusted)", "Calendar-time (fully adjusted)", "Matched")
  ) %>%
   tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
   tab_options(table.font.size = pct(70)) %>% #table.width = pct(80) 
   tab_footnote(
     footnote = "IRR = incidence rate ratio.",
     locations = cells_column_labels(columns = c("IRR"))
   ) %>%
   cols_width(
     starts_with("Period") ~ px(100),
     starts_with("IRR") ~ px(200),
     ends_with("adjusted") ~ px(200)
     )
```
<br/>Frequencies are rounded to the nearest 5. Data are redacted for any rows with rounded counts or non-counts (relative to the denominator) of >0 and <=10.
<br/><br/>

#### Subgroup analysis - CKD3
```{r, fig.width=21, fig.height=15}
## Function for KM plot in subgroup
subset_km_plot = function(selected_subgroup = "CKD3") {
  ## Collate unmatched survival data
  surv_covid_postest = create_rounded_surv_table(1, subset(data_tte_unmatched, ckd_3cat==selected_subgroup)) %>% mutate(outcome_clean = clean_list[1])
  #surv_covid_emergency = create_rounded_surv_table(2) %>% mutate(outcome_clean = clean_list[2])
  surv_covid_hosp = create_rounded_surv_table(3, subset(data_tte_unmatched, ckd_3cat==selected_subgroup)) %>% mutate(outcome_clean = clean_list[3])
  surv_covid_death = create_rounded_surv_table(4, subset(data_tte_unmatched, ckd_3cat==selected_subgroup)) %>% mutate(outcome_clean = clean_list[4])
  surv_noncovid_death = create_rounded_surv_table(5, subset(data_tte_unmatched, ckd_3cat==selected_subgroup)) %>% mutate(outcome_clean = clean_list[5])
  
  ## Collate across outcomes
  surv_collated = rbind(surv_covid_postest, surv_covid_hosp, surv_covid_death, surv_noncovid_death)
  surv_collated$outcome_clean = factor(surv_collated$outcome_clean, levels = clean_list)
  
  ## Collate matched survival data
  surv_covid_postest_matched = create_rounded_surv_table(1, subset(data_tte_matched, ckd_3cat==selected_subgroup)) %>% mutate(outcome_clean = clean_list[1])
  #surv_covid_emergency_matched = create_rounded_surv_table(2) %>% mutate(outcome_clean = clean_list[2])
  surv_covid_hosp_matched = create_rounded_surv_table(3, subset(data_tte_matched, ckd_3cat==selected_subgroup)) %>% mutate(outcome_clean = clean_list[3])
  surv_covid_death_matched = create_rounded_surv_table(4, subset(data_tte_matched, ckd_3cat==selected_subgroup)) %>% mutate(outcome_clean = clean_list[4])
  surv_noncovid_death_matched = create_rounded_surv_table(5, subset(data_tte_matched, ckd_3cat==selected_subgroup)) %>% mutate(outcome_clean = clean_list[5])
  
  ## Collate across outcomes
  surv_collated_matched = rbind(surv_covid_postest_matched, surv_covid_hosp_matched, surv_covid_death_matched, surv_noncovid_death_matched)
  surv_collated_matched$outcome_clean = factor(surv_collated_matched$outcome_clean, levels = clean_list)
  
  ## Generate KM plot across 4 outcomes
  list(
    g1 = generate_km_plot(surv_collated) + ggtitle("Unmatched") + theme(title = element_text(size=20)) + scale_x_continuous(breaks=postvaxcuts, limits=c(0, max(postvaxcuts)), expand = c(0,0)),
    g1_matched = generate_km_plot(surv_collated_matched) + ggtitle("Matched") + theme(title = element_text(size=20)) + scale_x_continuous(breaks=postvaxcuts, limits=c(0, max(postvaxcuts)), expand = c(0,0))
  )
}

## Function to read in subgroup model outputs
read_in_subgroup_model = function(selected_subgroup="CKD3") {
  ## Read CKD4-5 models in separately owing to failure of COVID-related deaths to converge
  if(selected_subgroup=="CKD4-5") {
    model = rbind(
      read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[1],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[1]),
      read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[3],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[3]),
      #read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[4],"_",selected_subgroup,".rds"))) %>%
      #  mutate(outcome_clean = clean_list[4]),
      read_rds(here::here("output", "model","VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[5],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[5])
      ) %>% 
      mutate(model_group = paste0("Person-time"," (",model_name,")"))
  } else {
    model = rbind(
      read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[1],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[1]),
      read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[3],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[3]),
      read_rds(here::here("output", "model", "VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[4],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[4]),
      read_rds(here::here("output", "model","VE_primary", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[5],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[5])
      ) %>% 
      mutate(model_group = paste0("Person-time"," (",model_name,")"))
  }    
  
  ## Set factor levels
  model$model_name = factor(model$model_name, levels = c("unadjusted", "region/date adjusted", "fully adjusted"))
  model$outcome_clean = factor(model$outcome_clean, levels = clean_list)
  
  ## Remove redacted components from plot
  model$estimate = as.numeric(model$estimate)
  model$conf.low = as.numeric(model$conf.low)
  model$conf.high = as.numeric(model$conf.high)
  model
}

## Function to generate subgroup HR plot
plot_subgroup_HRs = function(subgroup_model_data) {
  ggplot(data = subgroup_model_data) +
      geom_point(size = 2.5, aes(y=exp(estimate), x=model_name, colour=model_name)) +
      geom_linerange(aes(ymin=exp(conf.low), ymax=exp(conf.high), x=model_name, colour=model_name)) +
      geom_hline(aes(yintercept=1), colour='grey') +
      scale_y_log10(
        limits = c(0.25,4),
        breaks=c(0.25, 0.5, 0.67, 1, 1.5, 2, 4),
        sec.axis = dup_axis(name="<- Favours BNT / Favours AZ ->", breaks = NULL)
      ) +
    facet_wrap(.~outcome_clean, nrow=1) +
    scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#7570B3", "#B40F20")) +
    labs(
      y="Hazard ratio (95% CI)",
      x="Time since second dose (days)",
      colour=NULL,
      title=NULL
    ) +
    theme_bw() +
    #geom_text(aes(x = term_midpoint, y = 1, label = redaction), size=6) +
    theme(
      strip.text = element_text(size=20, colour="white"), # set as white to avoid repeating text in aligned plot
      axis.text.y = element_text(size=20),
      axis.text.x = element_blank(),
      axis.title.y.right = element_text(size=18),
      axis.title = element_text(size=20),
      legend.text = element_text(size=20),
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),
      panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      panel.grid.major.x = element_blank(),
      strip.background = element_blank(),
      strip.placement = "outside",
      strip.text.y.left = element_text(angle = 0),
      panel.spacing = unit(0.8, "lines"),
      plot.title = element_text(hjust = 0),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      plot.caption = element_text(hjust = 0, face= "italic"),
      legend.position = "right",
      axis.line.y.right = element_line(size=0)
    )
}

create_subgroup_table = function(selected_subgroup="CKD3", subgroup_model_data) {
  ## Read in table of IRRs
  table_irr <- read_rds(here::here("output", "tables", paste0("table_irr_primary_redacted_unmatched_",selected_subgroup,".rds")))
  
  ## Update column names
  table_irr <- table_irr %>%
    filter(outcome_clean != "COVID-related A&E admission") %>%
    select(c(period, BNT_n, BNT_events, BNT_personyears, BNT_rate, AZ_n, AZ_events, AZ_personyears, AZ_rate, rr, outcome_clean))
  names(table_irr) <- c("Period (days)", "n, BNT (total)", "n, BNT (events)", "person-years, BNT", "rate, BNT", 
                        "n, AZ (total)", "n, AZ (events)", "person-years, AZ", "rate, AZ", 
                        "IRR", "outcome_clean")
  
  ## Generate table of HRs
  HR_summary <- subgroup_model_data %>% select(model_group, term, estimate, conf.low, conf.high, outcome_clean) %>%
    mutate(
      `HR (95% CI)` = paste0(round(exp(estimate),2)," (",round(exp(conf.low),2),"-",round(exp(conf.high),2),")"),
      `HR (95% CI)` = if_else(`HR (95% CI)`=="NA (NA-NA)", "--", `HR (95% CI)`),
      ) %>%
    select(-c(estimate, conf.low, conf.high)) %>%
    pivot_wider(
      names_from = model_group,
      values_from = `HR (95% CI)` 
      ) %>%
    rename(`Period (days)` = term)
  
  ## Merge tables
  left_join(table_irr, HR_summary, by = c("Period (days)", "outcome_clean")) %>%
    gt(groupname_col = "outcome_clean") %>%
    tab_spanner(
      label = "BNT162b2",
      columns = c("n, BNT (total)", "n, BNT (events)", "person-years, BNT", "rate, BNT")
    ) %>%
    tab_spanner(
      label = "ChAdOx1-S",
      columns = c("n, AZ (total)", "n, AZ (events)", "person-years, AZ", "rate, AZ")
    ) %>%
    tab_spanner(
      label = "Hazard ratios",
      columns = c("Person-time (unadjusted)", "Person-time (region/date adjusted)", "Person-time (fully adjusted)")
    ) %>%
     tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
     tab_options(table.font.size = pct(70))
}

km_plots = subset_km_plot("CKD3")
model = read_in_subgroup_model("CKD3")
plot_grid(km_plots$g1, km_plots$g1_matched, plot_subgroup_HRs(model), ncol=1,  align="v", axis = c("lr"))
```
<br/><br/>

```{r}
create_subgroup_table("CKD3", model)
```
<br/><br/>

#### Subgroup analysis - CKD4-5
```{r, fig.width=21, fig.height=15}
km_plots = subset_km_plot("CKD4-5")
model = read_in_subgroup_model("CKD4-5")
plot_grid(km_plots$g1, km_plots$g1_matched, plot_subgroup_HRs(model), ncol=1,  align="v", axis = c("lr"))
```
<br/><br/>

```{r}
create_subgroup_table("CKD4-5", model)
```
<br/>Models failed to converge for COVID-related deaths owing to insufficient event counts.
<br/><br/>

#### Subgroup analysis - RRT
```{r, fig.width=21, fig.height=15}
km_plots = subset_km_plot("RRT (any)")
model = read_in_subgroup_model("RRT")
plot_grid(km_plots$g1, km_plots$g1_matched, plot_subgroup_HRs(model), ncol=1,  align="v", axis = c("lr"))
```
<br/><br/>

```{r}
create_subgroup_table("RRT", model)
```
.