---
title: "Kaplan-Meier and risk ratio plots"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## Import libraries
library('here')
library('tidyverse')
library('readr')
library('tidyr')
library('lubridate')
library('glue')
library('gt')
library('gtsummary')
library('reshape2')
library('kableExtra')
library('cowplot')
library('fs')
library('survival')
library('survminer')
library('scales')
library('stringr')


## Import custom user functions
source(here::here("analysis", "functions.R"))

## Set list of outcomes and date variable names
outcomes <- read_rds(
  here::here("output", "lib", "outcomes.rds")
)
outcome_list = outcomes$short_name
clean_list = outcomes$clean_name
date_list = outcomes$date_name

## Read in primary vaccination cohort data 
data_tte_unmatched <- read_rds(here::here("output", "data", "data_cohort_VE_primary.rds")) %>%
  mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))

data_tte_matched <- read_rds(here::here("output", "data", "data_cohort_VE_primary_matched.rds")) %>%
  mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))

## Import outcome time periods
postvax_list <- read_rds(
  here::here("output", "lib", "postvax_list.rds")
)
postvaxcuts = postvax_list$postvaxcuts
postvax_periods = postvax_list$postvax_periods
lastfupday = max(postvaxcuts)

## Read in booster cohort data for cumulative incidence curves
data_tte_unmatched_boost <- read_rds(here::here("output", "data", "data_cohort_VE_boost.rds")) %>%
  mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))

data_tte_matched_boost <- read_rds(here::here("output", "data", "data_cohort_VE_boost_matched.rds")) %>%
  mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))

## Import outcome time periods
postvax_list_boost <- read_rds(
  here::here("output", "lib", "postboost_list.rds")
)
postvaxcuts_boost = postvax_list_boost$postvaxcuts
postvax_periods_boost = postvax_list_boost$postvax_periods
lastfupday_boost = max(postvaxcuts_boost)

## Set rounding threshold for calculation of KM steps
threshold = 5
```
<br/><br/>

#### Summary of population size by vaccine type and kidney disease status

##### Unmatched primary vaccination cohort
```{r}
round_any(table(data_tte_unmatched$vax2_type_descr, data_tte_unmatched$ckd_5cat), 5)
```

##### Unmatched booster cohort
```{r}
round_any(table(data_tte_unmatched_boost$vax2_type_descr, data_tte_unmatched_boost$ckd_5cat), 5)
```

##### Matched primary vaccination cohort
```{r}
round_any(table(data_tte_matched$vax2_type_descr, data_tte_matched$ckd_5cat), 5)
```

##### Matched booster cohort
```{r}
round_any(table(data_tte_matched_boost$vax2_type_descr, data_tte_matched_boost$ckd_5cat), 5)
```
<br/><br/>

#### Cumulative incidence plots and risk ratios over time

Cumulative incidence = 1 - Kaplan-Meier estimate for probability of survival in unadjusted models. Steps occur every 5 events. <br/><br/>

```{r}
### Functions for data manipulation and plotting 

## Function to create rounded KM survival table, with steps delayed until number of events specified by threshold
create_rounded_surv_table = function(outcome_number, input_data, boost=FALSE) {
  
  if (boost==TRUE) { plot_max = lastfupday_boost } else { plot_max = lastfupday }
  
  data_surv <-
    input_data %>%
    mutate(
      ind_outcome = get(paste0("ind_",outcome_list[outcome_number])),
      tte_outcome = get(paste0("tte_",outcome_list[outcome_number],"_or_censor"))
    ) %>%
    group_by(vax2_type_descr) %>%
    nest() %>%
    mutate(
      n_events = map_int(data, ~sum(.x$ind_outcome, na.rm=TRUE)),
      surv_obj = map(data, ~{
        survfit(Surv(tte_outcome, ind_outcome) ~ 1, data = .x, conf.type="log-log")
      }),
      surv_obj_tidy = map(surv_obj, ~tidy_surv(.x, times=seq_len(plot_max))), # return survival table for each day of follow up
    ) %>%
    select(vax2_type_descr, n_events, surv_obj_tidy) %>%
    unnest(surv_obj_tidy)

  data_surv_rounded <-
    data_surv %>%
    mutate(
      N = plyr::round_any(max(n.risk, na.rm=TRUE),threshold),
      cml.event = cumsum(replace_na(n.event, 0)),
      cml.censor = cumsum(replace_na(n.censor, 0)),
      cml.event = floor_any(cml.event, threshold),
      cml.censor = floor_any(cml.censor, threshold),
      n.event = diff(c(0,cml.event)),
      n.censor = diff(c(0,cml.censor)),
      n.risk = N - lag(cml.event + cml.censor,1,0),
      summand = n.event / ((n.risk - n.event) * n.risk),
      surv = cumprod(1 - n.event / n.risk),
      surv.se = surv * sqrt(cumsum(replace_na(summand, 0))),
      llsurv = log(-log(surv)),
      llsurv.se = sqrt((1 / log(surv)^2) * cumsum(summand)),
      surv.ll = exp(-exp(llsurv + qnorm(0.025)*llsurv.se)),
      surv.ul = exp(-exp(llsurv + qnorm(0.975)*llsurv.se)),
      cum.in = 1 - surv,
      haz = -(surv-lag(surv, 1, 1))/lag(surv, 1, 1), # n.event / (n.risk * interval),
      haz.se = haz * sqrt((n.risk - n.event) / (n.risk* n.event)),
      cml.haz = cumsum(haz),
      cml.haz.se = surv.se/surv,
    ) %>%
    select(
      vax2_type_descr, time, lagtime, leadtime, interval,
      n.risk, n.event, n.censor, summand,
      surv, surv.se, surv.ll, surv.ul,
      haz, haz.se,
      cml.haz, cml.haz.se
    )
  #write.csv(data_surv_rounded, "data_surv_rounded.csv")
  data_surv_rounded
}

## Calculate quantities relating to kaplan-meier curve and their ratio / difference / etc
## Adapted from https://github.com/opensafely/comparative-booster
kmcontrast <- function(data, cuts=NULL){
  
  if(is.null(cuts)){cuts <- unique(c(0,data$time))}
  
  data %>%
    filter(time!=0) %>%
    mutate(treatment = vax2_type_descr) %>% # added to original function
    transmute(
      #!!subgroup_sym, # redacted from original function
      treatment,
      
      time, lagtime, interval,
      period_start = as.integer(as.character(cut(time, cuts, right=TRUE, label=cuts[-length(cuts)]))),
      period_end = as.integer(as.character(cut(time, cuts, right=TRUE, label=cuts[-1]))),
      period = cut(time, cuts, right=TRUE, label=paste0(cuts[-length(cuts)]+1, " - ", cuts[-1])),
      
      n.atrisk = n.risk,
      n.event, n.censor, summand,
      
      cml.persontime = cumsum(n.atrisk*interval),
      cml.event = cumsum(replace_na(n.event, 0)),
      cml.censor = cumsum(replace_na(n.censor, 0)),
      cml.summand = cumsum(summand),
      
      rate = n.event / n.atrisk,
      cml.rate = cml.event / cml.persontime,
      
      surv, surv.se, surv.ll, surv.ul,
      
      risk = 1 - surv,
      risk.se = surv.se,
      risk.ll = 1 - surv.ul,
      risk.ul = 1 - surv.ll,
      
      haz, haz.se,
      cml.haz, cml.haz.se
      
    ) %>%
    # group_by(!!subgroup_sym, treatment, period_start, period_end, period) %>% # original
    group_by(treatment, period_start, period_end, period) %>%
    summarise(
      
      ## time-period-specific quantities
      
      persontime = sum(n.atrisk*interval), # total person-time at risk within time period
      
      n.atrisk = first(n.atrisk), # number at risk at start of time period
      n.event = sum(n.event, na.rm=TRUE), # number of events within time period
      n.censor = sum(n.censor, na.rm=TRUE), # number censored within time period
      
      rate = n.event/persontime, # = weighted.mean(haz, n.atrisk*interval), incidence rate. this is equivalent to a weighted average of the hazard ratio, with time-exposed as the weights
      
      interval = sum(interval), # width of time period
      
      ## quantities calculated from time zero until end of time period
      # these should be the same as the daily values as at the end of the time period
      
      surv = last(surv),
      surv.se = last(surv.se),
      surv.ll = last(surv.ll),
      surv.ul = last(surv.ul),
      
      risk = last(risk),
      risk.se = last(risk.se),
      risk.ll = last(risk.ul),
      risk.ul = last(risk.ll),
      
      cml.haz = last(cml.haz),  # cumulative hazard from time zero to end of time period
      
      cml.rate = last(cml.rate), # event rate from time zero to end of time period
      
      # cml.persontime = last(cml.persontime), # total person-time at risk from time zero to end of time period
      cml.event = last(cml.event), # number of events from time zero to end of time period
      # cml.censor = last(cml.censor), # number censored from time zero to end of time period
      
      # cml.summand = last(cml.summand), # summand used for estimation of SE of survival
      
      .groups="drop"
    ) %>%
    ungroup() %>%
    pivot_wider(
      id_cols= c("period_start", "period_end", "period",  "interval"),
     # id_cols= c(subgroup, "period_start", "period_end", "period",  "interval"),
      names_from=treatment,
      names_glue="{.value}_{treatment}",
      values_from=c(
        
        persontime, n.atrisk, n.event, n.censor,
        rate,
        
        cml.haz,
        surv, surv.se, surv.ll, surv.ul,
        risk, risk.se, risk.ll, risk.ul,
        
        cml.event, cml.rate
      )
    ) %>%
    mutate(
      n.nonevent_BNT = n.atrisk_BNT - n.event_BNT, # _BNT replaces _0 for remaining lines
      n.nonevent_AZ = n.atrisk_AZ - n.event_AZ, # _AZ replaces _1 for remaining lines
      
      
      ## time-period-specific quantities
      
      # hazard ratio, standard error and confidence limits
      
      # incidence rate ratio
      irr = rate_AZ / rate_BNT,
      irr.ln.se = sqrt((1/n.event_BNT) + (1/n.event_AZ)),
      irr.ll = exp(log(irr) + qnorm(0.025)*irr.ln.se),
      irr.ul = exp(log(irr) + qnorm(0.975)*irr.ln.se),
      
      # incidence rate difference
      #ird = rate_AZ - rate_BNT,
      
      ## quantities calculated from time zero until end of time period
      # these should be the same as values calculated on each day of follow up
      
      # survival ratio, standard error, and confidence limits
      kmsr = surv_AZ / surv_BNT,
      #kmsr.ln = log(kmsr),
      kmsr.ln.se = (surv.se_BNT/surv_BNT) + (surv.se_AZ/surv_AZ), #because cmlhaz = -log(surv) and cmlhaz.se = surv.se/surv
      kmsr.ll = exp(log(kmsr) + qnorm(0.025)*kmsr.ln.se),
      kmsr.ul = exp(log(kmsr) + qnorm(0.975)*kmsr.ln.se),
      
      # risk ratio, standard error, and confidence limits, using delta method
      kmrr = risk_AZ / risk_BNT,
      #kmrr.ln = log(kmrr),
      kmrr.ln.se = sqrt((risk.se_AZ/risk_AZ)^2 + (risk.se_BNT/risk_BNT)^2),
      kmrr.ll = exp(log(kmrr) + qnorm(0.025)*kmrr.ln.se),
      kmrr.ul = exp(log(kmrr) + qnorm(0.975)*kmrr.ln.se),
      
      #kmrr.se = (kmrr^2)*((risk.se_AZ/risk_AZ)^2 + (risk.se_BNT/risk_BNT)^2),
      #kmrr.ll2 = kmrr + qnorm(0.025)*kmrr.se,
      #kmrr.ul2 = kmrr + qnorm(0.975)*kmrr.se,
      
      
      # risk difference, standard error and confidence limits
      kmrd = risk_AZ - risk_BNT,
      #kmrd.se = sqrt( ((n.event_AZ*n.nonevent_AZ)/(n.atrisk_AZ^3)) + ((n.event_BNT*n.nonevent_BNT)/(n.atrisk_BNT^3)) ), # ignores censoring
      kmrd.se = sqrt( (risk.se_BNT^2) + (risk.se_AZ^2) ), # combining SEs from greenwood's formula
      kmrd.ll = kmrd + qnorm(0.025)*kmrd.se,
      kmrd.ul = kmrd + qnorm(0.975)*kmrd.se,
      
      
      # cumulative incidence rate ratio
      cmlirr = cml.rate_AZ / cml.rate_BNT,
      cmlirr.ln.se = sqrt((1/cml.event_BNT) + (1/cml.event_AZ)),
      cmlirr.ll = exp(log(cmlirr) + qnorm(0.025)*cmlirr.ln.se),
      cmlirr.ul = exp(log(cmlirr) + qnorm(0.975)*cmlirr.ln.se),
      
      # cumulative incidence rate difference
      #cmlird = cml.rate_AZ - cml.rate_BNT
    )
}

## Generate KM plot across 4 outcomes
generate_km_plot = function(surv_data) {
  
  surv_data %>%
    ggplot(aes(x = time, y = 1-surv, colour = vax2_type_descr, fill = vax2_type_descr)) + geom_step(size = 0.5) +
    facet_grid(outcome_clean~dose, scales="free", space="free_x") +
    geom_rect(aes(xmin=lagtime, xmax=time, ymin=1-surv.ll, ymax=1-surv.ul), alpha=0.1, colour="transparent") +
    scale_x_continuous(breaks=postvaxcuts, expand = c(0, 0)) +
    scale_y_continuous(expand = expansion(mult=c(0,0.01))) +
    labs(
      x="Time since vaccination (days)",
      y = "Cumulative incidence",
      colour = "Vaccine (primary course)",
      title = "") +
    theme_bw() +
    guides(fill="none") +
    scale_colour_manual(values = c("#CC79A7", "#0072B2")) +
    scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
    theme(
      strip.text.x = element_text(size=15), 
      strip.text.y = element_text(size=12),   
      axis.title.y.left = element_text(size=15, margin = margin(t = 0, r = 10, b = 0, l = 0)),
      axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
      axis.text = element_text(size=13),
      axis.title = element_text(size=15),
      legend.text = element_text(size=15),
      legend.title = element_text(size=15),
      panel.border = element_blank(),
      axis.line.y = element_line(colour = "black"),
      panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      strip.background = element_blank(),
      strip.placement = "outside",
      strip.text.y.left = element_text(angle = 0),
      panel.spacing = unit(2, "lines"),
      plot.title = element_text(hjust = 0),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      plot.caption = element_text(hjust = 0, face= "italic"),
      legend.position = "top",
      plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm")
      )
}

## Generate KM plot across 4 outcomes
generate_km_contrast_plot = function(surv_contrast) {
  
  # surv_contrast$kmrr[surv_contrast$kmrr>4] = 4
  # surv_contrast$kmrr[surv_contrast$kmrr<0.25] = 0.25
  ## Limit CIs to 0.25/4
  surv_contrast$kmrr.ul[surv_contrast$kmrr.ul>4] = 4
  surv_contrast$kmrr[surv_contrast$kmrr.ll<0.25] = 0.25
  
  surv_contrast %>%
    filter(period_start>=14) %>%
    ggplot(aes(x = period_start, y = kmrr)) + geom_step(size = 0.5, colour="#023858") +
    facet_grid(outcome_clean~dose, scales="free", space="free_x") +
    geom_rect(aes(xmin=period_start, xmax=period_end, ymin=kmrr.ll, ymax=kmrr.ul), alpha=0.1, colour="transparent", fill = "#023858") +
    geom_hline(aes(yintercept=1), colour='black', linetype="dotted", size=0.5) +
    scale_x_continuous(breaks=postvaxcuts, expand = c(0, 0)) +
    scale_y_log10(
      limits = c(0.25,4),
      breaks=c(0.25, 0.5, 1, 2, 4),
      sec.axis = dup_axis(name="<- Favours BNT-BNT primary / Favours AZ-AZ primary ->", breaks = NULL)
    ) +
    labs(
      x="Time since vaccination (days)",
      y = "Risk ratio",
      colour = "",
      title = "") +
    theme_bw() +
    guides(fill="none") +
    #scale_colour_manual(values = c("#CC79A7", "#0072B2")) +
    #scale_fill_manual(values = c("#CC79A7", "#0072B2")) +
    theme(
      strip.text.x = element_text(size=15), 
      strip.text.y = element_text(size=12),   
      axis.title.y.left = element_text(size=15, margin = margin(t = 0, r = 10, b = 0, l = 0)),
      axis.title.y.right = element_text(size=15, margin = margin(t = 0, r = 0, b = 0, l = 20)),
      axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
      axis.text = element_text(size=13),
      axis.title = element_text(size=15),
      legend.text = element_text(size=15),
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),
      panel.grid.minor.x = element_blank(),
      panel.grid.minor.y = element_blank(),
      strip.background = element_blank(),
      strip.placement = "outside",
      strip.text.y.left = element_text(angle = 0),
      panel.spacing = unit(2, "lines"),
      plot.title = element_text(hjust = 0),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      plot.caption = element_text(hjust = 0, face= "italic"),
      legend.position = "right",
      plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm")
      )
}

## Function to collate rounded survival tables 
collate_rounded_km = function(data_tte_primary, data_tte_boost) {
  
  ## Collate primary vaccination cohort data 
  surv_covid_postest = create_rounded_surv_table(1, data_tte_primary, boost=FALSE) %>% mutate(outcome_clean = clean_list[1])
  surv_covid_hosp = create_rounded_surv_table(3, data_tte_primary, boost=FALSE) %>% mutate(outcome_clean = clean_list[3])
  surv_covid_death = create_rounded_surv_table(4, data_tte_primary, boost=FALSE) %>% mutate(outcome_clean = clean_list[4])
  surv_noncovid_death = create_rounded_surv_table(5, data_tte_primary, boost=FALSE) %>% mutate(outcome_clean = clean_list[5])
  surv_collated = rbind(surv_covid_postest, surv_covid_hosp, surv_covid_death, surv_noncovid_death) %>% mutate(dose = "Primary vaccination")
  surv_collated$outcome_clean = factor(surv_collated$outcome_clean, levels = clean_list)
  
  ## Collate booster cohort data 
  surv_covid_postest_boost = create_rounded_surv_table(1, data_tte_boost, boost=TRUE) %>% mutate(outcome_clean = clean_list[1])
  surv_covid_hosp_boost = create_rounded_surv_table(3, data_tte_boost, boost=TRUE) %>% mutate(outcome_clean = clean_list[3])
  surv_covid_death_boost = create_rounded_surv_table(4, data_tte_boost, boost=TRUE) %>% mutate(outcome_clean = clean_list[4])
  surv_noncovid_death_boost = create_rounded_surv_table(5, data_tte_boost, boost=TRUE) %>% mutate(outcome_clean = clean_list[5])
  surv_collated_boost = rbind(surv_covid_postest_boost, surv_covid_hosp_boost, surv_covid_death_boost, surv_noncovid_death_boost) %>% mutate(dose = "BNT boost")
  surv_collated_boost$outcome_clean = factor(surv_collated_boost$outcome_clean, levels = clean_list)
  
  ## Collate across doses
  surv_combined = rbind(surv_collated, surv_collated_boost)
  surv_combined$dose = factor(surv_combined$dose, levels = unique(surv_combined$dose))
  
  ## Simplify outcome names for plotting
  surv_combined$outcome_clean <- recode_factor(surv_combined$outcome_clean, 
                                               `Positive SARS-CoV-2 test` = "SARS-CoV-2+", 
                                               `COVID-19-related hospitalisation` = "COVID-19 hosp.",
                                               `COVID-19-related death` = "COVID-19 death") 
  return(surv_combined)
}

## Function to collate contrast data
collate_km_contrasts = function(data_tte_primary, data_tte_boost) {
  
  ## Collate primary vaccination cohort data 
  surv_covid_postest_contrast = kmcontrast(create_rounded_surv_table(1, data_tte_primary, boost=FALSE)) %>% mutate(outcome_clean = clean_list[1])
  surv_covid_hosp_contrast = kmcontrast(create_rounded_surv_table(3, data_tte_primary, boost=FALSE)) %>% mutate(outcome_clean = clean_list[3])
  surv_covid_death_contrast = kmcontrast(create_rounded_surv_table(4, data_tte_primary, boost=FALSE)) %>% mutate(outcome_clean = clean_list[4])
  surv_noncovid_death_contrast = kmcontrast(create_rounded_surv_table(5, data_tte_primary, boost=FALSE)) %>% mutate(outcome_clean = clean_list[5])
  surv_collated_contrast = rbind(surv_covid_postest_contrast, surv_covid_hosp_contrast, surv_covid_death_contrast, surv_noncovid_death_contrast) %>% mutate(dose = "Primary vaccination")
  surv_collated_contrast$outcome_clean = factor(surv_collated_contrast$outcome_clean, levels = clean_list)
  
  ## Collate booster cohort data 
  surv_covid_postest_contrast_boost = kmcontrast(create_rounded_surv_table(1, data_tte_boost, boost=TRUE)) %>% mutate(outcome_clean = clean_list[1])
  surv_covid_hosp_contrast_boost = kmcontrast(create_rounded_surv_table(3, data_tte_boost, boost=TRUE)) %>% mutate(outcome_clean = clean_list[3])
  surv_covid_death_contrast_boost = kmcontrast(create_rounded_surv_table(4, data_tte_boost, boost=TRUE)) %>% mutate(outcome_clean = clean_list[4])
  surv_noncovid_death_contrast_boost = kmcontrast(create_rounded_surv_table(5, data_tte_boost, boost=TRUE)) %>% mutate(outcome_clean = clean_list[5])
  surv_collated_contrast_boost = rbind(surv_covid_postest_contrast_boost, surv_covid_hosp_contrast_boost, surv_covid_death_contrast_boost, surv_noncovid_death_contrast_boost) %>% mutate(dose = "BNT boost")
  surv_collated_contrast_boost$outcome_clean = factor(surv_collated_contrast_boost$outcome_clean, levels = clean_list)
  
  ## Collate across doses
  surv_combined_contrast = rbind(surv_collated_contrast, surv_collated_contrast_boost)
  surv_combined_contrast$dose = factor(surv_combined_contrast$dose, levels = unique(surv_combined_contrast$dose))
  
  ## Simplify outcome names for plotting
  surv_combined_contrast$outcome_clean <- recode_factor(surv_combined_contrast$outcome_clean, 
                                               `Positive SARS-CoV-2 test` = "SARS-CoV-2+", 
                                               `COVID-19-related hospitalisation` = "COVID-19 hosp.",
                                               `COVID-19-related death` = "COVID-19 death") 
  return(surv_combined_contrast)
}
```

##### Whole population - unmatched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(data_tte_unmatched, data_tte_unmatched_boost)
surv_contrasts = collate_km_contrasts(data_tte_unmatched, data_tte_unmatched_boost)
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### Whole population - matched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(data_tte_matched, data_tte_matched_boost)
surv_contrasts = collate_km_contrasts(data_tte_matched, data_tte_matched_boost)
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### CKD3 - unmatched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(subset(data_tte_unmatched, ckd_3cat=="CKD3"), subset(data_tte_unmatched_boost, ckd_3cat=="CKD3"))
surv_contrasts = collate_km_contrasts(subset(data_tte_unmatched, ckd_3cat=="CKD3"), subset(data_tte_unmatched_boost, ckd_3cat=="CKD3"))
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### CKD3 - matched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(subset(data_tte_matched, ckd_3cat=="CKD3"), subset(data_tte_matched_boost, ckd_3cat=="CKD3"))
surv_contrasts = collate_km_contrasts(subset(data_tte_matched, ckd_3cat=="CKD3"), subset(data_tte_matched_boost, ckd_3cat=="CKD3"))
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### CKD4-5 - unmatched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(subset(data_tte_unmatched, ckd_3cat=="CKD4-5"), subset(data_tte_unmatched_boost, ckd_3cat=="CKD4-5"))
surv_contrasts = collate_km_contrasts(subset(data_tte_unmatched, ckd_3cat=="CKD4-5"), subset(data_tte_unmatched_boost, ckd_3cat=="CKD4-5"))
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### CKD4-5 - matched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(subset(data_tte_matched, ckd_3cat=="CKD4-5"), subset(data_tte_matched_boost, ckd_3cat=="CKD4-5"))
surv_contrasts = collate_km_contrasts(subset(data_tte_matched, ckd_3cat=="CKD4-5"), subset(data_tte_matched_boost, ckd_3cat=="CKD4-5"))
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### RRT (any) - unmatched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(subset(data_tte_unmatched, ckd_3cat=="RRT (any)"), subset(data_tte_unmatched_boost, ckd_3cat=="RRT (any)"))
surv_contrasts = collate_km_contrasts(subset(data_tte_unmatched, ckd_3cat=="RRT (any)"), subset(data_tte_unmatched_boost, ckd_3cat=="RRT (any)"))
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### RRT (any) - matched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(subset(data_tte_matched, ckd_3cat=="RRT (any)"), subset(data_tte_matched_boost, ckd_3cat=="RRT (any)"))
surv_contrasts = collate_km_contrasts(subset(data_tte_matched, ckd_3cat=="RRT (any)"), subset(data_tte_matched_boost, ckd_3cat=="RRT (any)"))
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### RRT (Tx) - unmatched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(subset(data_tte_unmatched, ckd_5cat=="RRT (Tx)"), subset(data_tte_unmatched_boost, ckd_5cat=="RRT (Tx)"))
surv_contrasts = collate_km_contrasts(subset(data_tte_unmatched, ckd_5cat=="RRT (Tx)"), subset(data_tte_unmatched_boost, ckd_5cat=="RRT (Tx)"))
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```
<br><br>

##### RRT (Tx) - matched

```{r fig.width=14, fig.height=9}
surv_combined = collate_rounded_km(subset(data_tte_matched, ckd_5cat=="RRT (Tx)"), subset(data_tte_matched_boost, ckd_5cat=="RRT (Tx)"))
surv_contrasts = collate_km_contrasts(subset(data_tte_matched, ckd_5cat=="RRT (Tx)"), subset(data_tte_matched_boost, ckd_5cat=="RRT (Tx)"))
plot_grid(generate_km_plot(surv_combined), 
          generate_km_contrast_plot(surv_contrasts),
          ncol=2, align = "h", axis = "tb")
```

#### Hazard ratios - whole population
See *cox_VE_primary_summary.html* and *cox_VE_boost_summary.html* for tabulated values.

```{r fig.width=9, fig.height=9}
## Read in primary model outputs
primary <- read_csv(here::here("output", "tables", "irr_hr_summary_VE_primary.csv")) %>%
  pivot_longer(c(starts_with("Person-time"), starts_with("Calendar-time"), starts_with("Matched")), 
                         names_to = "model", values_to = "HR_CI")  %>%
  separate(HR_CI, c('HR','CI'), sep = '\\ \\(') %>%
  separate(CI, c('lowerCI','upperCI'), sep = '-') %>%
  separate(upperCI, c('upperCI','bracket'), sep = '\\)') %>%
  select(-bracket) %>%
  mutate(HR = as.numeric(HR), lowerCI = as.numeric(lowerCI), upperCI = as.numeric(upperCI), 
         dose = "Primary vaccination", 
         period_alt = ifelse(`Period (days)` == "15-182", "All", `Period (days)`))

## Read in booster model outputs
boost <- read_csv(here::here("output", "tables", "irr_hr_summary_VE_boost.csv")) %>%
  pivot_longer(c(starts_with("Person-time"), starts_with("Calendar-time"), starts_with("Matched")), 
                         names_to = "model", values_to = "HR_CI")  %>%
  separate(HR_CI, c('HR','CI'), sep = '\\ \\(') %>%
  separate(CI, c('lowerCI','upperCI'), sep = '-') %>%
  separate(upperCI, c('upperCI','bracket'), sep = '\\)') %>%
  select(-bracket) %>%
  mutate(HR = as.numeric(HR), lowerCI = as.numeric(lowerCI), upperCI = as.numeric(upperCI), 
         dose = "BNT boost", 
         period_alt = ifelse(`Period (days)` == "15-126", "All", `Period (days)`))

## Collate 
d = rbind(primary, boost)
d$model[d$model=="Person-time (unadjusted)"] = "Unadjusted"
d$model[d$model=="Person-time (region/date adjusted)"] = "Region/date adjusted"
d$model[d$model=="Person-time (fully adjusted)"] = "Fully adjusted"
d$model[d$model=="Calendar-time (fully adjusted)"] = "Calendar-time"
d$model = factor(d$model, levels = unique(d$model))
d$outcome_clean[d$outcome_clean=="Positive SARS-CoV-2 test"] = "SARS-CoV-2+"
d$outcome_clean[d$outcome_clean=="COVID-related hospitalisation"] = "COVID-19 hosp."
d$outcome_clean[d$outcome_clean=="COVID-related death"] = "COVID-19 death"
d$outcome = factor(d$outcome_clean, levels = unique(d$outcome_clean))
d$period_alt = factor(d$period_alt, levels = unique(d$period_alt))
d$dose = factor(d$dose, levels = unique(d$dose))

## Read in data for cumulative incidence curves
ggplot(data = d) +
  geom_point(size = 2.5, aes(y=HR, x=factor(period_alt), colour=model), alpha = 0.8, position = position_dodge(width = 0.6)) +
  geom_linerange(aes(ymin=lowerCI, ymax=upperCI, x=factor(period_alt), colour=model), alpha = 1, position = position_dodge(width = 0.6)) +
  geom_hline(aes(yintercept=1), colour='grey') +
  theme_bw()+
  facet_grid(outcome~dose, scales="free_x", space="free_x") +
    scale_y_log10(
      limits = c(0.25,4),
      breaks=c(0.25, 0.5, 1, 2, 4),
      sec.axis = dup_axis(name="<- Favours BNT-BNT primary / Favours AZ-AZ primary ->", breaks = NULL)
    ) + 
  #scale_x_continuous(breaks=c(0,14,70,126,182), expand = c(0, 0)) +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#7570B3", "#B40F20", "grey")) +
  labs(
    y="Hazard ratio (95% CI)",
    x="Time since vaccination (days)",
    colour=NULL,
    title=NULL
  ) +
  #annotate("rect", xmin = lastfupday, xmax =  lastfupday+period_length, ymin = 0.25, ymax = 4, alpha = .3, fill = "grey") +
  #annotate("text", x =lastfupday+period_length/2, y = 3.3, label = "All", size=7) +
  #geom_text(aes(x = term_midpoint, y = 1, label = redaction), size=6) +
  theme(
    strip.text.x = element_text(size=12), # set as white to avoid repeating text in aligned plot
    strip.text.y = element_text(size=10), # set as white to avoid repeating text in aligned plot
    axis.text = element_text(size=12),
    axis.title.y.left = element_text(size=12, margin = margin(t = 0, r = 10, b = 0, l = 0)),
    axis.title.y.right = element_text(size=10, margin = margin(t = 0, r = 0, b = 0, l = 20)),
    axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
    axis.title = element_text(size=12),
    legend.text = element_text(size=12),
    panel.border = element_blank(),
    axis.line.x = element_line(colour = "black"),
    axis.line.y = element_line(colour = "black"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(hjust = 0),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0, face= "italic"),
    legend.position = "right",
    axis.line.y.right = element_line(size=0)
  )
```
<br/><br/>

#### Hazard ratios - subgroups
See *cox_VE_primary_summary.html* and *cox_VE_boost_summary.html* for tabulated values.

```{r fig.width=5, fig.height=8}
## Read in primary model outputs
primary <- read_csv(here::here("output", "tables", "irr_hr_summary_VE_primary_subgroups.csv")) %>%
  separate(`HR (95% CI)`, c('HR','CI'), sep = '\\ \\(') %>%
  separate(CI, c('lowerCI','upperCI'), sep = '-') %>%
  separate(upperCI, c('upperCI','bracket'), sep = '\\)') %>%
  select(-bracket) %>%
  mutate(HR = as.numeric(HR), lowerCI = as.numeric(lowerCI), upperCI = as.numeric(upperCI), 
         dose = "Primary vaccination")

## Read in booster model outputs
boost <- read_csv(here::here("output", "tables", "irr_hr_summary_VE_boost_subgroups.csv")) %>%
  separate(`HR (95% CI)`, c('HR','CI'), sep = '\\ \\(') %>%
  separate(CI, c('lowerCI','upperCI'), sep = '-') %>%
  separate(upperCI, c('upperCI','bracket'), sep = '\\)') %>%
  select(-bracket) %>%
  mutate(HR = as.numeric(HR), lowerCI = as.numeric(lowerCI), upperCI = as.numeric(upperCI), 
         dose = "BNT boost")

## Collate 
d = rbind(primary, boost)
d$outcome_clean[d$outcome_clean=="Positive SARS-CoV-2 test"] = "SARS-CoV-2+"
d$outcome_clean[d$outcome_clean=="COVID-19-related hospitalisation"] = "COVID-19 hosp."
d$outcome_clean[d$outcome_clean=="COVID-19-related death"] = "COVID-19 death"
d$Dose = factor(d$dose, levels = unique(d$dose))
d$Outcome = factor(d$outcome_clean, levels = unique(d$outcome_clean))
d$Subgroup[d$Subgroup=="all"] = "All"
d$Subgroup[d$Subgroup=="RRT"] = "RRT (any)"
d$Subgroup[d$Subgroup=="Tx"] = "RRT (Tx)"
d$Subgroup = factor(d$Subgroup, levels = unique(d$Subgroup))

## Render plot
ggplot(data = d) +
  geom_point(size = 2.5, aes(y=HR, x=factor(Subgroup), colour=Subgroup), alpha = 0.8, position = position_dodge(width = 0.6)) +
  geom_linerange(aes(ymin=lowerCI, ymax=upperCI, x=factor(Subgroup), colour=Subgroup), alpha = 1, position = position_dodge(width = 0.6)) +
  geom_hline(aes(yintercept=1), colour='grey') +
  theme_bw() +
  facet_grid(Outcome~Dose, scales="free_x", space="free_x") +
    scale_y_log10(
      limits = c(0.25,4),
      breaks=c(0.25, 0.5, 1, 2, 4),
      sec.axis = dup_axis(name="<- Favours BNT-BNT primary / Favours AZ-AZ primary ->", breaks = NULL)
    ) + 
  #scale_x_continuous(breaks=c(0,14,70,126,182), expand = c(0, 0)) +
  scale_colour_manual(values = c("#993404", "#3690c0", "#0570b0", "#045a8d", "#023858")) +
  labs(
    y="Hazard ratio (95% CI)",
    x="",
    colour=NULL,
    title=NULL
  ) +
  #annotate("rect", xmin = lastfupday, xmax =  lastfupday+period_length, ymin = 0.25, ymax = 4, alpha = .3, fill = "grey") +
  #annotate("text", x =lastfupday+period_length/2, y = 3.3, label = "All", size=7) +
  #geom_text(aes(x = term_midpoint, y = 1, label = redaction), size=6) +
  theme(
    strip.text.x = element_text(size=12), # set as white to avoid repeating text in aligned plot
    strip.text.y = element_text(size=10), # set as white to avoid repeating text in aligned plot
    axis.text = element_text(size=12),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.title.y.left = element_text(size=12, margin = margin(t = 0, r = 10, b = 0, l = 0)),
    axis.title.y.right = element_text(size=10, margin = margin(t = 0, r = 0, b = 0, l = 20)),
    axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
    axis.title = element_text(size=12),
    legend.text = element_text(size=12),
    panel.border = element_blank(),
    axis.line.x = element_line(colour = "black"),
    axis.line.y = element_line(colour = "black"),
    panel.grid.minor.x = element_blank(),
    panel.grid.minor.y = element_blank(),
    strip.background = element_blank(),
    strip.placement = "outside",
    strip.text.y.left = element_text(angle = 0),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(hjust = 0),
    plot.title.position = "plot",
    plot.caption.position = "plot",
    plot.caption = element_text(hjust = 0, face= "italic"),
    legend.position = "none",
    axis.line.y.right = element_line(size=0)
  )
```
.
