---
title: "Comparative effectiveness of BNT162b2 boost following BNT162b2 vs ChAdOx1-S primary series in people with kidney disease"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
## Import libraries
library('here')
library('tidyverse')
library('readr')
library('tidyr')
library('lubridate')
library('glue')
library('gt')
library('gtsummary')
library('reshape2')
library('kableExtra')
library('cowplot')
library('fs')
library('survival')
library('survminer')
library('scales')

## Import custom user functions
source(here::here("analysis", "functions.R"))

## Set list of outcomes and date variable names
outcomes <- read_rds(
  here::here("output", "lib", "outcomes_boost.rds")
)
outcome_list = outcomes$short_name
clean_list = outcomes$clean_name
date_list = outcomes$date_name

## Read in data for cumulative incidence curves
data_tte_unmatched <- read_rds(here::here("output", "data", "data_cohort_VE_boost.rds")) %>%
  mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))

data_tte_matched <- read_rds(here::here("output", "data", "data_cohort_VE_boost_matched.rds")) %>%
  mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))

## Import outcome time periods
postvax_list <- read_rds(
  here::here("output", "lib", "postboost_list.rds")
)
postvaxcuts = postvax_list$postvaxcuts
postvax_periods = postvax_list$postvax_periods
period_length = postvaxcuts[2]-postvaxcuts[1]
lastfupday = max(postvaxcuts)

## Set rounding threshold for calculation of KM steps
threshold = 5

## Calculated total cohort size rounded to nearest 5
rounded_n_unmatched = plyr::round_any(nrow(data_tte_unmatched), 5)
rounded_n_matched = plyr::round_any(nrow(data_tte_matched), 5)
```
<br/><br/>  

#### Background
Kidney disease is a significant risk factor for COVID-19-related mortality. Although vaccination has the potential to mitigate this risk, chronic kidney disease (CKD) and kidney failure requiring renal replacement therapy (RRT) have been linked with impaired COVID-19 vaccine immunogenicity and high rates of post-vaccination infection among individuals who have received a 2-dose primary vaccine series.

Vaccine recommendations for people with kidney disease in the UK have evolved over time (see [protocol](https://docs.google.com/document/d/1w48W-bCMfn0RdkfxlU6fbRkPv3MnIYd3/edit#heading=h.1fob9te). Relative uptake of different vaccines in this population has been described in our recent [preprint](https://www.medrxiv.org/content/10.1101/2022.06.14.22276391v1). However, the relative vaccine effectiveness (VE) of different regimens remains uncertain. This project seeks to address this key evidence gap.

Most people with kidney disease received a 2-dose homologous primary series of either BNT162b2 or ChAdOx1-S between January and June 2021 (see Supplementary Table 1 of [coverage preprint](https://www.medrxiv.org/content/10.1101/2022.06.14.22276391v1)). Subsequently, individuals received a third primary or first booster dose of an RNA vaccine (either BNT162b2 or ChAdOx1-S). The primary comparison of interest in the present study was post-vaccination outcomes for BNT162b2 vs ChAdOx1-S, with outcomes after receipt of BNT162b2 booster doses as a secondary analyses.
<br/><br/>

#### Inclusion criteria for booster cohort
* Registered for at least 3m before booster dose 
* Aged ≥16 as of 31-Mar-2021
* eGFR<60 in 2 years before booster dose OR present in UK Renal Registry (UKRR) on 31-Dec-2020 (the status update closest to the index date)  
* No RRT mismatch (primary care dialysis/Tx code but absent from UKRR 2020 population)
* No missing demographic data   
* Received 2 x ChAdOx1-S or 2 x BNT162b2 as first two vaccine doses followed by BNT162b2 boost
* Received first dose on or after 04-Jan-2021 (the period in which vaccines were in use) and third dose on or after 01-Sep-2021
* Dose 1-2 interval was in the range of 8-14 weeks and dose 2-3 interval was >=12 weeks
* Not a healthcare worker, care home resident, receiving end-of-life care, housebound, or in JCVI priority group 2
* Events designated as post-vaccination outcomes occurred after the date of the second dose
* No SARS-CoV-2 infection in the interval dose 1 to dose 3 (to mitigate the impact of hybrid immunity)

### Matching criteria for matched cohort
* Region   
* Age (within 3y)      
* Dose 3 date (within 3d)         
* Dose 2 date (within 14d)         
* JCVI group    
* IMD    
* Ethnicity    
* Kidney disease category (CDK3a, CKD3b, CKD4-5, dialysis, Tx)    
* Clinically extremely vulnerable    
* Prior SARS-CoV-2
* Any indicator of immunosuppression (imunosuppressive condition, recent immunosuppressive medication, asplenia, transplant, or haematologic malignancy)

#### Cohort selection - unmatched
```{r}
flowchart <- read.csv(here::here("output", "tables", "flowchart_VE_boost.csv"))
names(flowchart)[1] = "Criteria"

# Render flowchart
flowchart %>%
  mutate(`N (rounded)` = prettyNum(plyr::round_any(flowchart$n, 5), big.mark=",")) %>%
  select(Criteria, `N (rounded)`) %>%
  gt() %>%
  tab_options(table.font.size = pct(95), column_labels.font.weigh="bold")
```
<br/><br/>

#### Cohort selection - unmatched
Of the **`r prettyNum(rounded_n_unmatched)`** individuals in the unmatched cohort (see above), **`r prettyNum(rounded_n_matched)`** were selected for the matched cohort (see matching criteria above).
<br/><br/>

#### Table 1: Summary of primary outcome population
```{r}
table_1 <- rbind(
  read_rds(here::here("output", "tables", "table1_VE_boost_redacted_unmatched_all.rds")) %>% mutate(subgroup = "All", subgroup_id = 1),
  read_rds(here::here("output", "tables", "table1_VE_boost_redacted_matched_all.rds")) %>% mutate(subgroup = "Matched (all)", subgroup_id = 2),
  read_rds(here::here("output", "tables", "table1_VE_boost_redacted_unmatched_CKD3.rds")) %>% mutate(subgroup = "CKD3", subgroup_id = 3),
  read_rds(here::here("output", "tables", "table1_VE_boost_redacted_unmatched_CKD4-5.rds")) %>% mutate(subgroup = "CKD4-5", subgroup_id = 4),
  read_rds(here::here("output", "tables", "table1_VE_boost_redacted_unmatched_RRT.rds")) %>% mutate(subgroup = "RRT (any)", subgroup_id = 5),
  read_rds(here::here("output", "tables", "table1_VE_boost_redacted_unmatched_Tx.rds")) %>% mutate(subgroup = "RRT (Tx)", subgroup_id = 6),
  read_rds(here::here("output", "tables", "table1_VE_boost_redacted_unmatched_dialysis.rds")) %>% mutate(subgroup = "RRT (dialysis)", subgroup_id = 7)
)

table_1_wide = table_1 %>% 
    pivot_wider(    
      names_from = c(subgroup, subgroup_id),
      values_from = c(`ChAdOx1-S`, `BNT162b2`),
      names_glue = "{.value} [{subgroup_id}]"
    ) 

## Generate table
table_1_wide %>%
    gt(rowname_col = "Variable", groupname_col = "Group") %>%
    tab_spanner(
      label = "Unmatched",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [1]")
    ) %>%
     tab_spanner(
      label = "Matched",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [2]")
    ) %>%
    tab_spanner(
      label = "CKD3 subgroup (unmatched)",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [3]")
    ) %>%
    tab_spanner(
      label = "CKD4-5 subgroup (unmatched)",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [4]")
    ) %>%
    tab_spanner(
      label = "RRT (any) subgroup (unmatched)",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [5]")
    ) %>%
    tab_spanner(
      label = "RRT (Tx) subgroup (unmatched)",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [6]")
    ) %>%
    tab_spanner(
      label = "RRT (dialysis) subgroup (unmatched)",
      columns = paste0(c("ChAdOx1-S", "BNT162b2")," [7]")
    ) %>%

    tab_options(table.font.size = pct(70)) %>%
     tab_style(
        style = list(
          cell_borders(
            sides = c("right"), color = "#cccccc"
          )
          ),
        locations = list(
          cells_body(
            columns = starts_with("BNT")
          )
        )
     ) %>%
    tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
    tab_style(
       style = cell_text(indent = pct(5)),
       locations = cells_body(columns = "Variable")
     )
```
Data are n (%) after rounding to the nearest 5. Any cells with rounded counts or non-counts (relative to the denominator) of >0 and <=10 are redacted. Primary care codes and risk groups are coded by separate binary variables; percentages in these subheadings therefore do not sum to 100. **Prior SARS-CoV-2** was determined based on evidence of a positive SARS-CoV-2 test, COVID-19-related primary care code, COVID-19-related A&E admission, or COVID-19-related hospitalisation as of the booster dose. JCVI group was inferred based on age and shielding code lists (to define **Clinically extremely vulnerable** individuals). **Comorbidity count** includes severe obesity, chronic heart disease, diabetes, chronic liver disease, any respiratory disease (including asthma), and chronic neurological disease. CKD, chronic kidney disease; CND, chronic neurological disease; RRT, renal replacement therapy. 
<br/><br/>

#### Cumulative incidence plots
See outputs of *km_rr_plots.Rmd* script for Kaplan-Meier and risk ratio plots.

#### Crude incidence rate ratios and hazard ratios over time (table)
```{r, fig.width=21, fig.height=15}
## Read in persontime models
model_persontime = rbind(
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[1],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[1]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[3],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[3]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[4],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[4]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[5],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[5])
  ) %>% 
  mutate(model_group = paste0("Person-time"," (",model_name,")"))

## Read in calendartime models
model_calendartime = rbind(
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_calendartime_",outcome_list[1],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[1]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_calendartime_",outcome_list[3],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[3]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_calendartime_",outcome_list[4],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[4]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_calendartime_",outcome_list[5],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[5])
  ) %>% 
  mutate(model_group = paste0("Calendar-time"," (",model_name,")"))

## Read in matched models
model_matched = rbind(
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_matched_persontime_",outcome_list[1],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[1]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_matched_persontime_",outcome_list[3],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[3]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_matched_persontime_",outcome_list[4],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[4]),
  read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_matched_persontime_",outcome_list[5],"_all.rds"))) %>%
    mutate(outcome_clean = clean_list[5])
  ) %>% 
  mutate(model_group = "Matched")

## Collated models
model = rbind(model_persontime, model_calendartime, model_matched)

## Set factor levels
model$model_name = factor(model$model_name, levels = c("unadjusted", "region/date adjusted", "fully adjusted"))
model$outcome_clean = factor(model$outcome_clean, levels = clean_list)

## Remove redacted components from plot
model$estimate = as.numeric(model$estimate)
model$conf.low = as.numeric(model$conf.low)
model$conf.high = as.numeric(model$conf.high)

## Read in table of IRRs
table_irr <- read_rds(here::here("output", "tables", "table_irr_boost_redacted_unmatched_all.rds"))
table_irr_matched <- read_rds(here::here("output", "tables", "table_irr_boost_redacted_matched_all.rds"))

## Append matched counts (total/events)
if (all(table_irr$period==table_irr_matched$period) & all(table_irr$outcome==table_irr_matched$outcome)) {
  table_irr$BNT_n_matched = table_irr_matched$BNT_n
  table_irr$BNT_events_matched = table_irr_matched$BNT_events
  table_irr$AZ_n_matched = table_irr_matched$AZ_n
  table_irr$AZ_events_matched = table_irr_matched$AZ_events
  table_irr$rr_matched = table_irr_matched$rr
}

## Apply rounding
table_irr$BNT_personyears = round(table_irr$BNT_personyears, 0)
table_irr$AZ_personyears = round(table_irr$AZ_personyears, 0)

## Update column names
table_irr <- table_irr %>%
  select(c(outcome_clean, period, 
           BNT_n, BNT_events, BNT_personyears, BNT_rate, BNT_n_matched, BNT_events_matched,
           AZ_n, AZ_events, AZ_personyears, AZ_rate, AZ_n_matched, AZ_events_matched,
           rr, rr_matched))
names(table_irr) <- c("outcome_clean", "Period (days)", 
                      "N, BNT", "N events, BNT", "Person-years, BNT", "Rate (per p-y), BNT", "N, matched, BNT", "N events, matched, BNT", 
                      "N, AZ", "N events, AZ", "Person-years, AZ", "Rate (per p-y), AZ", "N, matched, AZ", "N events, matched, AZ", 
                      "IRR (95% CI)", "IRR (95% CI), matched")

## Redact rates if number of events = 0
table_irr$`Rate (per p-y), BNT`[table_irr$`N events, BNT`==0] = "--"
table_irr$`Rate (per p-y), AZ`[table_irr$`N events, AZ`==0] = "--"

## Generate table of HRs
HR_summary <- model %>% select(model_group, term, estimate, conf.low, conf.high, outcome_clean) %>%
  mutate(
    `HR (95% CI)` = paste0(round(exp(estimate),2)," (",round(exp(conf.low),2),"-",round(exp(conf.high),2),")"),
    `HR (95% CI)` = if_else(`HR (95% CI)`=="NA (NA-NA)", "--", `HR (95% CI)`),
    ) %>%
  select(-c(estimate, conf.low, conf.high)) %>%
  pivot_wider(
    names_from = model_group,
    values_from = `HR (95% CI)` 
    ) %>%
  rename(`Period (days)` = term) %>%
  select(-c(`Calendar-time (unadjusted)`, `Calendar-time (region/date adjusted)`))

## Merge tables
table_irr = left_join(table_irr, HR_summary, by = c("Period (days)", "outcome_clean"))

## Save collated table
write_csv(table_irr, here::here("output", "tables", "irr_hr_summary_VE_boost.csv"))

## Merge tables
table_irr %>%
  gt(groupname_col = "outcome_clean") %>%
  tab_spanner(
    label = "BNT-BNT-BNT",
    columns = c("N, BNT", "N events, BNT", "Person-years, BNT", "Rate (per p-y), BNT", "N, matched, BNT", "N events, matched, BNT")
  ) %>%
  tab_spanner(
    label = "AZ-AZ-BNT",
    columns = c("N, AZ", "N events, AZ", "Person-years, AZ", "Rate (per p-y), AZ", "N, matched, AZ", "N events, matched, AZ")
  ) %>%
  tab_spanner(
    label = "Hazard ratio (95% CI)",
    columns = c("Person-time (unadjusted)", "Person-time (region/date adjusted)", "Person-time (fully adjusted)", "Calendar-time (fully adjusted)", "Matched")
  ) %>%
   tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
   tab_options(table.font.size = pct(70)) %>% #table.width = pct(80) 
   cols_width(
     starts_with("Period") ~ px(100),
     starts_with("IRR") ~ px(200),
     ends_with("adjusted)") ~ px(200)
     )
```
<br/>Frequencies are rounded to the nearest 5. Data are redacted for any rows with rounded counts or non-counts (relative to the denominator) of >0 and <=10.
<br/><br/>

#### Subgroup analysis
```{r, fig.width=21, fig.height=15}
create_subgroup_table = function(selected_subgroup="CKD3") {
  ## Read in table of IRRs
  table_irr <- read_rds(here::here("output", "tables", paste0("table_irr_boost_redacted_unmatched_",selected_subgroup,".rds")))
  table_irr_matched <- read_rds(here::here("output", "tables", paste0("table_irr_boost_redacted_matched_",selected_subgroup,".rds")))
  
  ## Append matched counts (total/events)
  if (all(table_irr$period==table_irr_matched$period) & all(table_irr$outcome==table_irr_matched$outcome)) {
    table_irr$BNT_n_matched = table_irr_matched$BNT_n
    table_irr$BNT_events_matched = table_irr_matched$BNT_events
    table_irr$AZ_n_matched = table_irr_matched$AZ_n
    table_irr$AZ_events_matched = table_irr_matched$AZ_events
    table_irr$rr_matched = table_irr_matched$rr
  }
  
  ## Apply rounding
  table_irr$BNT_personyears = round(table_irr$BNT_personyears, 0)
  table_irr$AZ_personyears = round(table_irr$AZ_personyears, 0)

  ## Update column names
  table_irr$Subgroup = selected_subgroup
  table_irr <- table_irr %>%
    filter(period == "1-182") %>%
    select(c(outcome_clean, Subgroup, 
           BNT_n, BNT_events, BNT_personyears, BNT_rate, BNT_n_matched, BNT_events_matched,
           AZ_n, AZ_events, AZ_personyears, AZ_rate, AZ_n_matched, AZ_events_matched,
           rr, rr_matched))
  names(table_irr) <- c("outcome_clean", "Subgroup",
      "N, BNT", "N events, BNT", "Person-years, BNT", "Rate (per p-y), BNT", "N, matched, BNT", "N events, matched, BNT", 
      "N, AZ", "N events, AZ", "Person-years, AZ", "Rate (per p-y), AZ", "N, matched, AZ", "N events, matched, AZ", 
      "IRR (95% CI)", "IRR (95% CI), matched")

  ## Redact rates if number of events = 0
  table_irr$`Rate (per p-y), BNT`[table_irr$`N events, BNT`==0] = "--"
  table_irr$`Rate (per p-y), AZ`[table_irr$`N events, AZ`==0] = "--"

  ## Read in model outputs
  model = rbind(
      read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[1],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[1]),
      read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[3],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[3]),
      read_rds(here::here("output", "model", "VE_boost", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[4],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[4]),
      read_rds(here::here("output", "model","VE_boost", paste0("modelcox_tidy_reduced_unmatched_persontime_",outcome_list[5],"_",selected_subgroup,".rds"))) %>%
        mutate(outcome_clean = clean_list[5])
      ) %>% 
      filter(model == 2, term == "1-182") %>%
    select(c(outcome_clean, estimate, conf.low, conf.high))

  ## Remove redacted components from plot
  model$estimate = as.numeric(model$estimate)
  model$conf.low = as.numeric(model$conf.low)
  model$conf.high = as.numeric(model$conf.high)
  
  model = model %>%
    mutate(
      `HR (95% CI)` = paste0(round(exp(estimate),2)," (",round(exp(conf.low),2),"-",round(exp(conf.high),2),")"),
      `HR (95% CI)` = if_else(`HR (95% CI)`=="NA (NA-NA)", "--", `HR (95% CI)`),
      ) %>%
    select(-c(estimate, conf.low, conf.high)) 
  
  ## Merge IRR and model outcomes
  if (all(table_irr$outcome_clean==model$outcome_clean)) { table_irr = merge(table_irr, model, by="outcome_clean") }
  
  ## Set factor levels
  table_irr$outcome_clean = factor(table_irr$outcome_clean, levels = clean_list)

  return(table_irr)
}

## Collate different subgroup models
collate_subgroups = rbind(
  create_subgroup_table("all"),
  create_subgroup_table("CKD3"),
  create_subgroup_table("CKD4-5"),
  create_subgroup_table("RRT"),
  create_subgroup_table("Tx"),
  create_subgroup_table("dialysis")
) %>% arrange(outcome_clean)

## Save collated table
write_csv(collate_subgroups, here::here("output", "tables", "irr_hr_summary_VE_boost_subgroups.csv"))

## Render table
collate_subgroups %>%
  gt(groupname_col = "outcome_clean") %>%
  tab_spanner(
    label = "BNT-BNT-BNT",
    columns = c("N, BNT", "N events, BNT", "Person-years, BNT", "Rate (per p-y), BNT", "N, matched, BNT", "N events, matched, BNT")
  ) %>%
  tab_spanner(
    label = "AZ-AZ-BNT",
    columns = c("N, AZ", "N events, AZ", "Person-years, AZ", "Rate (per p-y), AZ", "N, matched, AZ", "N events, matched, AZ")
  ) %>%
   tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
   tab_options(table.font.size = pct(70)) %>% #table.width = pct(80) 
   cols_width(
     starts_with("Period") ~ px(100),
     starts_with("IRR") ~ px(200),
     ends_with("CI)") ~ px(200)
     )
```

```{r}
## Additional code to generate covariate model outputs
dir.create(here::here("output", "model", "summary"), showWarnings = FALSE, recursive=TRUE)
cols_to_keep = c("label", "term", "variable", "estimate", "conf.low", "conf.high", "outcome_clean")
outcome_list_sub = outcome_list[outcome_list!="covid_emergency"]

## Outer loop for outcome list
for (i in 1:length(outcome_list_sub)) {
  selected_outcome = outcome_list_sub[i]
  
  ## Read in full model outputs
  all <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_full_unmatched_persontime_{selected_outcome}_all.csv"))) %>% filter(model==2) %>% mutate(label="All")
  all_ct <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_full_unmatched_calendartime_{selected_outcome}_all.csv"))) %>% filter(model==2) %>% mutate(label="All (CT)")
  ckd3 <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_full_unmatched_persontime_{selected_outcome}_CKD3.csv"))) %>% filter(model==2) %>% mutate(label="CKD3")
  ckd4_5 <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_full_unmatched_persontime_{selected_outcome}_CKD4-5.csv"))) %>% filter(model==2) %>% mutate(label="CKD4-5")
  rrt_any <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_full_unmatched_persontime_{selected_outcome}_RRT.csv"))) %>% filter(model==2) %>% mutate(label="RRT (any)")
  rrt_tx <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_full_unmatched_persontime_{selected_outcome}_Tx.csv"))) %>% filter(model==2) %>% mutate(label="RRT (Tx)")
  rrt_dialysis <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_full_unmatched_persontime_{selected_outcome}_dialysis.csv"))) %>% filter(model==2) %>% mutate(label="RRT (dialysis)")
  all_strata <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_strata_unmatched_persontime_{selected_outcome}_all.csv"))) %>% filter(model==2) %>% mutate(label="All - strata")
  all_ct_strata <- read_csv(here::here("output", "model", "VE_boost", glue("modelcox_tidy_strata_unmatched_calendartime_{selected_outcome}_all.csv"))) %>% filter(model==2) %>% mutate(label="All (CT) - strata")

  ## Collate 
  merged = rbind(
    all[,cols_to_keep], 
    all_ct[,cols_to_keep], 
    ckd3[,cols_to_keep], 
    ckd4_5[,cols_to_keep], 
    rrt_tx[,cols_to_keep],
    rrt_dialysis[,cols_to_keep],
    all_strata[,cols_to_keep],
    all_ct_strata[,cols_to_keep]
  ) %>%
    ## Calculate exponentiated HRs and CIs, then clean ref values
    mutate(HR =  paste0(round(exp(estimate),2)," (",round(exp(conf.low),2),"-",round(exp(conf.high),2),")")) %>%
    mutate(HR = ifelse(HR == "1 (NA-NA)", "1", HR))
  
  ## Pivot to wide format
  merged_wide = merged %>%
    select(term, variable, label, HR) %>%
    pivot_wider(names_from = "label", values_from = "HR") %>%
    mutate(outcome = selected_outcome, level = selected_level)
  
  ## Save
  write_csv(merged_wide, here::here("output", "model", "summary", glue("VE_boost_covariate_estimates_{selected_outcome}.csv")))
}
```

.