---
title: "Descriptive statistics for follow-up periods"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
## Import libraries
library('here')
library('tidyverse')
library('readr')
library('tidyr')
library('lubridate')
library('glue')
library('gt')
library('gtsummary')
library('reshape2')
library('kableExtra')
library('cowplot')
library('fs')
library('survival')
library('survminer')
library('scales')

## Import custom user functions
source(here::here("analysis", "functions.R"))

## Set rounding and redaction thresholds
round_threshold = 5
redaction_threshold = 10

## Import outcome time periods
postvax_list <- read_rds(here::here("output", "lib", "postvax_list.rds"))
postvaxcuts = postvax_list$postvaxcuts
postvax_periods = postvax_list$postvax_periods
lastfupday = max(postvaxcuts)
```
<br><br>  

#### Primary vaccination cohort
```{r, fig.width=5, fig.height=6}
## Set palette
#palette1 = c("#fe9929", "#d95f0e", "#993404") # oranges
palette1 = c("#74a9cf", "#2b8cbe", "#045a8d") # blues
palette2 = c("#fe9929", "#018571", "#a6611a")

## Read in data
d <- read_rds(here::here("output", "data", "data_cohort_VE_primary.rds")) %>%
  mutate(
    stop_date = pmin(censor_date, postvax_positive_test_date, na.rm=TRUE),
    tte_stop = tte(vax2_date - 1, stop_date, na.censor=TRUE)
  )

## Create summary data frame
summary_df = data.frame(
  date = seq(as.Date("2021-01-04", format="%Y-%m-%d"), as.Date("2021-11-30", format="%Y-%m-%d"), "weeks")
)

## Calculate number enrolled, cumulative next dose administration, and case counts over time
for (i in 1:nrow(summary_df)) {
  selected_date = summary_df$date[i]
  summary_df$n_enrolled[i] = plyr::round_any(nrow(subset(d, (vax2_date-1)<=selected_date & stop_date>selected_date)), round_threshold)
  summary_df$cumulative_nextvax[i] = plyr::round_any(sum(d$vax3_date<=selected_date, na.rm = TRUE), round_threshold)

  if (i == 1) {
    summary_df$n_cases[i] = plyr::round_any(sum(d$postvax_positive_test_date==selected_date, na.rm = TRUE), round_threshold)
  } else {
    previous_date = summary_df$date[i-1]
    summary_df$n_cases[i] = plyr::round_any(sum(d$postvax_positive_test_date<=selected_date & d$postvax_positive_test_date>previous_date, na.rm = TRUE), round_threshold)
  }
}

## Set non-zero values below redaction threshold to 0
summary_df$n_enrolled[summary_df$date>as.Date("2021-11-16") | (summary_df$n_enrolled>0 & summary_df$n_enrolled<=redaction_threshold)] = NA
summary_df$cumulative_nextvax[summary_df$date>as.Date("2021-11-16") | (summary_df$cumulative_nextvax>0 & summary_df$cumulative_nextvax<=redaction_threshold)] = NA
summary_df$n_cases[summary_df$date>as.Date("2021-11-16") | (summary_df$n_cases>0 & summary_df$n_cases<=redaction_threshold)] = NA

## Set variant
summary_df$variant = "Alpha"
summary_df$variant[summary_df$date>as.Date("2021-06-04")] = "Delta"
summary_df$variant[summary_df$date>as.Date("2021-12-15")] = "Omicron"
summary_df$variant = factor(summary_df$variant, levels = c("Alpha", "Delta", "Omicron"))

g1 = ggplot(summary_df, aes(x=date, y=n_enrolled/1000)) + 
    geom_bar(stat="identity", fill = palette1[1]) +
    scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-01-01"), as.Date("2021-11-30")), 
               breaks = c(as.Date("2021-01-01"), as.Date("2021-04-01"), as.Date("2021-07-01"), as.Date("2021-10-01"))) +
    theme_bw() + xlab(" ") + ylab("N followed up\n(1000s)") + ylim(0,450) + 
    geom_vline(xintercept = as.Date(c("2021-01-04", "2021-11-16")), linetype="dotted", colour=palette1[3]) +
    theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12))

g2 = ggplot(summary_df, aes(x=date, y=n_cases, fill=variant)) + 
    geom_bar(stat="identity") +
    scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-01-01"), as.Date("2021-11-30")), 
               breaks = c(as.Date("2021-01-01"), as.Date("2021-04-01"), as.Date("2021-07-01"), as.Date("2021-10-01"))) +
    theme_bw() + xlab(" ") + ylab("N cases (weekly)") +
    geom_vline(xintercept = as.Date(c("2021-01-04", "2021-11-16")), linetype="dotted", colour=palette1[3]) +
    scale_fill_manual(values = c("Alpha"=palette2[1], "Delta"=palette2[2], "Omicron"=palette2[3])) +
    labs(fill = "Major variant") +
    theme(strip.background = element_blank(), strip.text = element_text(size=12),
          legend.position = "right",
          axis.text = element_text(size=12), axis.title = element_text(size=12),
          legend.title = element_text(size=12), legend.text = element_text(size=12),
          axis.title.y.left = element_text(size=12, margin = margin(t = 0, r = 8, b = 0, l = 0)))

g3 = ggplot(summary_df, aes(x=date, y=cumulative_nextvax/1000)) + 
    geom_line(colour =  palette1[3]) +
    scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-01-01"), as.Date("2021-11-30")), 
               breaks = c(as.Date("2021-01-01"), as.Date("2021-04-01"), as.Date("2021-07-01"), as.Date("2021-10-01"))) +
    theme_bw() + xlab("Date") + ylab("Cumulative 3rd dose\ncount (1000s)") + ylim(0,450) + 
    geom_vline(xintercept = as.Date(c("2021-01-04", "2021-11-16")), linetype="dotted", colour=palette1[3]) +
    theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12))

plot_grid(g1, g2, g3, ncol=1, align="v", axis = "lr")
```
<br><br>  

#### Follow-up time by outcome (days)
```{r}
data.frame(
  Quartile = c("25%", "Median", "75%")
  ) %>% 
  mutate(
  `SARS-CoV-2 test` = quantile(d$tte_covid_postest_or_censor)[2:4],
  `COVID-19 hosp.` = quantile(d$tte_covid_hosp_or_censor)[2:4],
  `COVID-19 death` = quantile(d$tte_covid_death_or_censor)[2:4],
  `Non-COVID-19 death` = quantile(d$tte_noncovid_death_or_censor)[2:4]
  ) %>% 
  gt()
```
<br>Follow-up quartiles could theoretically relate to individuals but are measured in person-time with varying study entry date; they therefore present no meaningful disclosure risk.<br><br>

#### Uncensored at start of follow-up
```{r}
data.frame(
  Day = c("Day 1")
  ) %>% 
  mutate(
  `SARS-CoV-2 test` = plyr::round_any(sum(d$tte_covid_postest_or_censor>=1), round_threshold),
  `COVID-19 hosp.` = plyr::round_any(sum(d$tte_covid_hosp_or_censor>=1), round_threshold),
  `COVID-19 death` = plyr::round_any(sum(d$tte_covid_death_or_censor>=1), round_threshold),
  `Non-COVID-19 death` = plyr::round_any(sum(d$tte_noncovid_death_or_censor>=1), round_threshold)
  ) %>% 
  gt()
```
<br><br>

#### Uncensored at day 182
```{r}
data.frame(
  Day = c("Day 182")
  ) %>% 
  mutate(
  `SARS-CoV-2 test` = plyr::round_any(sum(d$tte_covid_postest_or_censor==182), round_threshold),
  `COVID-19 hosp.` = plyr::round_any(sum(d$tte_covid_hosp_or_censor==182), round_threshold),
  `COVID-19 death` = plyr::round_any(sum(d$tte_covid_death_or_censor==182), round_threshold),
  `Non-COVID-19 death` = plyr::round_any(sum(d$tte_noncovid_death_or_censor==182), round_threshold)
  ) %>% 
  gt()
```
<br>Frequencies are rounded to the nearest 5.<br><br>

#### Variant breakdown in primary cohort
```{r}
## Subselect individuals followed up until case date
d1 = subset(d, postvax_positive_test_date==stop_date)
d1_Alpha = subset(d, postvax_positive_test_date==stop_date & postvax_positive_test_date<as.Date("2021-06-04"))
d1_Delta = subset(d, postvax_positive_test_date==stop_date & postvax_positive_test_date>=as.Date("2021-06-04"))

## Create variant dataframe to fill in
collated = data.frame(
  period = c(postvax_periods, paste0(postvaxcuts[1]+1,"-",lastfupday)),
  period_start = c(postvaxcuts[1:4]+1,postvaxcuts[1]+1),
  period_end = c(postvaxcuts[2:5], lastfupday)
)

## Calculate variant profile by period
for (i in 1:nrow(collated)) {
  collated$`Count, total`[i] = plyr::round_any(sum(d1$tte_stop>=collated$period_start[i] & 
                                                  d1$tte_stop<=collated$period_end[i]), round_threshold)
  collated$`Count, Alpha`[i] = plyr::round_any(sum(d1_Alpha$tte_stop>=collated$period_start[i] & 
                                                  d1_Alpha$tte_stop<=collated$period_end[i]), round_threshold)
  collated$`Count, Delta`[i] = plyr::round_any(sum(d1_Delta$tte_stop>=collated$period_start[i] & 
                                                    d1_Delta$tte_stop<=collated$period_end[i]), round_threshold)
}

collated$`%, Delta` = round(collated$`Count, Delta`/collated$`Count, total`*100,1)
collated %>% 
  select(-c(period_start, period_end)) %>%
  gt()
```
<br>Counts are rounded to the nearest 5 and percentages calculated from rounded counts.<br><br>

#### Booster vaccination cohort
```{r, fig.width=5, fig.height=6}
## Set palette
palette1 = c("#74a9cf", "#2b8cbe", "#045a8d")

## Read in data
d <- read_rds(here::here("output", "data", "data_cohort_VE_boost.rds")) %>%
  mutate(
    stop_date = pmin(censor_date_testing, postvax_positive_test_date, na.rm=TRUE),
    tte_stop = tte(vax3_date - 1, stop_date, na.censor=TRUE)
  )

## Create summary data frame
summary_df = data.frame(
  date = seq(as.Date("2021-09-01", format="%Y-%m-%d"), as.Date("2022-04-07", format="%Y-%m-%d"), "weeks")
)

## Calculate number enrolled, cumulative next dose administration, and case counts over time
for (i in 1:nrow(summary_df)) {
  selected_date = summary_df$date[i]
  summary_df$n_enrolled[i] = plyr::round_any(nrow(subset(d, (vax3_date-1)<=selected_date & stop_date>selected_date)), round_threshold)
  summary_df$cumulative_nextvax[i] = plyr::round_any(sum(d$vax4_date<=selected_date, na.rm = TRUE), round_threshold)

  if (i == 1) {
    summary_df$n_cases[i] = plyr::round_any(sum(d$postvax_positive_test_date==selected_date, na.rm = TRUE), round_threshold)
  } else {
    previous_date = summary_df$date[i-1]
    summary_df$n_cases[i] = plyr::round_any(sum(d$postvax_positive_test_date<=selected_date & d$postvax_positive_test_date>previous_date, na.rm = TRUE), round_threshold)
  }
}

## Set non-zero values below redaction threshold to 0
summary_df$n_enrolled[summary_df$date>as.Date("2022-03-31") | (summary_df$n_enrolled>0 & summary_df$n_enrolled<=redaction_threshold)] = NA
summary_df$cumulative_nextvax[summary_df$date>as.Date("2022-03-31") | (summary_df$cumulative_nextvax>0 & summary_df$cumulative_nextvax<=redaction_threshold)] = NA
summary_df$n_cases[summary_df$date>as.Date("2022-03-31") | (summary_df$n_cases>0 & summary_df$n_cases<=redaction_threshold)] = NA

## Set variant
summary_df$variant = "Alpha"
summary_df$variant[summary_df$date>as.Date("2021-06-04")] = "Delta"
summary_df$variant[summary_df$date>as.Date("2021-12-15")] = "Omicron"
summary_df$variant = factor(summary_df$variant, levels = c("Alpha", "Delta", "Omicron"))

## Generate plots
g1 = ggplot(summary_df, aes(x=date, y=n_enrolled/1000)) + 
    geom_bar(stat="identity", fill = palette1[1]) +
    scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-09-01"), as.Date("2022-04-07")), 
               breaks = c(as.Date("2021-09-01"), as.Date("2021-11-01"), as.Date("2022-01-01"), as.Date("2022-03-01"))) +
    theme_bw() + xlab(" ") + ylab("N followed up\n(1000s)") + ylim(0,400) + 
    geom_vline(xintercept = as.Date(c("2021-09-01", "2022-03-31")), linetype="dotted", colour=palette1[3]) +
    theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12))

g2 = ggplot(summary_df, aes(x=date, y=n_cases, fill=factor(variant))) + 
    geom_bar(stat="identity") +
    scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-09-01"), as.Date("2022-04-07")), 
               breaks = c(as.Date("2021-09-01"), as.Date("2021-11-01"), as.Date("2022-01-01"), as.Date("2022-03-01"))) +
    theme_bw() + xlab(" ") + ylab("N cases (weekly)") + 
    geom_vline(xintercept = as.Date(c("2021-09-01", "2022-03-31")), linetype="dotted", colour=palette1[3]) +
    scale_fill_manual(values = c("Alpha"=palette2[1], "Delta"=palette2[2], "Omicron"=palette2[3])) +
    labs(fill = "Major variant") +
    theme(strip.background = element_blank(), strip.text = element_text(size=12),
          legend.position = "right",
          axis.text = element_text(size=12), axis.title = element_text(size=12),
          legend.title = element_text(size=12), legend.text = element_text(size=12),
          axis.title.y.left = element_text(size=12, margin = margin(t = 0, r = 8, b = 0, l = 0)))

g3 = ggplot(summary_df, aes(x=date, y=cumulative_nextvax/1000)) + 
    geom_line(colour =  palette1[3]) +
    scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-09-01"), as.Date("2022-04-07")), 
               breaks = c(as.Date("2021-09-01"), as.Date("2021-11-01"), as.Date("2022-01-01"), as.Date("2022-03-01"))) +
    theme_bw() + xlab("Date") + ylab("Cumulative 4th dose\ncount (1000s)") + ylim(0,400) + 
    geom_vline(xintercept = as.Date(c("2021-09-01", "2022-03-31")), linetype="dotted", colour=palette1[3]) +
    theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12))

plot_grid(g1, g2, g3, ncol=1, align="v", axis = "lr")
```
<br><br>

#### Follow-up time by outcome (days)
```{r}
data.frame(
  Quartile = c("25%", "Median", "75%")
  ) %>% 
  mutate(
  `SARS-CoV-2 test` = quantile(d$tte_covid_postest_or_censor)[2:4],
  `COVID-19 hosp.` = quantile(d$tte_covid_hosp_or_censor)[2:4],
  `COVID-19 death` = quantile(d$tte_covid_death_or_censor)[2:4],
  `Non-COVID-19 death` = quantile(d$tte_noncovid_death_or_censor)[2:4]
  ) %>% 
  gt()
```
<br>Quartiles are rounded to the nearest 5 as a precaution against small-number disclosures.<br><br>

#### Uncensored at start of follow-up
```{r}
data.frame(
  Day = c("Day 1")
  ) %>% 
  mutate(
  `SARS-CoV-2 test` = plyr::round_any(sum(d$tte_covid_postest_or_censor>=1), round_threshold),
  `COVID-19 hosp.` = plyr::round_any(sum(d$tte_covid_hosp_or_censor>=1), round_threshold),
  `COVID-19 death` = plyr::round_any(sum(d$tte_covid_death_or_censor>=1), round_threshold),
  `Non-COVID-19 death` = plyr::round_any(sum(d$tte_noncovid_death_or_censor>=1), round_threshold)
  ) %>% 
  gt()
```
<br>Follow-up quartiles could theoretically relate to individuals but are measured in person-time with varying study entry date; they therefore present no meaningful disclosure risk.<br><br>

#### Uncensored at day 182
```{r}
data.frame(
  Day = c("Day 182")
  ) %>% 
  mutate(
  `SARS-CoV-2 test` = plyr::round_any(sum(d$tte_covid_postest_or_censor==182), round_threshold),
  `COVID-19 hosp.` = plyr::round_any(sum(d$tte_covid_hosp_or_censor==182), round_threshold),
  `COVID-19 death` = plyr::round_any(sum(d$tte_covid_death_or_censor==182), round_threshold),
  `Non-COVID-19 death` = plyr::round_any(sum(d$tte_noncovid_death_or_censor==182), round_threshold)
  ) %>% 
  gt()
```
<br>Frequencies are rounded to the nearest 5.<br><br>

#### Variant breakdown in booster cohort
```{r}
## Subselect individuals followed up until case date
d1 = subset(d, postvax_positive_test_date==stop_date)
d1_Delta = subset(d, postvax_positive_test_date==stop_date & postvax_positive_test_date<as.Date("2021-12-15"))
d1_Omicron = subset(d, postvax_positive_test_date==stop_date & postvax_positive_test_date>=as.Date("2021-12-15"))

## Create variant dataframe to fill in
collated = data.frame(
  period = c(postvax_periods, paste0(postvaxcuts[1]+1,"-",lastfupday)),
  period_start = c(postvaxcuts[1:4]+1,postvaxcuts[1]+1),
  period_end = c(postvaxcuts[2:5], lastfupday)
)

## Calculate variant profile by period
for (i in 1:nrow(collated)) {
  collated$`Count, total`[i] = plyr::round_any(sum(d1$tte_stop>=collated$period_start[i] & 
                                                  d1$tte_stop<=collated$period_end[i]), round_threshold)
  collated$`Count, Delta`[i] = plyr::round_any(sum(d1_Delta$tte_stop>=collated$period_start[i] & 
                                                  d1_Delta$tte_stop<=collated$period_end[i]), round_threshold)
  collated$`Count, Omicron`[i] = plyr::round_any(sum(d1_Omicron$tte_stop>=collated$period_start[i] & 
                                                    d1_Omicron$tte_stop<=collated$period_end[i]), round_threshold)
}

collated$`%, Omicron` = round(collated$`Count, Omicron`/collated$`Count, total`*100,1)
collated %>% 
  select(-c(period_start, period_end)) %>%
  gt()
```
<br>Counts are rounded to the nearest 5 and percentages calculated from rounded counts.<br><br>