---
title: "Descriptive plots for BNT162b2 vs ChAdOx1-S vaccination in people with kidney disease"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
## Import libraries
library('here')
library('tidyverse')
library('readr')
library('tidyr')
library('lubridate')
library('glue')
library('gt')
library('gtsummary')
library('reshape2')
library('kableExtra')
library('cowplot')
library('fs')
library('survival')
library('survminer')
library('scales')

## Import custom user functions
source(here::here("analysis", "functions.R"))

## Read in unfiltered data
data_unfiltered <- read_rds(here::here("output", "data", "data_processed.rds")) %>%
  mutate(jcvi_simple = recode(jcvi_group,
                              "1 (65+ care home resident)" = "JCVI 1",
                              "2 (80+ or health/social care worker)" = "JCVI 2", 
                              "3 (75+)" = "JCVI 3",
                              "4 (70+ or clinically extremely vulnerable)" = "JCVI 4", 
                              "5 (65+)" = "JCVI 5",
                              "6 (16-65 and clinically vulnerable)" = "JCVI 6"))

## Read in filtered data
data_filtered <- read_rds(here::here("output", "data", "data_cohort_VE.rds")) %>%
  mutate(jcvi_simple = recode(jcvi_group, 
                              "2 (80+ or health/social care worker)" = "JCVI 2", 
                              "3 (75+)" = "JCVI 3",
                              "4 (70+ or clinically extremely vulnerable)" = "JCVI 4", 
                              "5 (65+)" = "JCVI 5",
                              "6 (16-65 and clinically vulnerable)" = "JCVI 6"))

# data_tte_matched <- read_rds(here::here("output", "data", "data_cohort_VE_matched.rds")) %>%
#   mutate(vax2_type_descr = recode(vax2_type_descr, "BNT162b2" = "BNT", "ChAdOx1" = "AZ"))
```
<br><br>  

#### Histogram: dose 1 dates by region and JCVI group - unfiltered
```{r, fig.width=14, fig.height=10}
ggplot(data_unfiltered, aes(x=vax1_date, group=vax2_type_descr, fill=vax2_type_descr)) + 
     geom_histogram(alpha=0.5, adjust = 1.5, position="identity", binwidth=3) +
     scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2020-12-01"), as.Date("2021-04-01")), 
               breaks = c(as.Date("2021-01-01"),as.Date("2021-02-01"),as.Date("2021-03-01"),as.Date("2021-04-01"))) +
     theme_bw() + xlab("date") + #ylab("density (smoothed)") + 
     scale_fill_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free") + 
  annotate("rect", xmin = as.Date("2020-12-01"), xmax = as.Date("2021-04-01"), ymin = 0, ymax = 10, alpha = 1, colour="grey")
```
<br><br>

#### Histogram: dose 1 dates by region and JCVI group - filtered
```{r, fig.width=14, fig.height=10}
ggplot(data_filtered, aes(x=vax1_date, group=vax2_type_descr, fill=vax2_type_descr)) + 
     geom_histogram(alpha=0.5, adjust = 1.5, position="identity", binwidth=3) +
     scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-01-01"), as.Date("2021-04-01")), 
               breaks = c(as.Date("2021-01-01"),as.Date("2021-02-01"),as.Date("2021-03-01"),as.Date("2021-04-01"))) +
     theme_bw() + xlab("date") + #ylab("density (smoothed)") + 
     scale_fill_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free") + 
  annotate("rect", xmin = as.Date("2021-01-01"), xmax = as.Date("2021-04-01"), ymin = 0, ymax = 10, alpha = 1, colour="grey")
```
<br><br>

#### Density: dose 1 dates by region and JCVI group - unfiltered
```{r, fig.width=14, fig.height=10}
ggplot(data_unfiltered, aes(x=vax1_date, colour=vax2_type_descr)) + 
     geom_density(alpha=0.5) +
     scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2020-12-01"), as.Date("2021-04-01")), 
               breaks = c(as.Date("2021-01-01"),as.Date("2021-02-01"),as.Date("2021-03-01"),as.Date("2021-04-01"))) +
     theme_bw() + xlab("date") + #ylab("density (smoothed)") + 
     scale_colour_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free")
```
<br><br>

#### Density: dose 1 dates by region and JCVI group - filtered
```{r, fig.width=14, fig.height=10}
ggplot(data_filtered, aes(x=vax1_date, colour=vax2_type_descr)) + 
     geom_density(alpha=0.5) +
     scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2020-12-01"), as.Date("2021-04-01")), 
               breaks = c(as.Date("2021-01-01"),as.Date("2021-02-01"),as.Date("2021-03-01"),as.Date("2021-04-01"))) +
     theme_bw() + xlab("date") + #ylab("density (smoothed)") + 
     scale_colour_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free")
```
<br><br>

#### Histogram: dose 2 dates by region and JCVI group - unfiltered
```{r, fig.width=14, fig.height=10}
ggplot(data_unfiltered, aes(x=vax2_date, group=vax2_type_descr, fill=vax2_type_descr)) + 
     geom_histogram(alpha=0.5, adjust = 1.5, position="identity", binwidth=3) +
     scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2020-12-01"), as.Date("2021-07-01")), 
               breaks = c(as.Date("2020-12-01"),as.Date("2021-04-01"),as.Date("2021-05-01"),as.Date("2021-06-01"))) +
     theme_bw() + xlab("date") + #ylab("density (smoothed)") + 
     scale_fill_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free") + 
  annotate("rect", xmin = as.Date("2020-12-01"), xmax = as.Date("2021-07-01"), ymin = 0, ymax = 10, alpha = 1, colour="grey")
```
<br><br>

#### Histogram: dose 2 dates by region and JCVI group - filtered
```{r, fig.width=14, fig.height=10}
ggplot(data_filtered, aes(x=vax2_date, group=vax2_type_descr, fill=vax2_type_descr)) + 
     geom_histogram(alpha=0.5, adjust = 1.5, position="identity", binwidth=3) +
     scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-03-01"), as.Date("2021-07-01")), 
               breaks = c(as.Date("2021-03-01"),as.Date("2021-04-01"),as.Date("2021-05-01"),as.Date("2021-06-01"))) +
     theme_bw() + xlab("date") + #ylab("density (smoothed)") + 
     scale_fill_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free") + 
  annotate("rect", xmin = as.Date("2021-03-01"), xmax = as.Date("2021-07-01"), ymin = 0, ymax = 10, alpha = 1, colour="grey")
```
<br><br>

#### Density: dose 2 dates by region and JCVI group - unfiltered
```{r, fig.width=14, fig.height=10}
ggplot(data_unfiltered, aes(x=vax2_date, colour=vax2_type_descr)) + 
     geom_density(alpha=0.5) +
     scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2020-12-01"), as.Date("2021-07-01")), 
               breaks = c(as.Date("2021-03-01"),as.Date("2021-04-01"),as.Date("2021-05-01"),as.Date("2021-06-01"))) +
     theme_bw() + xlab("date") + #ylab("density (smoothed)") + 
     scale_colour_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free")
```
<br><br>

#### Density: dose 2 dates by region and JCVI group - filtered
```{r, fig.width=14, fig.height=10}
ggplot(data_filtered, aes(x=vax2_date, colour=vax2_type_descr)) + 
     geom_density(alpha=0.5) +
     scale_x_date(labels = date_format("%m/%y"),
               limits = c(as.Date("2021-03-01"), as.Date("2021-07-01")), 
               breaks = c(as.Date("2021-03-01"),as.Date("2021-04-01"),as.Date("2021-05-01"),as.Date("2021-06-01"))) +
     theme_bw() + xlab("date") + #ylab("density (smoothed)") + 
     scale_colour_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free")
```
<br><br>

#### Histogram: dose 1-2 interval by region and JCVI group - unfiltered
```{r, fig.width=14, fig.height=10}
ggplot(data_unfiltered, aes(x=tbv1_2, group=vax2_type_descr, fill=vax2_type_descr)) + 
     geom_histogram(alpha=0.5, adjust = 1.5, position="identity", binwidth=1) +
     theme_bw() + xlab("dose 1-2 interval (days)") + #ylab("density (smoothed)") + 
     scale_fill_brewer(palette="Dark2", name = "Product") +
     xlim(2*7,20*7) +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free") + 
 annotate("rect", xmin = 2*7, xmax = 20*7, ymin = 0, ymax = 10, alpha = 1, colour="grey")
```
<br><br>

#### Histogram: dose 1-2 interval by region and JCVI group - filtered
```{r, fig.width=14, fig.height=10}
ggplot(data_filtered, aes(x=tbv1_2, group=vax2_type_descr, fill=vax2_type_descr)) + 
     geom_histogram(alpha=0.5, adjust = 1.5, position="identity", binwidth=1) +
     theme_bw() + xlab("dose 1-2 interval (days)") + #ylab("density (smoothed)") + 
     scale_fill_brewer(palette="Dark2", name = "Product") +
     xlim(2*7,20*7) + 
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free") + 
 annotate("rect", xmin = 2*7, xmax = 20*7, ymin = 0, ymax = 10, alpha = 1, colour="grey")
```
<br><br>

#### Histogram: age by region and JCVI group - unfiltered
```{r, fig.width=14, fig.height=10}
ggplot(data_unfiltered, aes(x=age, group=vax2_type_descr, fill=vax2_type_descr)) + 
     geom_histogram(alpha=0.5, adjust = 1.5, position="identity", binwidth=1) +
     theme_bw() + xlab("age") + #ylab("density (smoothed)") + 
     scale_fill_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free") + 
  annotate("rect", xmin = 18, xmax = 100, ymin = 0, ymax = 10, alpha = 1, colour="grey")
```
<br><br>

#### Histogram: age by region and JCVI group - filtered
```{r, fig.width=14, fig.height=10}
ggplot(data_filtered, aes(x=age, group=vax2_type_descr, fill=vax2_type_descr)) + 
     geom_histogram(alpha=0.5, adjust = 1.5, position="identity", binwidth=1) +
     theme_bw() + xlab("age") + #ylab("density (smoothed)") + 
     scale_fill_brewer(palette="Dark2", name = "Product") +
     theme(strip.background = element_blank(), strip.text = element_text(size=12),
           axis.text = element_text(size=12), axis.title = element_text(size=12),
           legend.title = element_text(size=12), legend.text = element_text(size=12)) +
  facet_grid(region~jcvi_simple, scales="free") + 
  annotate("rect", xmin = 18, xmax = 100, ymin = 0, ymax = 10, alpha = 1, colour="grey")
```
<br>Grey lines are used to redact values of <10 in each plot.<br>
.