---
title: "Check of Cox model assumptions for coverage models"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

## Import libraries
library('here')
library('readr')
library('tidyr')
library('tidyverse')
library('lubridate')
library('survival')
library('gtsummary')
library('gt')
library('survminer')
library('glue')
library('fs')
library('cowplot')

## Import command-line arguments
args <- commandArgs(trailingOnly=TRUE)

## Set input and output pathways - default is dose 3 uptake by 20th April 2022
if(length(args)==0) {
  outcome_label = "dose3"
  selected_subgroup = "full"
} else {
  if (args[[1]]=="dose3") {
    outcome_label = "dose3"
    selected_subgroup = args[[2]]
  } else if (args[[1]]=="dose4") {
    outcome_label = "dose4"
    selected_subgroup = args[[2]]
  } else {
    # Print error if no argument specified
    stop("No outcome specified")
  }
}

## Update subgroup selection strings
if (selected_subgroup=="dialysis") { selected_subgroup = "RRT (dialysis)"}
if (selected_subgroup=="transplant") { selected_subgroup = "RRT (Tx)"}

## Import custom user functions
source(here::here("analysis", "functions.R"))

## Import data 
data_cox <- read_rds(here::here("output", "data", paste0("data_cox_coverage_",outcome_label,".rds")))

## Select subgroup depending on arg[[2]]
if (selected_subgroup!="full") {
  data_cox = subset(data_cox, ckd_5cat==selected_subgroup)
}

## Set variable list
var_list <- c("ageband2", "sex", "ethnicity", "imd",  "rural_urban_group",
              "ckd_5cat", "chronic_kidney_disease_stages_3_5",
              "care_home", "hscworker", "housebound", "endoflife",
              "prior_covid_cat", "immunosuppression", "mod_sev_obesity", "diabetes", "any_resp_dis", "chd", "cld", "asplenia", "cancer",
              "haem_cancer", "other_transplant", "chronic_neuro_dis_inc_sig_learn_dis","sev_mental_ill", "cev_other") 

## Set subset of variables to be used in minimally adjusted models
min_adj_list <- c("ageband2", "care_home", "hscworker")

## Set subset of variables to be used in partially adjusted models
adj_list <- c("ageband2", "care_home", "hscworker", "housebound", "endoflife", "rural_urban_group",
              "sex", "ethnicity", "imd", "prior_covid_cat", "haem_cancer", "immunosuppression")

## Select data subset
if (selected_subgroup!="full") { var_list = var_list[var_list!="ckd_5cat"] }
  
## Exclude cev_other from RRT groups given that all will be 0 by definition
if (selected_subgroup %in% c("RRT (dialysis)", "RRT (Tx)")) { var_list = var_list[var_list!="cev_other"] }

## Exclude other_transplant from RRT (Tx) groups given that all will be 0 by definition
if (selected_subgroup=="RRT (Tx)") { var_list = var_list[var_list!="other_transplant"] }
```

#### Summary of input data
* Selected subset: `r selected_subgroup`    
* Selected outcome: `r outcome_label`    
* N: `r plyr::round_any(nrow(data_cox),5)`    
<br/><br/>

#### Visualisation of KM curves for each covariate in turn
```{r, fig.width=10, fig.height=35}
## Loop across variable list
for (i in 1:length(var_list)) {
  ## Assign variable
  data_cox$var = data_cox[,var_list[i]]
  
  ## Create survival object
  surv = survfit(as.formula(paste0("Surv(follow_up_time, covid_vax) ~",var_list[i])), data = data_cox)
  
  ## Generate km plot
  km_plot = ggsurvplot(surv, censor = FALSE, xlim = c(250,450))[[1]]
  assign(paste0("km_", i), km_plot) # saves plot_i to environment
  
  ## Generate survival table for univariate model
  survival.table <- broom::tidy(surv) %>% 
    filter(n.event > 0) %>% 
    group_by(strata) %>%
    mutate(hazard = n.event / (n.risk * (lead(time) - time)),
           log_cum_hazard = log(cumsum(hazard)))
  
  ## Create log plot
  log_plot = ggplot() +
    geom_step(data = survival.table, aes(x = log(time), y = log_cum_hazard, col = strata)) +
    xlim(log(250),log(450)) +
    labs(x = "log(time)", y = "log(-log(survival))") +
    theme_classic() +
    guides(col = guide_legend(nrow = 1)) + 
    theme(legend.position = "top" ,legend.background = element_rect(fill = "white", colour = NA),
          plot.title = element_text(hjust = 0.5), legend.title = element_blank())
    assign(paste0("log_", i), log_plot) # saves plot_i to environment
}

## Render grid of KM plots (calibrating plot counts depending on variables included)
if (selected_subgroup=="full") {
  plot_grid(
    km_1, km_2, km_3, km_4, km_5, km_6, km_7, km_8, km_9, km_10, km_11, km_12, km_13, km_14, km_15, km_16, km_17, km_18, km_19, km_20, km_21, km_22, km_23, km_24, km_25,
    ncol=2
  )
} else if (selected_subgroup %in% c("CKD3a", "CKD3b", "CKD4-5")) {
  plot_grid(
    km_1, km_2, km_3, km_4, km_5, km_6, km_7, km_8, km_9, km_10, km_11, km_12, km_13, km_14, km_15, km_16, km_17, km_18, km_19, km_20, km_21, km_22, km_23, km_24,
    ncol=2
  )
} else if (selected_subgroup %in% c("RRT (dialysis)")) {
  plot_grid(
    km_1, km_2, km_3, km_4, km_5, km_6, km_7, km_8, km_9, km_10, km_11, km_12, km_13, km_14, km_15, km_16, km_17, km_18, km_19, km_20, km_21, km_22, km_23,
    ncol=2
  )
} else {
    plot_grid(
    km_1, km_2, km_3, km_4, km_5, km_6, km_7, km_8, km_9, km_10, km_11, km_12, km_13, km_14, km_15, km_16, km_17, km_18, km_19, km_20, km_21, km_22, 
    ncol=2
  )
}
```
<br/><br/>

#### Test for proportional hazards (partially/fully adjusted models)
```{r}
############################################################################
## Update of ggcoxzph function to address confidence interval plotting issue
## https://github.com/kassambara/survminer/issues/444
############################################################################

ggcoxzph_mod = function (fit, resid = TRUE, se = TRUE, df = 4, nsmo = 40, var, 
    point.col = "red", point.size = 1, point.shape = 19, point.alpha = 1, 
    caption = NULL, ggtheme = theme_survminer(), ...) 
{
    x <- fit
    if (!methods::is(x, "cox.zph")) 
        stop("Can't handle an object of class ", class(x))
    xx <- x$x
    yy <- x$y
    d <- nrow(yy)
    df <- max(df)
    nvar <- ncol(yy)
    pred.x <- seq(from = min(xx), to = max(xx), length = nsmo)
    temp <- c(pred.x, xx)
    lmat <- splines::ns(temp, df = df, intercept = TRUE)
    pmat <- lmat[1:nsmo, ]
    xmat <- lmat[-(1:nsmo), ]
    qmat <- qr(xmat)
    if (qmat$rank < df) 
        stop("Spline fit is singular, try a smaller degrees of freedom")
    if (se) {
        bk <- backsolve(qmat$qr[1:df, 1:df], diag(df))
        xtx <- bk %*% t(bk)
        seval <- ((pmat %*% xtx) * pmat) %*% rep(1, df) # d * removed prior to first bracket
    }
    ylab <- paste("B(t) for", dimnames(yy)[[2]])
    if (missing(var)) 
        var <- 1:nvar
    else {
        if (is.character(var)) 
            var <- match(var, dimnames(yy)[[2]])
        if (any(is.na(var)) || max(var) > nvar || min(var) < 
            1) 
            stop("Invalid variable requested")
    }
    if (x$transform == "log") {
        xx <- exp(xx)
        pred.x <- exp(pred.x)
    }
    else if (x$transform != "identity") {
        xtime <- as.numeric(dimnames(yy)[[1]])
        indx <- !duplicated(xx)
        apr1 <- approx(xx[indx], xtime[indx], seq(min(xx), max(xx), 
            length = 17)[2 * (1:8)])
        temp <- signif(apr1$y, 2)
        apr2 <- approx(xtime[indx], xx[indx], temp)
        xaxisval <- apr2$y
        xaxislab <- rep("", 8)
        for (i in 1:8) xaxislab[i] <- format(temp[i])
    }
    plots <- list()
    plots <- lapply(var, function(i) {
        invisible(pval <- round(x$table[i, 3], 4))
        gplot <- ggplot() + labs(title = paste0("p: ", 
            pval)) + ggtheme + 
            theme(axis.text = element_text(size=9), axis.title = element_text(size=9)) # added to reduce font size of axis text
        y <- yy[, i]
        yhat <- as.vector(pmat %*% qr.coef(qmat, y))
        if (resid) 
            yr <- range(yhat, y)
        else yr <- range(yhat)
        if (se) {
            temp <- as.vector(2 * sqrt(x$var[i, i] * seval))
            yup <- yhat + temp
            ylow <- yhat - temp
            yr <- range(yr, yup, ylow)
        }
        if (x$transform == "identity") {
            gplot <- gplot + geom_line(aes(x = pred.x, y = yhat)) + 
                xlab("Time") + ylab(ylab[i]) + ylim(yr)
        }
        else if (x$transform == "log") {
            gplot <- gplot + geom_line(aes(x = log(pred.x), y = yhat)) + 
                xlab("Time") + ylab(ylab[i]) + ylim(yr)
        }
        else {
            gplot <- gplot + geom_line(aes(x = pred.x, y = yhat)) + 
                xlab("Time") + ylab(ylab[i]) + scale_x_continuous(breaks = xaxisval, 
                labels = xaxislab) + ylim(yr)
        }
        if (resid) 
            gplot <- gplot + geom_point(aes(x = xx, y = y), col = point.col, 
                shape = point.shape, size = point.size, alpha = point.alpha)
        if (se) {
            gplot <- gplot + geom_line(aes(x = pred.x, y = yup), 
                lty = "dashed") + geom_line(aes(x = pred.x, y = ylow), 
                lty = "dashed")
        }
        ggpubr::ggpar(gplot, ...)
    })
    names(plots) <- var
    class(plots) <- c("ggcoxzph", "ggsurv", "list")
    if ("GLOBAL" %in% rownames(x$table)) 
        global_p <- x$table["GLOBAL", 3]
    else global_p <- NULL
    attr(plots, "global_pval") <- global_p
    attr(plots, "caption") <- caption
    plots
}
############################################################################
############################################################################

## Fit fully adjusted model
cox_full <- coxph(as.formula(paste0("Surv(follow_up_time, covid_vax) ~", paste(var_list, collapse="+"),"+ strata(region)")),data = data_cox)

## Run full cox.zph test
test.ph = cox.zph(cox_full)
tab = data.frame(test.ph$table)
names(tab) = paste0(names(tab),"_full")

## Create variables to fill with results from partially adjusted models
tab$chisq_partial = NA
tab$df_partial = NA
tab$p_partial = NA

## Create variables to fill with results from minimally adjusted models
tab$chisq_minimal = NA
tab$df_minimal = NA
tab$p_minimal = NA

## Fit partially adjusted models in loop and extract proportional test results
for (i in 1:length(var_list)) {
  ## Create residual plot for variable in question - fully adjusted model
  resid_full = ggcoxzph_mod(test.ph, var=var_list[i], point.alpha=0.005)[[1]]
  assign(paste0("res_f_", i), resid_full) # saves to environment
  
  ## Select variables for minimally adjusted model
  var = var_list[i]
  if (var %in% min_adj_list) { final_list = min_adj_list } else { final_list = c(var, min_adj_list) }
  
  ## Fit model and extract cox.zph outputs 
  cox_minimal = coxph(as.formula(paste0("Surv(follow_up_time, covid_vax) ~",paste(final_list, collapse="+"),"+ strata(region)")), 
                        data = data_cox)
  test.ph_minimal = cox.zph(cox_minimal)
  tab_minimal = data.frame(test.ph_minimal$table)
  tab$chisq_minimal[i] = tab_minimal[var,"chisq"]
  tab$df_minimal[i] = tab_minimal[var,"df"]
  tab$p_minimal[i] = tab_minimal[var,"p"]
  
  ## Create residual plot for variable in question - partially adjusted model
  resid_minimal = ggcoxzph_mod(test.ph_minimal, var=var_list[i], point.alpha=0.005)[[1]]
  assign(paste0("res_m_", i), resid_minimal) # saves to environment

  ## Select variables for partially adjusted model
  if (var %in% adj_list) { final_list = adj_list } else { final_list = c(var, adj_list) }
  
  ## Fit model and extract cox.zph outputs 
  cox_partial = coxph(as.formula(paste0("Surv(follow_up_time, covid_vax) ~",paste(final_list, collapse="+"),"+ strata(region)")), 
                        data = data_cox)
  test.ph_partial = cox.zph(cox_partial)
  tab_partial = data.frame(test.ph_partial$table)
  tab$chisq_partial[i] = tab_partial[var,"chisq"]
  tab$df_partial[i] = tab_partial[var,"df"]
  tab$p_partial[i] = tab_partial[var,"p"]
  
  ## Create residual plot for variable in question - partially adjusted model
  resid_partial = ggcoxzph_mod(test.ph_partial, var=var_list[i], point.alpha=0.005)[[1]]
  assign(paste0("res_p_", i), resid_partial) # saves to environment
}
gt(tab, rownames_to_stub = T) %>%
    tab_options(table.font.size = pct(85))
```
<br/>NB. Significant p values may partly reflect overpowered (and therefore) highly sensitive models, so should be interepreted alongside residual plots below.
<br/><br/>

#### Schoenfeld residuals - minimally adjusted (left), partially adjusted (middle), and fully adjusted models (right)
```{r, fig.width=12, fig.height=60}
## Render grid of residual plots (calibrating plot counts depending on variables included)
if (selected_subgroup=="full") {
  plot_grid(
    res_m_1, res_p_1, res_f_1, res_m_2, res_p_2, res_f_2, res_m_3, res_p_3, res_f_3,
    res_m_4, res_p_4, res_f_4, res_m_5, res_p_5, res_f_5, res_m_6, res_p_6, res_f_6,
    res_m_7, res_p_7, res_f_7, res_m_8, res_p_8, res_f_8, res_m_9, res_p_9, res_f_9, 
    res_m_10, res_p_10, res_f_10, res_m_11, res_p_11, res_f_11, res_m_12, res_p_12, res_f_12,
    res_m_13, res_p_13, res_f_13, res_m_14, res_p_14, res_f_14, res_m_15, res_p_15, res_f_15,
    res_m_16, res_p_16, res_f_16, res_m_17, res_p_17, res_f_17, res_m_18, res_p_18, res_f_18,
    res_m_19, res_p_19, res_f_19, res_m_20, res_p_20, res_f_20, res_m_21, res_p_21, res_f_21,
    res_m_22, res_p_22, res_f_22, res_m_23, res_p_23, res_f_23, res_m_24, res_p_24, res_f_24,
    res_m_25, res_p_25, res_f_25,
    ncol=3
  )
} else if (selected_subgroup %in% c("CKD3a", "CKD3b", "CKD4-5")) {
  plot_grid(
    res_m_1, res_p_1, res_f_1, res_m_2, res_p_2, res_f_2, res_m_3, res_p_3, res_f_3,
    res_m_4, res_p_4, res_f_4, res_m_5, res_p_5, res_f_5, res_m_6, res_p_6, res_f_6,
    res_m_7, res_p_7, res_f_7, res_m_8, res_p_8, res_f_8, res_m_9, res_p_9, res_f_9, 
    res_m_10, res_p_10, res_f_10, res_m_11, res_p_11, res_f_11, res_m_12, res_p_12, res_f_12,
    res_m_13, res_p_13, res_f_13, res_m_14, res_p_14, res_f_14, res_m_15, res_p_15, res_f_15,
    res_m_16, res_p_16, res_f_16, res_m_17, res_p_17, res_f_17, res_m_18, res_p_18, res_f_18,
    res_m_19, res_p_19, res_f_19, res_m_20, res_p_20, res_f_20, res_m_21, res_p_21, res_f_21,
    res_m_22, res_p_22, res_f_22, res_m_23, res_p_23, res_f_23, res_m_24, res_p_24, res_f_24,
    ncol=3
  )
} else if (selected_subgroup %in% c("RRT (dialysis)")) {
  plot_grid(
    res_m_1, res_p_1, res_f_1, res_m_2, res_p_2, res_f_2, res_m_3, res_p_3, res_f_3,
    res_m_4, res_p_4, res_f_4, res_m_5, res_p_5, res_f_5, res_m_6, res_p_6, res_f_6,
    res_m_7, res_p_7, res_f_7, res_m_8, res_p_8, res_f_8, res_m_9, res_p_9, res_f_9, 
    res_m_10, res_p_10, res_f_10, res_m_11, res_p_11, res_f_11, res_m_12, res_p_12, res_f_12,
    res_m_13, res_p_13, res_f_13, res_m_14, res_p_14, res_f_14, res_m_15, res_p_15, res_f_15,
    res_m_16, res_p_16, res_f_16, res_m_17, res_p_17, res_f_17, res_m_18, res_p_18, res_f_18,
    res_m_19, res_p_19, res_f_19, res_m_20, res_p_20, res_f_20, res_m_21, res_p_21, res_f_21,
    res_m_22, res_p_22, res_f_22, res_m_23, res_p_23, res_f_23,
    ncol=3
  )
} else {
  plot_grid(
    res_m_1, res_p_1, res_f_1, res_m_2, res_p_2, res_f_2, res_m_3, res_p_3, res_f_3,
    res_m_4, res_p_4, res_f_4, res_m_5, res_p_5, res_f_5, res_m_6, res_p_6, res_f_6,
    res_m_7, res_p_7, res_f_7, res_m_8, res_p_8, res_f_8, res_m_9, res_p_9, res_f_9, 
    res_m_10, res_p_10, res_f_10, res_m_11, res_p_11, res_f_11, res_m_12, res_p_12, res_f_12,
    res_m_13, res_p_13, res_f_13, res_m_14, res_p_14, res_f_14, res_m_15, res_p_15, res_f_15,
    res_m_16, res_p_16, res_f_16, res_m_17, res_p_17, res_f_17, res_m_18, res_p_18, res_f_18,
    res_m_19, res_p_19, res_f_19, res_m_20, res_p_20, res_f_20, res_m_21, res_p_21, res_f_21,
    res_m_22, res_p_22, res_f_22,
    ncol=3
  )
}
```
<br/><br/>

#### Session info
```{r}
print(sessionInfo())
```
.