---
title: "Factors associated with COVID-19 vaccine coverage in chronic kidney disease patients"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

## Import libraries
library('here')
library('tidyverse')
library('readr')
library('tidyr')
library('lubridate')
library('glue')
library('gt')
library('gtsummary')
library('reshape2')
library('kableExtra')
library('cowplot')
library('fs')

## Import custom user functions
source(here::here("analysis", "functions.R"))

## Import data
data_cohort <- read_rds(here::here("output", "data", "data_cohort_coverage.rds"))
data_uncensored <- read_rds(here::here("output", "data", "data_cohort_coverage_logistic.rds"))
data_dose4 <- read_rds(here::here("output", "data", "data_cohort_coverage_dose4.rds"))
data_dose4_uncensored <- subset(data_dose4, is.na(death_date) & is.na(dereg_date))

## Calculate rounded population totals
rounded_n = plyr::round_any(nrow(data_cohort), 5)
rounded_n_uncensored = plyr::round_any(nrow(data_uncensored), 5)
rounded_n_dose4 = plyr::round_any(nrow(data_dose4), 5)
rounded_n_dose4_uncensored = plyr::round_any(nrow(data_dose4_uncensored), 5)

if (data_cohort$mock_data_flag[1]==1) { flag = "present" } else { flag = "absent" }
```
<br/><br/>  

#### Background
Chronic kidney disease (CKD) is a significant risk factor for COVID-19-related mortality. Although vaccination has the potential to mitigate this risk, CKD has been linked with impaired COVID-19 vaccine immunogenicity and high rates of breakthrough infection among individuals who have received a 2-dose primary vaccine series.

Vaccine recommendations for CKD patients in the UK have evolved over time (see [protocol](https://docs.google.com/document/d/1w48W-bCMfn0RdkfxlU6fbRkPv3MnIYd3/edit#heading=h.1fob9te). Relative uptake of different vaccines in this population remains uncertain, as does the relative vaccine effectiveness (VE) of different regimens, including homologous versus heterologous vaccine usage. This project seeks to address these key evidence gaps.

#### Inclusion criteria
* Registered for at least 3m before index date (01-Dec-2020)    
* Alive on index date    
* Aged ≥16 and <120 on index date
* eGFR<60 in 2 years before 01 Dec 2020 OR dialysis code (opensafely/dialysis/3ce108ac) OR kidney transplant code (opensafely/kidney-transplant//2020-07-15)    
* No missing demographic data   
* Maximum of 4 COVID-19 doses recorded
* No vaccines administered at an interval of <14 days

A total of **`r prettyNum(rounded_n)`** (rounded to the nearest 5) met the inclusion criteria (see *output/data/flowchart.csv* for additional details), of which **`r prettyNum(rounded_n_uncensored)`** remained uncensored (alive and registered) throughout follow-up (01-Dec-2020 to 16-Feb-2022).

Of the total population, **`r prettyNum(rounded_n_dose4)`** had a history of immunosuppression, haematologic cancer, or transplant on the index date. This population includes individuals eligible for an extended primary series and subsequent booster dose, and was therefore included in the dose 4 analysis subset. **`r prettyNum(rounded_n_dose4_uncensored)`** remained uncensored (alive and registered) throughout follow-up (01-Dec-2020 to 16-Feb-2022).

`r if(flag=="present") { paste0("NB: Dummy data processing flag detected!") }`    
<br/><br/><br/><br/>    

#### Table 1: Summary of population
```{r}
table_1 <- read_rds(here::here("output", "tables", "table1_coverage_redacted.rds"))

## Set factor levels for group
table_1$Group[table_1$Group=="Other"] = "Risk group"

subset(table_1, Group!="Time between doses 1 and 2" & Group!="Time between doses 2 and 3") %>% 
   gt(groupname_col = "Group") %>%
   tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
   tab_style(
     style = cell_text(indent = pct(5)),
     locations = cells_body(columns = "Variable")
     ) %>%
   tab_options(table.font.size = pct(95)) %>% #table.width = pct(80) 
   tab_footnote(
     footnote = "All counts rounded to nearest 5; any rounded counts <=10 or within <=10 of population total redacted.",
     locations = cells_column_labels(columns = "Count")
   )
```
<br/><br/>    

#### Coverage over time
```{r, message=FALSE, fig.width=8, fig.height=8}
# Create vector of dates between first and last recorded vaccines
campaign_start <- as_date("2020-12-01")
end_date <- as_date("2022-02-16")

# create vector containing every other week
date_vec <- seq(campaign_start, end_date, by="weeks")
date_vec <- date_vec[seq(1, length(date_vec), 2)]

# set rounding factor
rounding_cutoff = 10

# cumulative table
t_all <- data.frame(date = date_vec)
for (i in 1:nrow(t_all)) {
  date_ref = t_all$date[i]
  t_all$dose1_total[i] = plyr::round_any(sum(data_uncensored$vax1_date<=date_ref, na.rm=T), rounding_cutoff)
  t_all$dose2_total[i] = plyr::round_any(sum(data_uncensored$vax2_date<=date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose3_total[i] = plyr::round_any(sum(data_uncensored$vax3_date<=date_ref, na.rm=T), rounding_cutoff)
  t_all$dose4_total[i] = plyr::round_any(sum(data_uncensored$vax4_date<=date_ref, na.rm=T), rounding_cutoff)

  t_all$dose1_pfizer[i] = plyr::round_any(sum(data_uncensored$vax1_type=="pfizer" & data_uncensored$vax1_date<=date_ref, na.rm=T), rounding_cutoff)
  t_all$dose2_pfizer[i] = plyr::round_any(sum(data_uncensored$vax2_type=="pfizer" & data_uncensored$vax2_date<=date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose3_pfizer[i] = plyr::round_any(sum(data_uncensored$vax2_type=="pfizer" & data_uncensored$vax3_date<=date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose4_pfizer[i] = plyr::round_any(sum(data_uncensored$vax2_type=="pfizer" & data_uncensored$vax4_date<=date_ref, na.rm=T), rounding_cutoff)

  t_all$dose1_az[i] = plyr::round_any(sum(data_uncensored$vax1_type=="az" & data_uncensored$vax1_date<=date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose2_az[i] = plyr::round_any(sum(data_uncensored$vax2_type=="az" & data_uncensored$vax2_date<=date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose3_az[i] = plyr::round_any(sum(data_uncensored$vax3_type=="az" & data_uncensored$vax3_date<=date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose4_az[i] = plyr::round_any(sum(data_uncensored$vax4_type=="az" & data_uncensored$vax4_date<=date_ref, na.rm=T), rounding_cutoff)

  t_all$dose1_moderna[i] = plyr::round_any(sum(data_uncensored$vax1_type=="moderna" & data_uncensored$vax1_date<=date_ref, na.rm=T), rounding_cutoff)
  t_all$dose2_moderna[i] = plyr::round_any(sum(data_uncensored$vax2_type=="moderna" & data_uncensored$vax2_date<=date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose3_moderna[i] = plyr::round_any(sum(data_uncensored$vax3_type=="moderna" & data_uncensored$vax3_date<=date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose4_moderna[i] = plyr::round_any(sum(data_uncensored$vax4_type=="moderna" & data_uncensored$vax4_date<=date_ref, na.rm=T), rounding_cutoff)
  
  t_all$az_az[i] = plyr::round_any(sum(data_uncensored$vax2_date<=date_ref & data_uncensored$vax12_type=="az-az", na.rm=T), rounding_cutoff)
  t_all$pfizer_pfizer[i] = plyr::round_any(sum(data_uncensored$vax2_date<=date_ref & data_uncensored$vax12_type=="pfizer-pfizer", na.rm=T), rounding_cutoff)
  t_all$moderna_moderna[i] = plyr::round_any(sum(data_uncensored$vax2_date<=date_ref & data_uncensored$vax12_type=="moderna-moderna", na.rm=T), rounding_cutoff)
  t_all$heterologous_dose2[i] = plyr::round_any(sum(data_uncensored$vax2_date<=date_ref & (data_uncensored$vax1_type!=data_uncensored$vax2_type), na.rm=T), rounding_cutoff)
}

# Save as html ----
write_csv(t_all, here::here("output", "tables", "coverage_over_time_rounded.csv"))

# Plot cumulative distribution
palette = c("#3B9AB2","#78B7C5","#EBCC2A","#E1AF00","#B40F20")
t_plot = rbind(
  data.frame(dose = "dose 1", total = t_all$dose1_total, percent = round(t_all$dose1_total/rounded_n_uncensored*100,1), date = t_all$date),
  data.frame(dose = "dose 2", total = t_all$dose2_total, percent = round(t_all$dose2_total/rounded_n_uncensored*100,1), date = t_all$date),
  data.frame(dose = "dose 3", total = t_all$dose3_total, percent = round(t_all$dose3_total/rounded_n_uncensored*100,1), date = t_all$date),
  data.frame(dose = "dose 4", total = t_all$dose4_total, percent = round(t_all$dose4_total/rounded_n_uncensored*100,1), date = t_all$date)
)
plot_max = max(t_plot$total/1000)*1.1
g1 = ggplot(t_plot, aes(x = date, y = total/1000, colour = dose)) + geom_line() +
          theme_bw()+ scale_colour_manual(values = palette[c(1,2,4,5)]) +
          theme(legend.position="right") + 
  ggtitle("Any vaccine") +
  theme(legend.title = element_text(size=14), legend.text = element_text(size=12), axis.text = element_text(size=14), axis.title = element_text(size=14)) +
  scale_y_continuous(
    name = "N doses given (1000s)", limits=c(0,plot_max),
    sec.axis = sec_axis(~ ./rounded_n*100, name="%", breaks= c(0,25,50,75,100))
  )

# Plot cumulative product-specific vaccination
palette = c("#003c30","#b2182b","#74add1","grey")
t_plot = rbind(
  data.frame(product = "2 x ChAdOx1-S", total = t_all$az_az, date = t_all$date),
  data.frame(product = "2 x Pfizer", total = t_all$pfizer_pfizer, date = t_all$date),
  data.frame(product = "2 x Moderna", total = t_all$moderna_moderna, date = t_all$date),
  data.frame(product = "Heterologous", total = t_all$heterologous, date = t_all$date)
)
plot_max = max(t_plot$total/1000)*1.1
g2 = ggplot(t_plot, aes(x = date, y = total/1000, colour = product)) + geom_line() +
          theme_bw() + ylab("doses given") + scale_colour_manual(values = palette[c(1,2,3,4)]) +
          theme(legend.position="right") +
  ggtitle("Product-specific vaccination (primary series)") +
  theme(legend.title = element_text(size=14), legend.text = element_text(size=12), axis.text = element_text(size=14), axis.title = element_text(size=14)) +
  scale_y_continuous(
    name = "N doses given (1000s)", limits=c(0,plot_max),
    sec.axis = sec_axis(~ ./rounded_n*100, name="%", breaks= c(0,25,50,75,100))
  )
plot_grid(g1, g2, ncol=1,  align="v", axis = c("lr"))
```
<br/>Numbers rounded to the nearest 10 before plotting.     
<br/><br/>    

#### Coverage as of 16-Feb-2022
```{r}
## Calculate coverage in total and uncensored populations
collated = data.frame(
  Dose = c("1", "2", "3", "4"),
  N_cohort_total = c(rep(rounded_n, 3), rounded_n_dose4),
  N_vaccinated_total = c(sum(data_cohort$vax1_date<=end_date, na.rm=T), sum(data_cohort$vax2_date<=end_date, na.rm=T), 
                         sum(data_cohort$vax3_date<=end_date, na.rm=T), sum(data_dose4$vax4_date<=end_date, na.rm=T))
) %>%
  mutate(
    coverage_total = round(N_vaccinated_total/N_cohort_total*100,1),
    N_cohort_uncensored = c(rep(rounded_n_uncensored, 3), rounded_n_dose4_uncensored),
    N_vaccinated_uncensored = c(sum(data_uncensored$vax1_date<=end_date, na.rm=T), sum(data_uncensored$vax2_date<=end_date, na.rm=T), 
                                sum(data_uncensored$vax3_date<=end_date, na.rm=T), sum(data_uncensored$vax4_date<=end_date, na.rm=T)),
    coverage_uncensored = round(N_vaccinated_uncensored/N_cohort_uncensored*100,1)
  )
names(collated) = c("Dose", "N (total)", "n vaccinated (total)", "Coverage (total), %",
                            "N (uncensored)", "n vaccinated (uncensored)", "Coverage (uncensored), %")

## Generate table
gt(collated) %>%
   tab_spanner(
    label = "total",
    columns = c("N (total)", "n vaccinated (total)", "Coverage (total), %")
  ) %>%
    tab_spanner(
    label = "uncensored",
    columns = c("N (uncensored)", "n vaccinated (uncensored)", "Coverage (uncensored), %")
  )
```
<br/>Dose 4 calculations restricted to individuals with a history of immunosuppression, haematologic cancer, or transplant on the index date (01-Dec-2020). Uncensored analyses restricted to individauls alive and registered throughout follow-up (01-Dec-2020 to 16-Feb-2022).<br/><br/>  

#### Product profile by dose
```{r}
## Dose 1
t_dose_dose1 = data.frame(table(data_cohort$vax1_type_descr)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 1")

## Dose 2
t_dose_dose2 = data.frame(table(data_cohort$vax2_type_descr)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 2")

## Dose 3
t_dose_dose3 = data.frame(table(data_cohort$vax3_type_descr)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 3")

## Dose 4
t_dose_dose4 = data.frame(table(data_cohort$vax4_type_descr)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 4")

# Generate combined table
collated = rbind(t_dose_dose1, t_dose_dose2, t_dose_dose3, t_dose_dose4)
collated %>% 
  gt(groupname_col = "Group") %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_options(table.font.size = pct(95))
```
<br/>Data for full cohort (censored/uncensored). Any counts of <=100 grouped as 'other'; all counts rounded to nearest 5; any rounded counts <=10 redacted.<br/><br/>  

```{r, fig.width=8, fig.height=3}
collated$Vaccine = factor(collated$Combination, levels = c("other", "Moderna", "ChAdOx1", "BNT162b2"))
collated$Dose = str_replace(collated$Group, "Dose ", "")

# Frequency plot
g1 = ggplot(collated, aes(fill=Vaccine, y=as.numeric(Frequency)/1000, x=Dose)) + 
    geom_bar(position="stack", stat="identity") +
    theme_bw() + ylab("N doses (thousands)") + scale_fill_manual(values = palette[c(4,2,1,3)]) +
    theme(legend.position="right") + xlab("Dose") +
    ggtitle("Product profile by dose (frequency)") +
    theme(legend.title = element_text(size=14), legend.text = element_text(size=12), 
        axis.text = element_text(size=14), axis.title = element_text(size=14))

# % plot
g2 = ggplot(collated, aes(fill=Vaccine, y=as.numeric(Percent), x=Dose)) + 
    geom_bar(position="stack", stat="identity") +
    theme_bw() + ylab("% doses") + scale_fill_manual(values = palette[c(4,2,1,3)]) +
    theme(legend.position="right") + xlab("Dose") +
    ggtitle("Product profile by dose (%)") +
    theme(legend.title = element_text(size=14), legend.text = element_text(size=12), 
        axis.text = element_text(size=14), axis.title = element_text(size=14))

plot_grid(g1, g2, ncol=2,  align="h", axis = c("tb"))
```
<br/>Data for full cohort (censored/uncensored).<br/><br/>

#### Product combinations across doses
```{r}
## Dose 1-2
t_dose_dose12 = data.frame(table(data_cohort$vax12_type)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 1-2 combination")

## Dose 1-2-3
t_dose_dose123 = data.frame(table(data_cohort$vax123_type)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 1-2-3 combination")

# Generate combined table
rbind(t_dose_dose12, t_dose_dose123) %>% 
  gt(groupname_col = "Group") %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_options(table.font.size = pct(95))
```
Data for full cohort (censored/uncensored). Any counts of <=100 grouped as 'other'; all counts rounded to nearest 5; any rounded counts <=10 redacted.<br/><br/>  

#### Dose interval distribution
```{r}
subset(table_1, Group=="Time between doses 1 and 2" | Group=="Time between doses 2 and 3") %>% 
  gt(groupname_col = "Group") %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_style(
    style = cell_text(indent = pct(5)),
    locations = cells_body(columns = "Variable")
    ) %>%
  tab_options(table.font.size = pct(95))
```
Data for full cohort (censored/uncensored). All counts rounded to nearest 5; any rounded counts <=10 or within <=10 of population total redacted.<br/><br/><br/><br/> 





#### Covariates associated with vaccine coverage: dose 2 by 01 July 2021

##### Approach (1): Cox proportional hazards
```{r}
data_cox <- read_rds(here::here("output", "data", "data_cox_coverage_dose2.rds"))

## Censored populations
total_vax = plyr::round_any(sum(data_cox$covid_vax),5)
total_N = plyr::round_any(nrow(data_cox),5)
vax_perc = round(total_vax/total_N*100,1)

## Uncensored population totals
total_vax_uncensored = plyr::round_any(sum(data_cox$uncensored_at_cut_off==1 & data_cox$unvax_uncensored_at_cut_off==0),5)
total_N_uncensored = plyr::round_any(sum(data_cox$uncensored_at_cut_off),5)
vax_perc_uncensored = round(total_vax_uncensored/total_N_uncensored*100,1)
```

Cox proportional hazards models were used to explore factors associated with completion of a 2-dose series via any product combination between **08-Dec-2020** and **01-Jul-2021** (at which point 2nd-dose vaccination had plateaued based on the coverage plots above).  
    
Follow-up was censored on the date of death, deregistration, or the end of the study period (01-Jul-2021). Overall coverage among individuals uncensored on 01-Jul-2021 was `r vax_perc_uncensored`% (`r prettyNum(total_vax_uncensored)` / `r prettyNum(total_N_uncensored)`, rounded to nearest 5). 
<br/><br/>
   
##### Model structure 
* Univariate models stratified by region were used to explore associations for each covariate in turn.    
* Partially adjusted stratified by region included the following covariates: age (5-cat), care home residence (1/0), healthcare worked status (1/0), end of life care (1/0), rurality (3-cat), sex (M/F), ethnicity (6-cat), IMD (5-cat), and prior COVID at baseline (1/0)    
* Fuly adjusted models stratified by region included all other covariates.
<br/><br/>

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
## Function to create clean table of dose-specific cox outputs
create_reduced_tbl = function(selected_dose=c("dose2", "dose3", "dose4full", "dose4subset")) {
  # example: selected_dose = "dose2"
  ## Import cox regression results
  tbl_summary <- read_rds(here::here("output", "model", paste0("mod_strat_coxph_redacted_",selected_dose,"_full.rds")))
  
  ## Add % unvaccinated at cut-off
  tbl_summary$perc_unvac <- round(as.numeric(tbl_summary$n_unvax_at_cut_off)/as.numeric(tbl_summary$n_uncensored_at_cut_off)*100,1)
  
  ## Select variables of interes
  tbl_reduced <- tbl_summary %>%
    select(var_group, var_label, label, n_obs,  n_event, n_uncensored_at_cut_off, perc_unvac,
           estimate_uni, conf.low_uni, conf.high_uni, p.value_uni,
           estimate_partial, conf.low_partial, conf.high_partial, p.value_partial,
           estimate, conf.low, conf.high, p.value)
  
  ## Relabel columns
  names(tbl_reduced) = c("var_group", "group", "level", "n (total)", "n (vaccinated)", "n (uncensored)", "% unvaccinated",
                              "HR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)",
                              "HR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)",
                              "HR (full)", "lower CI (full)", "upper CI (full)", "p (full)")
  return(tbl_reduced)
}

## Function to create formatted gt output
tabulate_reduced_tbl = function(input_tbl) {
  input_tbl %>% 
    gt(rowname_col = "level", groupname_col = "group") %>%
    tab_spanner(
      label = "univariate",
      columns = c("HR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)")
    ) %>%
      tab_spanner(
      label = "partially adjusted",
      columns = c("HR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)")
    ) %>%
    tab_spanner(
      label = "fully adjusted",
      columns = c("HR (full)", "lower CI (full)", "upper CI (full)", "p (full)")
    )  %>%
    cols_hide(columns = "var_group") %>%
    tab_options(table.font.size = pct(85)) %>%
     tab_style(
        style = list(
          cell_borders(
            sides = c("right"), color = "#cccccc"
          )
          ),
        locations = list(
          cells_body(
            columns = c("p (uni)", "p (multi)", "% unvaccinated")
          )
        )
     ) %>%
    tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold")
}

dose2_tbl = create_reduced_tbl("dose2")
tabulate_reduced_tbl(dose2_tbl)
```
All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding. % unvaccinated calculated among individuals who were uncensored at cut-off.<br/><br/>    

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
## Function to create plot of cox outputs
plot_reduced_tbl = function(input_tbl, dose4=FALSE) {
  ## Remove redacted components from plot
  input_tbl$`HR (multi)`[input_tbl$`HR (multi)`=="[Redacted]"] = NA
  input_tbl$`lower CI (multi)`[input_tbl$`HR (multi)`=="[Redacted]"] = NA
  input_tbl$`upper CI (multi)`[input_tbl$`HR (multi)`=="[Redacted]"] = NA
  
  ## Recode HRs and CIs as numerics
  input_tbl$`HR (multi)` = as.numeric(input_tbl$`HR (multi)`)
  input_tbl$`lower CI (multi)` = as.numeric(input_tbl$`lower CI (multi)`)
  input_tbl$`upper CI (multi)` = as.numeric(input_tbl$`upper CI (multi)`)
  
  ## Set plot min
  plot_min = 0.5
  if(min(input_tbl$`lower CI (multi)`, na.rm=T) < plot_min) { plot_min = min(input_tbl$`lower CI (multi)`, na.rm=T) }
  
  ## Set plot max
  plot_max = 2
  if(max(input_tbl$`upper CI (multi)`, na.rm=T) > plot_max) { plot_max = max(input_tbl$`upper CI (multi)`, na.rm=T) }
  
  ## Add redaction text variable
  input_tbl$redaction = NA
  input_tbl$redaction[input_tbl$`n (total)`=="[Redacted]"] = "[R]"
  
  ## Generate plot of HRs
  g1 = ggplot(input_tbl, aes(y = `HR (multi)`, x = level, colour = var_group)) + 
    geom_point(size = 2, alpha=0.8) +
    geom_text(aes(y = plot_min+0.02, label = redaction)) +
    geom_errorbar(aes(ymin=as.numeric(`lower CI (multi)`), ymax=as.numeric(`upper CI (multi)`), colour = var_group), width=0) + 
    coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
    theme_bw() + theme(strip.background = element_blank()) + labs(colour = "Group") +
    geom_hline(yintercept=1, linetype="dotted") + 
    ylab("Hazard ratio") + xlab("") +
    scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
    scale_y_continuous(trans="log",limits=c(plot_min, plot_max), breaks=c(0.5,1,2)) +
    theme(axis.title = element_text(size=12), axis.text = element_text(size=12), strip.text = element_blank(), 
          legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = c(-1.5,0.95))
  
  if (dose4==TRUE) { plot_min = min(input_tbl$`% unvaccinated`, na.rm=T)-10 } else { plot_min = 0 }
  if (dose4==TRUE) { plot_max = 100 } else { plot_max = max(input_tbl$`% unvaccinated`, na.rm=T)+5 }
  g2 = ggplot(input_tbl, aes(y = `% unvaccinated`, x = level,  colour = var_group)) + 
    geom_point(size = 2, alpha=0.8) +
    geom_segment(aes(xend=level), yend=0) +
    ylim(plot_min,plot_max) + coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
    theme_bw() + theme(strip.background = element_blank()) + 
    ylab("% Unvaccinated") + xlab("") +
    scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
    theme(axis.title = element_text(size=12), axis.text.x = element_text(size=12), axis.text.y = element_blank(), strip.text = element_blank(), 
          legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = "none")
  
  plot_grid(g1, g2, ncol=2,  align="h", axis = c("tb"), rel_widths = c(3,0.9))
}
plot_reduced_tbl(dose2_tbl)
```
<br/><br/> 





##### Approach (2): Logistic regression (sensitivity analysis)
```{r}
data_lr <- read_rds(here::here("output", "data", "data_lr.rds"))
total_vax = plyr::round_any(sum(data_lr$covid_vax),5)
total_N = plyr::round_any(nrow(data_lr),5)
vax_perc = round(total_vax/total_N*100,1)
```

Logistic regression models were used to explore factors associated with completion of a 2-dose series via any product combination by **01 Jul 2021** as a binary outcome variable. Individuals were included if they were registered and alive up to the analysis cut-off (N = `r prettyNum(total_N)`, rounded to nearest 5).    
    
Overall coverage as of **01 Jul 2021** was `r vax_perc`% (`r prettyNum(total_vax)` / `r prettyNum(total_N)`, rounded to nearest 5).    
    
Univariate models were used to explore the potential influence of each covariate in turn. Multivariate models adjusting for all other covariates were used to explore the potential influence of each covariate after adjusting for the effect of others.
<br/><br/>    

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
## Import logistic regression results
tbl_summary <- read_rds(here::here("output", "model", "mod_strat_logistic_redacted.rds"))

## Add % unvaccinated at cut-off
tbl_summary$perc_unvac <- round(100 - (as.numeric(tbl_summary$n_event) / as.numeric(tbl_summary$n_obs))*100,1)

## Select variables of interes
tbl_reduced <- tbl_summary %>%
   select(var_group, var_label, label, n_obs, n_event, perc_unvac,
         estimate_uni, conf.low_uni, conf.high_uni, p.value_uni,
         estimate_partial, conf.low_partial, conf.high_partial, p.value_partial,
         estimate, conf.low, conf.high, p.value)

## Relabel columns
names(tbl_reduced) = c("var_group", "group", "level", "n (total)", "n (vaccinated)", "% unvaccinated",
                            "OR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)",
                            "OR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)",
                            "OR (full)", "lower CI (full)", "upper CI (full)", "p (full)")

## Create formatted gt output
tbl_reduced %>% 
  gt(rowname_col = "level", groupname_col = "group") %>%
  tab_spanner(
    label = "univariate",
    columns = c("OR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)")
  ) %>%
    tab_spanner(
    label = "partially adjusted",
    columns = c("OR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)")
  ) %>%
  tab_spanner(
    label = "fully adjusted",
    columns = c("OR (full)", "lower CI (full)", "upper CI (full)", "p (full)")
  ) %>%
  cols_hide(columns = "var_group") %>%
  tab_options(table.font.size = pct(85)) %>%
   tab_style(
      style = list(
        cell_borders(
          sides = c("right"), color = "#cccccc"
        )
        ),
      locations = list(
        cells_body(
          columns = c("p (uni)", "p (multi)", "% unvaccinated")
        )
      )
   ) %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_footnote(
    footnote = "All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), 
            n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding.",
    locations = cells_column_labels(columns = "n (vaccinated)")
  ) %>%
  tab_footnote(
    footnote = "Calculated among individuals who were uncensored at cut-off.",
    locations = cells_column_labels(columns = "% unvaccinated")
  )
```
<br/><br/>     

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
## Remove redacted components from plot
tbl_reduced$`OR (multi)`[tbl_reduced$`OR (multi)`=="[Redacted]"] = NA
tbl_reduced$`lower CI (multi)`[tbl_reduced$`OR (multi)`=="[Redacted]"] = NA
tbl_reduced$`upper CI (multi)`[tbl_reduced$`OR (multi)`=="[Redacted]"] = NA

## Recode ORs and CIs as numerics
tbl_reduced$`OR (multi)` = as.numeric(tbl_reduced$`OR (multi)`)
tbl_reduced$`lower CI (multi)` = as.numeric(tbl_reduced$`lower CI (multi)`)
tbl_reduced$`upper CI (multi)` = as.numeric(tbl_reduced$`upper CI (multi)`)

## Set plot min
plot_min = 0.5
if(min(tbl_reduced$`lower CI (multi)`, na.rm=T) < plot_min) { plot_min = min(tbl_reduced$`lower CI (multi)`, na.rm=T) }

## Set plot max
plot_max = 2
if(max(tbl_reduced$`upper CI (multi)`, na.rm=T) > plot_max) { plot_max = max(tbl_reduced$`upper CI (multi)`, na.rm=T) }

## Add redaction text variable
tbl_reduced$redaction = NA
tbl_reduced$redaction[tbl_reduced$`n (total)`=="[Redacted]"] = "[R]"

## Generate plot of HRs
g1 = ggplot(tbl_reduced, aes(y = `OR (multi)`, x = level, colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_text(aes(y = plot_min+0.02, label = redaction)) +
  geom_errorbar(aes(ymin=as.numeric(`lower CI (multi)`), ymax=as.numeric(`upper CI (multi)`), colour = var_group), width=0) + 
  coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + labs(colour = "Group") +
  geom_hline(yintercept=1, linetype="dotted") + 
  ylab("Odds ratio") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  scale_y_continuous(trans="log",limits=c(plot_min, plot_max), breaks=c(0.5,1,2)) +
  theme(axis.title = element_text(size=12), axis.text = element_text(size=12), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = c(-1.5,0.95))


plot_max = max(tbl_reduced$`% unvaccinated`, na.rm=T)+5
g2 = ggplot(tbl_reduced, aes(y = `% unvaccinated`, x = level,  colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_segment(aes(xend=level), yend=0) +
  ylim(0,plot_max) + coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + 
  ylab("% Unvaccinated") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  theme(axis.title = element_text(size=12), axis.text.x = element_text(size=12), axis.text.y = element_blank(), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = "none")

plot_grid(g1, g2, ncol=2,  align="h", axis = c("tb"), rel_widths = c(3,0.9))
```
<br/><br/><br/><br/>





#### Covariates associated with vaccine coverage: dose 3 by 16 Feb 2022

##### Cox proportional hazards
```{r}
data_cox <- read_rds(here::here("output", "data", "data_cox_coverage_dose3.rds"))

## Censored populations
total_vax = plyr::round_any(sum(data_cox$covid_vax),5)
total_N = plyr::round_any(nrow(data_cox),5)
vax_perc = round(total_vax/total_N*100,1)

## Uncensored population totals
total_vax_uncensored = plyr::round_any(sum(data_cox$uncensored_at_cut_off==1 & data_cox$unvax_uncensored_at_cut_off==0),5)
total_N_uncensored = plyr::round_any(sum(data_cox$uncensored_at_cut_off),5)
vax_perc_uncensored = round(total_vax_uncensored/total_N_uncensored*100,1)
```

Follow-up was censored on the date of death, deregistration, or the end of the study period (16-Feb-2022). Overall coverage among individuals uncensored on 16-Feb-2022 was `r vax_perc_uncensored`% (`r prettyNum(total_vax_uncensored)` / `r prettyNum(total_N_uncensored)`, rounded to nearest 5). 
<br/><br/>

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
dose3_tbl = create_reduced_tbl("dose3")
tabulate_reduced_tbl(dose3_tbl)
```
<br/><br/>    

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
plot_reduced_tbl(dose3_tbl)
```
<br/><br/><br/><br/>





#### Covariates associated with vaccine coverage: dose 4 by 16 Feb 2022 (full cohort)

##### Cox proportional hazards
```{r}
data_cox <- read_rds(here::here("output", "data", "data_cox_coverage_dose4full.rds"))

## Censored populations
total_vax = plyr::round_any(sum(data_cox$covid_vax),5)
total_N = plyr::round_any(nrow(data_cox),5)
vax_perc = round(total_vax/total_N*100,1)

## Uncensored population totals
total_vax_uncensored = plyr::round_any(sum(data_cox$uncensored_at_cut_off==1 & data_cox$unvax_uncensored_at_cut_off==0),5)
total_N_uncensored = plyr::round_any(sum(data_cox$uncensored_at_cut_off),5)
vax_perc_uncensored = round(total_vax_uncensored/total_N_uncensored*100,1)
```

Follow-up was censored on the date of death, deregistration, or the end of the study period (16-Feb-2022). Overall coverage among individuals uncensored on 16-Feb-2022 was `r vax_perc_uncensored`% (`r prettyNum(total_vax_uncensored)` / `r prettyNum(total_N_uncensored)`, rounded to nearest 5). 
<br/><br/>

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
dose4full_tbl = create_reduced_tbl("dose4full")
tabulate_reduced_tbl(dose4full_tbl)
```
<br/><br/>    

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
plot_reduced_tbl(dose4full_tbl, dose4=TRUE)
```
<br/><br/><br/><br/>





#### Covariates associated with vaccine coverage: dose 4 by 16 Feb 2022 (subset)

**Same analyses  restricted to individuals with a history of immunosuppression, haematologic cancer, or transplant on the index date (01-Dec-2020).**

##### Cox proportional hazards
```{r}
data_cox <- read_rds(here::here("output", "data", "data_cox_coverage_dose4subset.rds"))

## Censored populations
total_vax = plyr::round_any(sum(data_cox$covid_vax),5)
total_N = plyr::round_any(nrow(data_cox),5)
vax_perc = round(total_vax/total_N*100,1)

## Uncensored population totals
total_vax_uncensored = plyr::round_any(sum(data_cox$uncensored_at_cut_off==1 & data_cox$unvax_uncensored_at_cut_off==0),5)
total_N_uncensored = plyr::round_any(sum(data_cox$uncensored_at_cut_off),5)
vax_perc_uncensored = round(total_vax_uncensored/total_N_uncensored*100,1)
```

Follow-up was censored on the date of death, deregistration, or the end of the study period (16-Feb-2022). Overall coverage among individuals uncensored on 16-Feb-2022 was `r vax_perc_uncensored`% (`r prettyNum(total_vax_uncensored)` / `r prettyNum(total_N_uncensored)`, rounded to nearest 5). 
<br/><br/>

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
dose4subset_tbl = create_reduced_tbl("dose4subset")
tabulate_reduced_tbl(dose4subset_tbl)
```
<br/><br/>    

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
plot_reduced_tbl(dose4subset_tbl, dose4=TRUE)
```
<br/><br/><br/><br/>







#### Subgroup analyses

##### Dose 2 summary
```{r}
## Function to create clean table of dose-specific cox subgroup outputs
create_reduced_tbl_subgroup = function(selected_dose=c("dose2", "dose3", "dose4full", "dose4subset")) {
  # Example: selected_dose = "dose2"
  
  # Define strata
  subgroups = c("CKD3a (D-T-)", "CKD3b (D-T-)", "CKD4-5 (D-T-)", "CKD (T+)", "CKD (D+T-)")
  
  # Drop CDK (D+T-) from dose4subset due to low N
  if (selected_dose == "dose4subset") { subgroups = subgroups[subgroups!="CKD (D+T-)"]} 
  
  ## Import cox regression results for subgroup analyses
  for (i in 1:length(subgroups)) {
    tbl_subset <- read_rds(here::here("output", "model", paste0("mod_strat_coxph_redacted_",selected_dose,"_",subgroups[i],".rds")))
    tbl_subset$subgroup = subgroups[i]
    tbl_subset$subgroup_id = i
    if (i == 1) { tbl_summary = tbl_subset } else { tbl_summary = rbind(tbl_summary, tbl_subset) }
  }

  ## Add % unvaccinated at cut-off
  tbl_summary$perc_unvac <- round(as.numeric(tbl_summary$n_unvax_at_cut_off)/as.numeric(tbl_summary$n_uncensored_at_cut_off)*100,1)
  return(tbl_summary)
}

## Function to create formatted gt output
tabulate_reduced_tbl_subgroup = function(input_tbl, selected_dose=c("dose2", "dose3", "dose4full", "dose4subset")) { 
  # Example: input_tbl = tbl_summary

  ## Select variables of interes
  tbl_reduced <- input_tbl %>%
    mutate(
      # Collate summary outputs
      HR_summary_uni = paste0(estimate_uni," (", conf.low,"-",conf.high,")"),
      HR_summary_partial = paste0(estimate_partial," (", conf.low,"-",conf.high,")"),
      HR_summary_full = paste0(estimate_uni," (", conf.low,"-",conf.high,")"),
      
      # Clean summary outputs
      HR_summary_uni = ifelse(HR_summary_uni=="[Redacted] ([Redacted]-[Redacted])", "[Redacted]", HR_summary_uni),
      HR_summary_partial = ifelse(HR_summary_partial=="[Redacted] ([Redacted]-[Redacted])", "[Redacted]", HR_summary_partial),
      HR_summary_full = ifelse(HR_summary_full=="[Redacted] ([Redacted]-[Redacted])", "[Redacted]", HR_summary_full),
      
      HR_summary_uni = ifelse(HR_summary_uni=="1 (NA-NA)", "1", HR_summary_uni),
      HR_summary_partial = ifelse(HR_summary_partial=="1 (NA-NA)", "1", HR_summary_partial),
      HR_summary_full = ifelse(HR_summary_full=="1 (NA-NA)", "1", HR_summary_full)
    ) %>%
    select(subgroup, subgroup_id, var_group, var_label, label, n_obs, n_uncensored_at_cut_off, perc_unvac,
           HR_summary_uni, HR_summary_partial, HR_summary_full)
  
  ## Relabel columns
  names(tbl_reduced) = c("subgroup", "subgroup_id", "var_group", "group", "level", "n (total)", "n (uncen)", "% unvax", "HR uni", "HR partial", "HR full")

  ## Pivot to wide format based on subgroup
  tbl_wide = tbl_reduced %>% 
    pivot_wider(    
      names_from = c(subgroup, subgroup_id),
      values_from = c(`n (total)`, `n (uncen)`, `% unvax`, `HR uni`, `HR partial`, `HR full`),
      names_glue = "{.value} [{subgroup_id}]"
    ) 
  
  ## Generate table
  tbl_wide = tbl_wide %>%
    gt(rowname_col = "level", groupname_col = "group") %>%
    tab_spanner(
      label = "CKD3a (D-T-)",
      columns = paste0(c("n (total)", "n (uncen)", "% unvax", "HR uni", "HR partial", "HR full")," [1]")
    )  %>%
    tab_spanner(
      label = "CKD3b (D-T-)",
      columns = paste0(c("n (total)", "n (uncen)", "% unvax", "HR uni", "HR partial", "HR full")," [2]")
    )  %>%
    tab_spanner(
      label = "CKD4-5 (D-T-)",
      columns = paste0(c("n (total)", "n (uncen)", "% unvax", "HR uni", "HR partial", "HR full")," [3]")
    )  %>%
    tab_spanner(
      label = "CKD (T+)",
      columns = paste0(c("n (total)", "n (uncen)", "% unvax", "HR uni", "HR partial", "HR full")," [4]")
    )  %>%
    cols_hide(columns = "var_group") %>%
    tab_options(table.font.size = pct(70)) %>%
     tab_style(
        style = list(
          cell_borders(
            sides = c("right"), color = "#cccccc"
          )
          ),
        locations = list(
          cells_body(
            columns = starts_with("HR full")
          )
        )
     ) %>%
    tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold")

    if (selected_dose != "dose4subset") { 
      tbl_wide = tbl_wide %>%
        tab_spanner(
          label = "CKD (D+T-)",
          columns = paste0(c("n (total)", "n (uncen)", "% unvax", "HR uni", "HR partial", "HR full")," [5]")
        ) 
      } 
  return(tbl_wide)
}

## Create table for dose 2 data
dose2_tbl_subgroup = create_reduced_tbl_subgroup("dose2")
tabulate_reduced_tbl_subgroup(dose2_tbl_subgroup, "dose2")
```
<br/>All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding. % unvaccinated calculated among individuals who were uncensored at cut-off.
<br/><br/>

##### Dose 2 plot
```{r, fig.width=13, fig.height=10}
## Function to create plot of cox subgroup outputs 
plot_reduced_tbl_subgroup = function(input_tbl) {
  ## Example: input_tbl = dose2_tbl_subgroup
  
  ## Remove redacted components from plot
  input_tbl$estimate_partial[input_tbl$estimate_partial=="[Redacted]"] = NA
  input_tbl$conf.low_partial[input_tbl$conf.low_partial=="[Redacted]"] = NA
  input_tbl$conf.high_partial[input_tbl$conf.high_partial=="[Redacted]"] = NA
  
  ## Recode HRs and CIs as numerics
  input_tbl$estimate_partial = as.numeric(input_tbl$estimate_partial)
  input_tbl$conf.low_partial = as.numeric(input_tbl$conf.low_partial)
  input_tbl$conf.high_partial = as.numeric(input_tbl$conf.high_partial)
  
  ## Set CKD factor levels
  input_tbl$subgroup = factor(input_tbl$subgroup, level = c("CKD3a (D-T-)", "CKD3b (D-T-)", "CKD4-5 (D-T-)", "CKD (T+)", "CKD (D+T-)"))
  
  ## Set plot min
  plot_min = 0.5
  if(min(input_tbl$conf.low_partial, na.rm=T) < plot_min) { plot_min = min(input_tbl$conf.low_partial, na.rm=T) }
  
  ## Set plot max
  plot_max = 2
  if(max(input_tbl$conf.high_partial, na.rm=T) > plot_max) { plot_max = max(input_tbl$conf.high_partial, na.rm=T) }
  
  ## Add redaction text variable
  input_tbl$redaction = NA
  input_tbl$redaction[input_tbl$n_obs=="[Redacted]"] = "[R]"
  
  ## Generate plot of HRs
  ggplot(input_tbl, aes(y = estimate_partial, x = label, colour = var_group)) + 
    geom_point(size = 2, alpha=0.8) +
    geom_text(aes(y = plot_min+0.02, label = redaction)) +
    geom_errorbar(aes(ymin=as.numeric(conf.low_partial), ymax=as.numeric(conf.high_partial), colour = var_group), width=0) + 
    coord_flip() + facet_grid(var_label~subgroup, scales = "free", space = "free") + 
    theme_bw() + theme(strip.background = element_blank()) + labs(colour = "Group") +
    geom_hline(yintercept=1, linetype="dotted") + 
    ylab("Hazard ratio") + xlab("") +
    scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
    scale_y_continuous(trans="log",limits=c(plot_min, plot_max), breaks=c(0.5,1,2)) +
    theme(axis.title = element_text(size=12), axis.text = element_text(size=12), strip.text.y = element_blank(), strip.text.x = element_text(size=12), 
          legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = c(-1.5,0.95))
}
plot_reduced_tbl_subgroup(dose2_tbl_subgroup)
```
<br/><br/><br/><br/>  

##### Dose 3 summary
```{r}
tbl_subgroup = create_reduced_tbl_subgroup("dose3")
tabulate_reduced_tbl_subgroup(tbl_subgroup, "dose3")
```
<br/>All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding. % unvaccinated calculated among individuals who were uncensored at cut-off.
<br/><br/>   

##### Dose 3 plot
```{r, fig.width=13, fig.height=10}
plot_reduced_tbl_subgroup(tbl_subgroup)
```
<br/><br/><br/><br/>   





##### Dose 4 summary (full cohort)
```{r}
tbl_subgroup = create_reduced_tbl_subgroup("dose4full")
tabulate_reduced_tbl_subgroup(tbl_subgroup, "dose4full")
```
<br/>All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding. % unvaccinated calculated among individuals who were uncensored at cut-off.
<br/><br/>  

##### Dose 4 plot (full cohort)
```{r, fig.width=13, fig.height=10}
plot_reduced_tbl_subgroup(tbl_subgroup)
```
<br/><br/><br/><br/>  





##### Dose 4 summary (subset)
```{r}
tbl_subgroup = create_reduced_tbl_subgroup("dose4subset")
tabulate_reduced_tbl_subgroup(tbl_subgroup, "dose4subset")
```
<br/>All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding. % unvaccinated calculated among individuals who were uncensored at cut-off.
<br/><br/>  

##### Dose 4 plot (subset)
```{r, fig.width=13, fig.height=10}
plot_reduced_tbl_subgroup(tbl_subgroup)
```
<br/><br/><br/><br/>  




##### Session info
```{r}
print(sessionInfo())
```

