---
title: "Factors associated with COVID-19 vaccine coverage in chronic kidney disease patients"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

## Import libraries
library('here')
library('tidyverse')
library('readr')
library('tidyr')
library('lubridate')
library('glue')
library('gt')
library('gtsummary')
library('reshape2')
library('kableExtra')
library('cowplot')
library('fs')

## Import custom user functions
source(here::here("analysis", "functions.R"))

## Import data
data_cohort <- read_rds(here::here("output", "data", "data_cohort_coverage.rds"))
rounded_n = plyr::round_any(nrow(data_cohort), 5)

if (data_cohort$mock_data_flag[1]==1) { flag = "present" } else { flag = "absent" }
```
<br/><br/>  

#### Background
Chronic kidney disease (CKD) is a significant risk factor for COVID-19-related mortality. Although vaccination has the potential to mitigate this risk, CKD has been linked with impaired COVID-19 vaccine immunogenicity and high rates of breakthrough infection among individuals who have received a 2-dose primary vaccine series.

Vaccine recommendations for CKD patients in the UK have evolved over time (see [protocol](https://docs.google.com/document/d/1w48W-bCMfn0RdkfxlU6fbRkPv3MnIYd3/edit#heading=h.1fob9te). Relative uptake of different vaccines in this population remains uncertain, as does the relative vaccine effectiveness (VE) of different regimens, including homologous versus heterologous vaccine usage. This project seeks to address these key evidence gaps.

#### Inclusion criteria
* Registered for at least 3m before index date (01-Dec-2020)    
* Alive on index date    
* Aged ≥16 and <120 on index date
* eGFR<60 in 2 years before 01 Dec 2020 OR dialysis code (opensafely/dialysis/3ce108ac) OR kidney transplant code (opensafely/kidney-transplant//2020-07-15)    
* No missing demographic data   
* Maximum of 4 COVID-19 doses recorded
* No vaccines administered at an interval of <14 days

A total of **`r prettyNum(rounded_n)`** (rounded to the nearest 5) met the inclusion criteria (see *output/data/flowchart.csv* for additional details).    
`r if(flag=="present") { paste0("NB: Dummy data processing flag detected!") }`    
<br/><br/><br/><br/>    

#### Table 1: Summary of population
```{r}
table_1 <- read_rds(here::here("output", "tables", "table1_coverage_redacted.rds"))

## Set factor levels for group
table_1$Group[table_1$Group=="Other"] = "Risk group"

subset(table_1, Group!="Time between doses 1 and 2" & Group!="Time between doses 2 and 3") %>% 
   gt(groupname_col = "Group") %>%
   tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
   tab_style(
     style = cell_text(indent = pct(5)),
     locations = cells_body(columns = "Variable")
     ) %>%
   tab_options(table.font.size = pct(95)) %>% #table.width = pct(80) 
   tab_footnote(
     footnote = "All counts rounded to nearest 5; any rounded counts <=10 or within <=10 of population total redacted.",
     locations = cells_column_labels(columns = "Count")
   )
```
<br/><br/>    

#### Coverage over time
```{r, message=FALSE, fig.width=8, fig.height=8}
# Create vector of dates between first and last recorded vaccines
campaign_start <- min(data_cohort$vax1_date, na.rm=T)
end_date <- max(c(data_cohort$vax1_date, data_cohort$vax2_date, data_cohort$vax3_date, data_cohort$vax4_date), na.rm=T)

# create vector containing every other week
date_vec <- seq(campaign_start, end_date, by="weeks")
date_vec <- date_vec[seq(1, length(date_vec), 2)]

# set rounding factor
rounding_cutoff = 10

# cumulative table
t_all <- data.frame(date = date_vec)
for (i in 1:nrow(t_all)) {
  date_ref = t_all$date[i]
  t_all$dose1_total[i] = plyr::round_any(sum(data_cohort$vax1_date<date_ref, na.rm=T), rounding_cutoff)
  t_all$dose2_total[i] = plyr::round_any(sum(data_cohort$vax2_date<date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose3_total[i] = plyr::round_any(sum(data_cohort$vax3_date<date_ref, na.rm=T), rounding_cutoff)
  t_all$dose4_total[i] = plyr::round_any(sum(data_cohort$vax4_date<date_ref, na.rm=T), rounding_cutoff)

  t_all$dose1_pfizer[i] = plyr::round_any(sum(data_cohort$vax1_type=="pfizer" & data_cohort$vax1_date<date_ref, na.rm=T), rounding_cutoff)
  t_all$dose2_pfizer[i] = plyr::round_any(sum(data_cohort$vax2_type=="pfizer" & data_cohort$vax2_date<date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose3_pfizer[i] = plyr::round_any(sum(data_cohort$vax2_type=="pfizer" & data_cohort$vax3_date<date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose4_pfizer[i] = plyr::round_any(sum(data_cohort$vax2_type=="pfizer" & data_cohort$vax4_date<date_ref, na.rm=T), rounding_cutoff)

  t_all$dose1_az[i] = plyr::round_any(sum(data_cohort$vax1_type=="az" & data_cohort$vax1_date<date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose2_az[i] = plyr::round_any(sum(data_cohort$vax2_type=="az" & data_cohort$vax2_date<date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose3_az[i] = plyr::round_any(sum(data_cohort$vax3_type=="az" & data_cohort$vax3_date<date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose4_az[i] = plyr::round_any(sum(data_cohort$vax4_type=="az" & data_cohort$vax4_date<date_ref, na.rm=T), rounding_cutoff)

  t_all$dose1_moderna[i] = plyr::round_any(sum(data_cohort$vax1_type=="moderna" & data_cohort$vax1_date<date_ref, na.rm=T), rounding_cutoff)
  t_all$dose2_moderna[i] = plyr::round_any(sum(data_cohort$vax2_type=="moderna" & data_cohort$vax2_date<date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose3_moderna[i] = plyr::round_any(sum(data_cohort$vax3_type=="moderna" & data_cohort$vax3_date<date_ref, na.rm=T), rounding_cutoff) 
  t_all$dose4_moderna[i] = plyr::round_any(sum(data_cohort$vax4_type=="moderna" & data_cohort$vax4_date<date_ref, na.rm=T), rounding_cutoff)
  
  t_all$az_az[i] = plyr::round_any(sum(data_cohort$vax2_date<date_ref & data_cohort$vax12_type=="az-az", na.rm=T), rounding_cutoff)
  t_all$pfizer_pfizer[i] = plyr::round_any(sum(data_cohort$vax2_date<date_ref & data_cohort$vax12_type=="pfizer-pfizer", na.rm=T), rounding_cutoff)
  t_all$moderna_moderna[i] = plyr::round_any(sum(data_cohort$vax2_date<date_ref & data_cohort$vax12_type=="moderna-moderna", na.rm=T), rounding_cutoff)
  t_all$heterologous_dose2[i] = plyr::round_any(sum(data_cohort$vax2_date<date_ref & (data_cohort$vax1_type!=data_cohort$vax2_type), na.rm=T), rounding_cutoff)
}

# Save as html ----
write_csv(t_all, here::here("output", "tables", "coverage_over_time_rounded.csv"))

# Plot cumulative distribution
palette = c("#3B9AB2","#78B7C5","#EBCC2A","#E1AF00","#B40F20")
t_plot = rbind(
  data.frame(dose = "dose 1", total = t_all$dose1_total, date = t_all$date),
  data.frame(dose = "dose 2", total = t_all$dose2_total, date = t_all$date),
  data.frame(dose = "dose 3", total = t_all$dose3_total, date = t_all$date),
  data.frame(dose = "dose 4", total = t_all$dose4_total, date = t_all$date)
)
plot_max = max(t_plot$total)*1.1
g1 = ggplot(t_plot, aes(x = date, y = total, colour = dose)) + geom_line() +
          theme_bw()+ scale_colour_manual(values = palette[c(1,2,4,5)]) +
          theme(legend.position="right") + 
  ggtitle("Any vaccine") +
  theme(legend.title = element_text(size=14), legend.text = element_text(size=12), axis.text = element_text(size=14), axis.title = element_text(size=14)) +
  scale_y_continuous(
    name = "doses given", limits=c(0,plot_max),
    sec.axis = sec_axis(~ ./rounded_n*100, name="%", breaks= c(0,25,50,75,100))
  )

# Plot cumulative product-specific vaccination
palette = c("#003c30","#b2182b","#74add1","grey")
t_plot = rbind(
  data.frame(product = "2 x ChAdOx1-S", total = t_all$az_az, date = t_all$date),
  data.frame(product = "2 x Pfizer", total = t_all$pfizer_pfizer, date = t_all$date),
  data.frame(product = "2 x Moderna", total = t_all$moderna_moderna, date = t_all$date),
  data.frame(product = "Heterologous", total = t_all$heterologous, date = t_all$date)
)
plot_max = max(t_plot$total)*1.1
g2 = ggplot(t_plot, aes(x = date, y = total, colour = product)) + geom_line() +
          theme_bw() + ylab("doses given") + scale_colour_manual(values = palette[c(1,2,3,4)]) +
          theme(legend.position="right") +
  ggtitle("Product-specific vaccination (primary series)") +
  theme(legend.title = element_text(size=14), legend.text = element_text(size=12), axis.text = element_text(size=14), axis.title = element_text(size=14)) +
  scale_y_continuous(
    name = "doses given", limits=c(0,plot_max),
    sec.axis = sec_axis(~ ./rounded_n*100, name="%", breaks= c(0,25,50,75,100))
  )
plot_grid(g1, g2, ncol=1,  align="v", axis = c("lr"))
```
<br/>Numbers rounded to the nearest 10 before plotting.     
<br/><br/>    

#### Product profile by dose
```{r}
## Dose 1
t_dose_dose1 = data.frame(table(data_cohort$vax1_type_descr)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 1")

## Dose 2
t_dose_dose2 = data.frame(table(data_cohort$vax2_type_descr)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 2")

## Dose 3
t_dose_dose3 = data.frame(table(data_cohort$vax3_type_descr)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 3")

## Dose 4
t_dose_dose4 = data.frame(table(data_cohort$vax4_type_descr)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 4")

# Generate combined table
collated = rbind(t_dose_dose1, t_dose_dose2, t_dose_dose3, t_dose_dose4)
collated %>% 
  gt(groupname_col = "Group") %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_options(table.font.size = pct(95)) %>% #table.width = pct(80) 
  tab_footnote(
    footnote = "Any counts of <=100 grouped as 'other'; all counts rounded to nearest 5; any rounded counts <=10 redacted.",
    locations = cells_column_labels(columns = "Frequency")
  )
```
<br/><br/>  

```{r, fig.width=8, fig.height=3}
collated$Vaccine = factor(collated$Combination, levels = c("other", "Moderna", "ChAdOx1", "BNT162b2"))
collated$Dose = str_replace(collated$Group, "Dose ", "")

# Frequency plot
g1 = ggplot(collated, aes(fill=Vaccine, y=as.numeric(Frequency)/1000, x=Dose)) + 
    geom_bar(position="stack", stat="identity") +
    theme_bw() + ylab("N doses (thousands)") + scale_fill_manual(values = palette[c(4,2,1,3)]) +
    theme(legend.position="right") + xlab("Dose") +
    ggtitle("Product profile by dose (frequency)") +
    theme(legend.title = element_text(size=14), legend.text = element_text(size=12), 
        axis.text = element_text(size=14), axis.title = element_text(size=14))

# % plot
g2 = ggplot(collated, aes(fill=Vaccine, y=as.numeric(Percent), x=Dose)) + 
    geom_bar(position="stack", stat="identity") +
    theme_bw() + ylab("% doses") + scale_fill_manual(values = palette[c(4,2,1,3)]) +
    theme(legend.position="right") + xlab("Dose") +
    ggtitle("Product profile by dose (%)") +
    theme(legend.title = element_text(size=14), legend.text = element_text(size=12), 
        axis.text = element_text(size=14), axis.title = element_text(size=14))

plot_grid(g1, g2, ncol=2,  align="h", axis = c("tb"))
```
<br/><br/>

#### Product combinations across doses
```{r}
## Dose 1-2
t_dose_dose12 = data.frame(table(data_cohort$vax12_type)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 1-2 combination")

## Dose 1-2-3
t_dose_dose123 = data.frame(table(data_cohort$vax123_type)) %>% 
  redact_table() %>%
  mutate(Group = "Dose 1-2-3 combination")

# Generate combined table
rbind(t_dose_dose12, t_dose_dose123) %>% 
  gt(groupname_col = "Group") %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_options(table.font.size = pct(95)) %>% #table.width = pct(80) 
  tab_footnote(
    footnote = "Any counts of <=100 grouped as 'other'; all counts rounded to nearest 5; any rounded counts <=10 redacted.",
    locations = cells_column_labels(columns = "Frequency")
  )
```
<br/><br/>  

#### Dose interval distribution
```{r}
subset(table_1, Group=="Time between doses 1 and 2" | Group=="Time between doses 2 and 3") %>% 
  gt(groupname_col = "Group") %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_style(
    style = cell_text(indent = pct(5)),
    locations = cells_body(columns = "Variable")
    ) %>%
  tab_options(table.font.size = pct(95)) %>% #table.width = pct(80) 
  tab_footnote(
    footnote = "All counts rounded to nearest 5; any rounded counts <=10 or within <=10 of population total redacted.",
    locations = cells_column_labels(columns = "Count")
  )
```
<br/><br/><br/><br/> 

#### Covariates associated with vaccine coverage: dose 2 by 01 July 2021

##### Approach (1): Cox proportional hazards
```{r}
data_cox <- read_rds(here::here("output", "data", "data_cox_coverage_dose2.rds"))
total_vax = plyr::round_any(sum(data_cox$covid_vax),5)
total_N = plyr::round_any(nrow(data_cox),5)
vax_perc = round(total_vax/total_N*100,1)
```

Cox proportional hazards models were used to explore factors associated with completion of a 2-dose series via any product combination between **08 Dec 2020** and **01 Jul 2021** (at which point 2nd-dose vaccination had plateaued based on the coverage plots above).  
    
Overall coverage as of **01 Jul 2021** was `r vax_perc`% (`r prettyNum(total_vax)` / `r prettyNum(total_N)`, rounded to nearest 5). Follow-up was censored on the date of death, deregistration, or the end of the study period (01 Jul 2021).     
    
Univariate models stratified by region were used to explore the potential influence of each covariate in turn. Multivariate models stratified by region, adjusting for all other covariates, were used to explore the potential influence of each covariate after adjusting for the effect of others.
<br/><br/>   

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
## Import cox regression results
tbl_summary <- read_rds(here::here("output", "model", "mod_strat_coxph_redacted_dose2.rds")) 

## Add % unvaccinated at cut-off
tbl_summary$perc_unvac <- round(as.numeric(tbl_summary$n_unvax_at_cut_off)/as.numeric(tbl_summary$n_uncensored_at_cut_off)*100,1)

## Select variables of interes
tbl_reduced <- tbl_summary %>%
  select(var_group, var_label, label, n_obs,  n_event, n_uncensored_at_cut_off, perc_unvac,
         estimate_uni, conf.low_uni, conf.high_uni, p.value_uni,
         estimate_partial, conf.low_partial, conf.high_partial, p.value_partial,
         estimate, conf.low, conf.high, p.value)

## Relabel columns
names(tbl_reduced) = c("var_group", "group", "level", "n (total)", "n (vaccinated)", "n (uncensored)", "% unvaccinated",
                            "HR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)",
                            "HR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)",
                            "HR (full)", "lower CI (full)", "upper CI (full)", "p (full)")

## Create formatted gt output
tbl_reduced %>% 
  gt(rowname_col = "level", groupname_col = "group") %>%
  tab_spanner(
    label = "univariate",
    columns = c("HR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)")
  ) %>%
    tab_spanner(
    label = "partially adjusted",
    columns = c("HR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)")
  ) %>%
  tab_spanner(
    label = "fully adjusted",
    columns = c("HR (full)", "lower CI (full)", "upper CI (full)", "p (full)")
  )  %>%
  cols_hide(columns = "var_group") %>%
  tab_options(table.font.size = pct(85)) %>%
   tab_style(
      style = list(
        cell_borders(
          sides = c("right"), color = "#cccccc"
        )
        ),
      locations = list(
        cells_body(
          columns = c("p (uni)", "p (multi)", "% unvaccinated")
        )
      )
   ) %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_footnote(
    footnote = "All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), 
            n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding.",
    locations = cells_column_labels(columns = "n (vaccinated)")
  )  %>%
  tab_footnote(
    footnote = "n (unvaccinated and uncensored)/n (uncensored)*100",
    locations = cells_column_labels(columns = "% unvaccinated")
  )
```
<br/><br/>    

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
## Remove redacted components from plot
tbl_reduced$`HR (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA
tbl_reduced$`lower CI (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA
tbl_reduced$`upper CI (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA

## Recode HRs and CIs as numerics
tbl_reduced$`HR (multi)` = as.numeric(tbl_reduced$`HR (multi)`)
tbl_reduced$`lower CI (multi)` = as.numeric(tbl_reduced$`lower CI (multi)`)
tbl_reduced$`upper CI (multi)` = as.numeric(tbl_reduced$`upper CI (multi)`)

## Set plot min
plot_min = 0.5
if(min(tbl_reduced$`lower CI (multi)`, na.rm=T) < plot_min) { plot_min = min(tbl_reduced$`lower CI (multi)`, na.rm=T) }

## Set plot max
plot_max = 2
if(max(tbl_reduced$`upper CI (multi)`, na.rm=T) > plot_max) { plot_max = max(tbl_reduced$`upper CI (multi)`, na.rm=T) }

## Add redaction text variable
tbl_reduced$redaction = NA
tbl_reduced$redaction[tbl_reduced$`n (total)`=="[Redacted]"] = "[R]"

## Generate plot of HRs
g1 = ggplot(tbl_reduced, aes(y = `HR (multi)`, x = level, colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_text(aes(y = plot_min+0.02, label = redaction)) +
  geom_errorbar(aes(ymin=as.numeric(`lower CI (multi)`), ymax=as.numeric(`upper CI (multi)`), colour = var_group), width=0) + 
  coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + labs(colour = "Group") +
  geom_hline(yintercept=1, linetype="dotted") + 
  ylab("Hazard ratio") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  scale_y_continuous(trans="log",limits=c(plot_min, plot_max), breaks=c(0.5,1,2)) +
  theme(axis.title = element_text(size=12), axis.text = element_text(size=12), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = c(-1.5,0.95))


plot_max = max(tbl_reduced$`% unvaccinated`, na.rm=T)+5
g2 = ggplot(tbl_reduced, aes(y = `% unvaccinated`, x = level,  colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_segment(aes(xend=level), yend=0) +
  ylim(0,plot_max) + coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + 
  ylab("% Unvaccinated") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  theme(axis.title = element_text(size=12), axis.text.x = element_text(size=12), axis.text.y = element_blank(), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = "none")

plot_grid(g1, g2, ncol=2,  align="h", axis = c("tb"), rel_widths = c(3,0.9))
```
<br/><br/><br/><br/>     

##### Approach (2): Logistic regression (sensitivity analysis)
```{r}
data_lr <- read_rds(here::here("output", "data", "data_lr.rds"))
total_vax = plyr::round_any(sum(data_lr$covid_vax),5)
total_N = plyr::round_any(nrow(data_lr),5)
vax_perc = round(total_vax/total_N*100,1)
```

Logistic regression models were used to explore factors associated with completion of a 2-dose series via any product combination by **01 Jul 2021** as a binary outcome variable. Individuals were included if they were registered and alive up to the analysis cut-off (N = `r prettyNum(total_N)`, rounded to nearest 5).    
    
Overall coverage as of **01 Jul 2021** was `r vax_perc`% (`r prettyNum(total_vax)` / `r prettyNum(total_N)`, rounded to nearest 5).    
    
Univariate models were used to explore the potential influence of each covariate in turn. Multivariate models adjusting for all other covariates were used to explore the potential influence of each covariate after adjusting for the effect of others.
<br/><br/>    

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
## Import logistic regression results
tbl_summary <- read_rds(here::here("output", "model", "mod_strat_logistic_redacted.rds"))

## Add % unvaccinated at cut-off
tbl_summary$perc_unvac <- round(100 - (as.numeric(tbl_summary$n_event) / as.numeric(tbl_summary$n_obs))*100,1)

## Select variables of interes
tbl_reduced <- tbl_summary %>%
   select(var_group, var_label, label, n_obs, n_event, perc_unvac,
         estimate_uni, conf.low_uni, conf.high_uni, p.value_uni,
         estimate_partial, conf.low_partial, conf.high_partial, p.value_partial,
         estimate, conf.low, conf.high, p.value)

## Relabel columns
names(tbl_reduced) = c("var_group", "group", "level", "n (total)", "n (vaccinated)", "% unvaccinated",
                            "OR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)",
                            "OR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)",
                            "OR (full)", "lower CI (full)", "upper CI (full)", "p (full)")

## Create formatted gt output
tbl_reduced %>% 
  gt(rowname_col = "level", groupname_col = "group") %>%
  tab_spanner(
    label = "univariate",
    columns = c("OR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)")
  ) %>%
    tab_spanner(
    label = "partially adjusted",
    columns = c("OR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)")
  ) %>%
  tab_spanner(
    label = "fully adjusted",
    columns = c("OR (full)", "lower CI (full)", "upper CI (full)", "p (full)")
  ) %>%
  cols_hide(columns = "var_group") %>%
  tab_options(table.font.size = pct(85)) %>%
   tab_style(
      style = list(
        cell_borders(
          sides = c("right"), color = "#cccccc"
        )
        ),
      locations = list(
        cells_body(
          columns = c("p (uni)", "p (multi)", "% unvaccinated")
        )
      )
   ) %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_footnote(
    footnote = "All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), 
            n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding.",
    locations = cells_column_labels(columns = "n (vaccinated)")
  ) %>%
  tab_footnote(
    footnote = "n (unvaccinated)/n (total)*100",
    locations = cells_column_labels(columns = "% unvaccinated")
  )
```
<br/><br/>     

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
## Remove redacted components from plot
tbl_reduced$`OR (multi)`[tbl_reduced$`OR (multi)`=="[Redacted]"] = NA
tbl_reduced$`lower CI (multi)`[tbl_reduced$`OR (multi)`=="[Redacted]"] = NA
tbl_reduced$`upper CI (multi)`[tbl_reduced$`OR (multi)`=="[Redacted]"] = NA

## Recode ORs and CIs as numerics
tbl_reduced$`OR (multi)` = as.numeric(tbl_reduced$`OR (multi)`)
tbl_reduced$`lower CI (multi)` = as.numeric(tbl_reduced$`lower CI (multi)`)
tbl_reduced$`upper CI (multi)` = as.numeric(tbl_reduced$`upper CI (multi)`)

## Set plot min
plot_min = 0.5
if(min(tbl_reduced$`lower CI (multi)`, na.rm=T) < plot_min) { plot_min = min(tbl_reduced$`lower CI (multi)`, na.rm=T) }

## Set plot max
plot_max = 2
if(max(tbl_reduced$`upper CI (multi)`, na.rm=T) > plot_max) { plot_max = max(tbl_reduced$`upper CI (multi)`, na.rm=T) }

## Add redaction text variable
tbl_reduced$redaction = NA
tbl_reduced$redaction[tbl_reduced$`n (total)`=="[Redacted]"] = "[R]"

## Generate plot of HRs
g1 = ggplot(tbl_reduced, aes(y = `OR (multi)`, x = level, colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_text(aes(y = plot_min+0.02, label = redaction)) +
  geom_errorbar(aes(ymin=as.numeric(`lower CI (multi)`), ymax=as.numeric(`upper CI (multi)`), colour = var_group), width=0) + 
  coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + labs(colour = "Group") +
  geom_hline(yintercept=1, linetype="dotted") + 
  ylab("Odds ratio") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  scale_y_continuous(trans="log",limits=c(plot_min, plot_max), breaks=c(0.5,1,2)) +
  theme(axis.title = element_text(size=12), axis.text = element_text(size=12), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = c(-1.5,0.95))


plot_max = max(tbl_reduced$`% unvaccinated`, na.rm=T)+5
g2 = ggplot(tbl_reduced, aes(y = `% unvaccinated`, x = level,  colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_segment(aes(xend=level), yend=0) +
  ylim(0,plot_max) + coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + 
  ylab("% Unvaccinated") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  theme(axis.title = element_text(size=12), axis.text.x = element_text(size=12), axis.text.y = element_blank(), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = "none")

plot_grid(g1, g2, ncol=2,  align="h", axis = c("tb"), rel_widths = c(3,0.9))
```
<br/><br/><br/><br/>

#### Covariates associated with vaccine coverage: dose 3 by 16 Feb 2022

##### Cox proportional hazards
```{r}
data_cox <- read_rds(here::here("output", "data", "data_cox_coverage_dose3.rds"))
total_vax = plyr::round_any(sum(data_cox$covid_vax),5)
total_N = plyr::round_any(nrow(data_cox),5)
vax_perc = round(total_vax/total_N*100,1)
```

Cox proportional hazards models were used to explore factors associated with completion of a 3-dose series via any product combination between **08 Dec 2020** and **16 Feb 2022** (date of most recent update for [OpenSAFELY vaccine coverage analyses](https://www.opensafely.org/research/2021/covid-vaccine-coverage/)). 
    
Overall coverage as of **16 Feb 2022** was `r vax_perc`% (`r prettyNum(total_vax)` / `r prettyNum(total_N)`, rounded to nearest 5). Follow-up was censored on the date of death, deregistration, or the end of the study period (16 Feb 2022).     
    
Univariate models stratified by region were used to explore the potential influence of each covariate in turn. Multivariate models stratified by region, adjusting for all other covariates, were used to explore the potential influence of each covariate after adjusting for the effect of others.
<br/><br/>   

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
## Import cox regression results
tbl_summary <- read_rds(here::here("output", "model", "mod_strat_coxph_redacted_dose3.rds")) 

## Add % unvaccinated at cut-off
tbl_summary$perc_unvac <- round(as.numeric(tbl_summary$n_unvax_at_cut_off)/as.numeric(tbl_summary$n_uncensored_at_cut_off)*100,1)

## Select variables of interes
tbl_reduced <- tbl_summary %>%
  select(var_group, var_label, label, n_obs,  n_event, n_uncensored_at_cut_off, perc_unvac,
         estimate_uni, conf.low_uni, conf.high_uni, p.value_uni,
         estimate_partial, conf.low_partial, conf.high_partial, p.value_partial,
         estimate, conf.low, conf.high, p.value)

## Relabel columns
names(tbl_reduced) = c("var_group", "group", "level", "n (total)", "n (vaccinated)", "n (uncensored)", "% unvaccinated",
                            "HR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)",
                            "HR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)",
                            "HR (full)", "lower CI (full)", "upper CI (full)", "p (full)")

## Create formatted gt output
tbl_reduced %>% 
  gt(rowname_col = "level", groupname_col = "group") %>%
  tab_spanner(
    label = "univariate",
    columns = c("HR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)")
  ) %>%
    tab_spanner(
    label = "partially adjusted",
    columns = c("HR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)")
  ) %>%
  tab_spanner(
    label = "fully adjusted",
    columns = c("HR (full)", "lower CI (full)", "upper CI (full)", "p (full)")
  )  %>%
  cols_hide(columns = "var_group") %>%
  tab_options(table.font.size = pct(85)) %>%
   tab_style(
      style = list(
        cell_borders(
          sides = c("right"), color = "#cccccc"
        )
        ),
      locations = list(
        cells_body(
          columns = c("p (uni)", "p (multi)", "% unvaccinated")
        )
      )
   ) %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_footnote(
    footnote = "All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), 
            n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding.",
    locations = cells_column_labels(columns = "n (vaccinated)")
  )  %>%
  tab_footnote(
    footnote = "n (unvaccinated and uncensored)/n (uncensored)*100",
    locations = cells_column_labels(columns = "% unvaccinated")
  )
```
<br/><br/>    

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
## Remove redacted components from plot
tbl_reduced$`HR (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA
tbl_reduced$`lower CI (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA
tbl_reduced$`upper CI (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA

## Recode HRs and CIs as numerics
tbl_reduced$`HR (multi)` = as.numeric(tbl_reduced$`HR (multi)`)
tbl_reduced$`lower CI (multi)` = as.numeric(tbl_reduced$`lower CI (multi)`)
tbl_reduced$`upper CI (multi)` = as.numeric(tbl_reduced$`upper CI (multi)`)

## Set plot min
plot_min = 0.5
if(min(tbl_reduced$`lower CI (multi)`, na.rm=T) < plot_min) { plot_min = min(tbl_reduced$`lower CI (multi)`, na.rm=T) }

## Set plot max
plot_max = 2
if(max(tbl_reduced$`upper CI (multi)`, na.rm=T) > plot_max) { plot_max = max(tbl_reduced$`upper CI (multi)`, na.rm=T) }

## Add redaction text variable
tbl_reduced$redaction = NA
tbl_reduced$redaction[tbl_reduced$`n (total)`=="[Redacted]"] = "[R]"

## Generate plot of HRs
g1 = ggplot(tbl_reduced, aes(y = `HR (multi)`, x = level, colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_text(aes(y = plot_min+0.02, label = redaction)) +
  geom_errorbar(aes(ymin=as.numeric(`lower CI (multi)`), ymax=as.numeric(`upper CI (multi)`), colour = var_group), width=0) + 
  coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + labs(colour = "Group") +
  geom_hline(yintercept=1, linetype="dotted") + 
  ylab("Hazard ratio") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  scale_y_continuous(trans="log",limits=c(plot_min, plot_max), breaks=c(0.5,1,2)) +
  theme(axis.title = element_text(size=12), axis.text = element_text(size=12), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = c(-1.5,0.95))


plot_max = max(tbl_reduced$`% unvaccinated`, na.rm=T)+5
g2 = ggplot(tbl_reduced, aes(y = `% unvaccinated`, x = level,  colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_segment(aes(xend=level), yend=0) +
  ylim(0,plot_max) + coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + 
  ylab("% Unvaccinated") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  theme(axis.title = element_text(size=12), axis.text.x = element_text(size=12), axis.text.y = element_blank(), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = "none")

plot_grid(g1, g2, ncol=2,  align="h", axis = c("tb"), rel_widths = c(3,0.9))
```
<br/><br/><br/><br/>

#### Covariates associated with vaccine coverage: dose 4 by 16 Feb 2022

##### Cox proportional hazards
```{r}
data_cox <- read_rds(here::here("output", "data", "data_cox_coverage_dose4.rds"))
total_vax = plyr::round_any(sum(data_cox$covid_vax),5)
total_N = plyr::round_any(nrow(data_cox),5)
vax_perc = round(total_vax/total_N*100,1)
```

Cox proportional hazards models were used to explore factors associated with completion of a 4-dose series via any product combination between **08 Dec 2020** and **16 Feb 2022** (date of most recent update for [OpenSAFELY vaccine coverage analyses](https://www.opensafely.org/research/2021/covid-vaccine-coverage/)).   
    
Overall coverage as of **16 Feb 2022** was `r vax_perc`% (`r prettyNum(total_vax)` / `r prettyNum(total_N)`, rounded to nearest 5). Follow-up was censored on the date of death, deregistration, or the end of the study period (16 Feb 2022).     
    
Univariate models stratified by region were used to explore the potential influence of each covariate in turn. Multivariate models stratified by region, adjusting for all other covariates, were used to explore the potential influence of each covariate after adjusting for the effect of others.
<br/><br/>   

##### Univariate and multivariate model outputs (scroll left/right for full table)
```{r}
## Import cox regression results
tbl_summary <- read_rds(here::here("output", "model", "mod_strat_coxph_redacted_dose4.rds")) 

## Add % unvaccinated at cut-off
tbl_summary$perc_unvac <- round(as.numeric(tbl_summary$n_unvax_at_cut_off)/as.numeric(tbl_summary$n_uncensored_at_cut_off)*100,1)

## Select variables of interes
tbl_reduced <- tbl_summary %>%
  select(var_group, var_label, label, n_obs,  n_event, n_uncensored_at_cut_off, perc_unvac,
         estimate_uni, conf.low_uni, conf.high_uni, p.value_uni,
         estimate_partial, conf.low_partial, conf.high_partial, p.value_partial,
         estimate, conf.low, conf.high, p.value)

## Relabel columns
names(tbl_reduced) = c("var_group", "group", "level", "n (total)", "n (vaccinated)", "n (uncensored)", "% unvaccinated",
                            "HR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)",
                            "HR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)",
                            "HR (full)", "lower CI (full)", "upper CI (full)", "p (full)")

## Create formatted gt output
tbl_reduced %>% 
  gt(rowname_col = "level", groupname_col = "group") %>%
  tab_spanner(
    label = "univariate",
    columns = c("HR (uni)", "lower CI (uni)", "upper CI (uni)", "p (uni)")
  ) %>%
    tab_spanner(
    label = "partially adjusted",
    columns = c("HR (multi)", "lower CI (multi)", "upper CI (multi)", "p (multi)")
  ) %>%
  tab_spanner(
    label = "fully adjusted",
    columns = c("HR (full)", "lower CI (full)", "upper CI (full)", "p (full)")
  )  %>%
  cols_hide(columns = "var_group") %>%
  tab_options(table.font.size = pct(85)) %>%
   tab_style(
      style = list(
        cell_borders(
          sides = c("right"), color = "#cccccc"
        )
        ),
      locations = list(
        cells_body(
          columns = c("p (uni)", "p (multi)", "% unvaccinated")
        )
      )
   ) %>%
  tab_options(row_group.font.weight="bold", column_labels.font.weigh="bold") %>%
  tab_footnote(
    footnote = "All counts rounded to nearest 5; data redacted for any rows with rounded values of <=10 for n (total), 
            n (vaccinated), or n (unvaccinated), where n (unvaccinated) is the difference between n (total) and n (vaccinated) after rounding.",
    locations = cells_column_labels(columns = "n (vaccinated)")
  )  %>%
  tab_footnote(
    footnote = "n (unvaccinated and uncensored)/n (uncensored)*100",
    locations = cells_column_labels(columns = "% unvaccinated")
  )
```
<br/><br/>    

#### Plot of partially adjusted model outputs
```{r, fig.width=8, fig.height=12}
## Remove redacted components from plot
tbl_reduced$`HR (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA
tbl_reduced$`lower CI (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA
tbl_reduced$`upper CI (multi)`[tbl_reduced$`HR (multi)`=="[Redacted]"] = NA

## Recode HRs and CIs as numerics
tbl_reduced$`HR (multi)` = as.numeric(tbl_reduced$`HR (multi)`)
tbl_reduced$`lower CI (multi)` = as.numeric(tbl_reduced$`lower CI (multi)`)
tbl_reduced$`upper CI (multi)` = as.numeric(tbl_reduced$`upper CI (multi)`)

## Set plot min
plot_min = 0.5
if(min(tbl_reduced$`lower CI (multi)`, na.rm=T) < plot_min) { plot_min = min(tbl_reduced$`lower CI (multi)`, na.rm=T) }

## Set plot max
plot_max = 2
if(max(tbl_reduced$`upper CI (multi)`, na.rm=T) > plot_max) { plot_max = max(tbl_reduced$`upper CI (multi)`, na.rm=T) }

## Add redaction text variable
tbl_reduced$redaction = NA
tbl_reduced$redaction[tbl_reduced$`n (total)`=="[Redacted]"] = "[R]"

## Generate plot of HRs
g1 = ggplot(tbl_reduced, aes(y = `HR (multi)`, x = level, colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_text(aes(y = plot_min+0.02, label = redaction)) +
  geom_errorbar(aes(ymin=as.numeric(`lower CI (multi)`), ymax=as.numeric(`upper CI (multi)`), colour = var_group), width=0) + 
  coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + labs(colour = "Group") +
  geom_hline(yintercept=1, linetype="dotted") + 
  ylab("Hazard ratio") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  scale_y_continuous(trans="log",limits=c(plot_min, plot_max), breaks=c(0.5,1,2)) +
  theme(axis.title = element_text(size=12), axis.text = element_text(size=12), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = c(-1.5,0.95))

plot_min = max(tbl_reduced$`% unvaccinated`, na.rm=T)-10
plot_max = max(tbl_reduced$`% unvaccinated`, na.rm=T)+5
g2 = ggplot(tbl_reduced, aes(y = `% unvaccinated`, x = level,  colour = var_group)) + 
  geom_point(size = 2, alpha=0.8) +
  geom_segment(aes(xend=level), yend=0) +
  ylim(plot_min,plot_max) + coord_flip() + facet_grid(group~., scales = "free", space = "free") + 
  theme_bw() + theme(strip.background = element_blank()) + 
  ylab("% Unvaccinated") + xlab("") +
  scale_colour_manual(values = c("#3B9AB2", "#E1AF00", "#B40F20")) +
  theme(axis.title = element_text(size=12), axis.text.x = element_text(size=12), axis.text.y = element_blank(), strip.text = element_blank(), 
        legend.title = element_text(size = 12), legend.text = element_text(size = 12), legend.position = "none")

plot_grid(g1, g2, ncol=2,  align="h", axis = c("tb"), rel_widths = c(3,0.9))
```
<br/><br/>    

##### Session info
```{r}
print(sessionInfo())
```

